, 42
Boolean algebra, 3–24
Boolean algebra, complete, 6
Boolean algebra, completion of, 183–195, 184, 185
Boolean algebra, M-complete, 21
Boolean algebra, natural, 3
Boolean algebra, natural order

definable class, 66, 68, 73
defined over $M'$, 87
denotation operator, 83, 143
dense beneath, 105
dense set, 8
dense set, no-where, 36
descrete topology, 7
direct system, 189
distribute laws, 47–50, 165–168
distributive laws, $(\alpha, \beta)$-, 47
distributive law, complete, 47

Easton’s main lemma, 216
Easton’s model, 221–226
elementary embedding, 143–147
elementary mapping, 146
elementary substructure, 74
embedding, elementary, 143–147
embedding, topological, 191
epimorphism, 16
extensional function, 151
extensional set, 152

filter, 28, 51
filter, $M$-complete, 28
filter, maximal, 51
filter, principal, 28
filter, proper, 28
filter, trivial, 28
fine partial order structure, 58
finite intersection property, 39, 45–46
finite set, 38
forcing, 102–105, 103
forcing, setting for, 104
formula, absolute, 66
formula, limited, 79
formula, unlimited, 80
function, extensional, 151
function, normal, 69
function(s), projection, 45
function, semi-normal, 69
function, Skolem, 74

$\gamma$-chain condition, 161
Generalized Continuum Hypothesis, 74, 76, 107, 169, 171
generic sets, 25–34

Gödel, 64
Gödel-Bernays set theory, 67

meager set, 36
measure algebra, 177

natural Boolean algebra, 3
natural order for Boolean algebra, 5
neighborhood, 7
nonatomic Boolean algebra, 132
normal function, 69
normal limiting system, 192

(ω, ω)-weak distributive law, 175
(ωα, ωβ)-weak distributive law, 214
open, continuous and onto inverse system, 188
open set, 8
operator, abstraction, 79
operator, denotation, 83

P-generic set, 25
partial order structure(s), 14, 51–58
partial order structure(s), associated, 52
partial order structure(s), coatomic, 215
partial order structure(s), filter for, 51
partial order structure(s), fine, 58
partial order structure(s), normal limiting system of, 192
partial order structure(s), product, 57
partial order structure(s), strongly coatomic, 215
partial order structure, ultrafilter for, 51
partial order structure, weakly normal limiting system of, 193
partial ordering, 14
partition of unity, 61
predicate constants, 79
principal filter, 28
product partial order structure, 57
product topology (weak), 45
product topological space, 45
projection functions, 45
proper filter, 28

quantified ranked variable, grade of, 80
quasi-disjoint set, 179

ramified language, 79–86
Rasiowa-Sikorski, 29
Rasiowa-Sikorski Theorem, 60, 100
ramified language, 79
ranked variables, 79
regular open set, 8
relative constructibility, 64–86
relative constructibility, Boolean-valued, 87
relative topology, 42
restricted (α, 2)-distributive law, 166

satisfaction, 60
Scott, 64
semi-n

space, locally compact, 38
space, topological, 7, 51–58
space, topological product, 45
strongly coatomic partial order structure, 215
structure(s), Boolean-valued, 59–63
structure(s), partial order, 14, 51–58
subalgebra, complete, 125
subalgebra generated by, 35
substructure, 65
substructure, B-valued, 87

$T_1$-space, 51
term, abstraction, 79
term, constant, 80
term, grade of, 80
topological embedding, 191
topological space(s), 7, 51–58
topological space, atomic, 191
topological space(s), open continuous and onto inverse system of, 188
topological space, product, 45
topology, 7
topology, base for, 7
topology, descrete, 7

topology, induced, 15
topology, product, 45
topology, relative, 40
trivial filter, 25
Tychonoff’s Theorem, 45

ultrafilter for partial order structure, 51
uniform convergence law, 200
uniform set, 153
unity, partition of, 61
universe of Boolean algebra, 3
unlimited formulas, 80
unranked variables, 79

Variables, ranked, 79
variables, unranked, 79

weak distributive law(s), 175–178, 175
weakly normal limiting system, 193

Zorn’s Lemma, 44, 46

Index of Symbols

$\langle B, +, \cdot, -, 0, 1 \rangle$ 3
$0, 1$ 3
$\mathcal{P}(a)$ 3
$|\mathbf{B}|$ 4
$0_{\mathbf{B}}, 1_{\mathbf{B}}$ 4
$a - b, a \Rightarrow b$ 5
$a \Rightarrow b, a \leq b$ 5
$\sum_{a \in A} a, \prod_{a \in A} a$ 6
$\langle X, T \rangle$ 7
$\langle P, \leq \rangle$ 14
$[x]$ 14
ker $(f)$ 19
$a/I, |\mathbf{B}|/I$ 20
$\mathbf{B}^M$ 21
$\mu_a(P(\alpha))$ 24
$\bigcap_{a \in I} \mathbf{B}_a$ 35
Fin $(S)$ 38
c.c.c. 43
$\prod_{a \in A} T_a$ 45
$p_a(C)$ 45
$(\alpha, \beta)$-DL 47
$N(p), \mathbf{T}$ 52
$G_1^*$, 53
$G_2^A$ 53
$\prod_{i \in I} P_i$ 57
$\langle A, \phi \rangle$ 59
$[[\varphi]]$ 59
$[[\varphi]]_{\mathbf{A}}$ 60
$A \models \varphi$ 60
$\langle A_1, \equiv, \bar{R}_0, \dots, \bar{c}_0, \dots \rangle$ 61
$L[a], L_a$ 64
$L[A]$ 65
$B \cap A$ 65
$C(A)$ 65
$F(x), \bar{F}(x)$ 66
$C(x)$ 66
$Fml(A)$ 66
$Fml^0, Fml^1$ 66
$\varphi

sup $(u)$ 154
Const $(x)$ 163
$U(p_0)$ 173
$(\omega, \omega)$-WDL 175
$A^{-s}, A^{0s}$ 183
$\#(b_1)$ 186
o.c.o. 188
$V_{\alpha}^{(B)}, V^{(B)}$ 197
$V_{\alpha}^{(\tilde{B})}, V^{(\tilde{B})}$ 197
UCL 200

$\lim_{a \in 0n} b_a$ 201
s.c.c. 203
$\Delta(\mathbf{B}_a)$ 210
I-$\Delta$SL 210
$(\omega_\alpha, \omega_\beta)$-WDL 214
$P$ 221
$\leq, \mathbf{P}$ 222
$\Gamma_\alpha, \Delta_\alpha$ 222
$\mathbf{P}_\alpha$ 223

Graduate Texts in Mathematics

Soft and hard cover editions are available for each volume

For information

A student approaching mathematical research is often discouraged by the sheer volume of the literature and the long history of the subject, even when the actual problems are readily understandable. The new series, Graduate Texts in Mathematics, is intended to bridge the gap between passive study and creative understanding; it offers introductions on a suitably advanced level to areas of current research. These introductions are neither complete surveys, nor brief accounts of the latest results only. They are textbooks carefully designed as teaching aids; the purpose of the authors is, in every case, to highlight the characteristic features of the theory.

Graduate Texts in Mathematics can serve as the basis for advanced courses. They can be either the main or subsidiary sources for seminars, and they can be used for private study. Their guiding principle is to convince the student that mathematics is a living science.

Vol. 1 TAKEUTI/ZARING: Introduction to Axiomatic Set Theory. vii, 250 pages. 1971.

Vol. 2 OXTOBY: Measure and Category. viii, 95 pages. 1971.

Vol. 3 SCHAEFER: Topological Vector Spaces. xi, 294 pages. 1971.

Vol. 4 HILTON/STAMMBACH: A Course in Homological Algebra. ix, 338 pages. 1971.

Vol. 5 MAC LANE: Categories for the Working Mathematician. ix, 262 pages. 1972.

Vol. 8 TAKEUTI/ZARING: Axiomatic Set Theory. vii, 238 pages. 1973.

Vol. 9 HUMPHREYS: Introduction to Lie Algebras and Representation Theory. xiv, 169 pages. 1972.

In preparation

Vol. 6 HUGHES/PIPER: Projective Planes. xii, 296 pages approximately. Tentative publication date: March, 1973.

Vol. 7 SERRE: A Course in Arithmetic. x, 115 pages approximately. Tentative publication date: February, 1973.

Vol. 10 COHEN: A Course in Simple-Homotopy Theory. xii, 112 pages approximately. Tentative publication date: February, 1973.

Vol. 11 CONWAY: Functions of One Complex Variable. x, 313 pages approximately. Tentative publication date: July, 1973.
