Let $l$ be a prime number. Assume that $G$ is the semidirect product of an $l$-group $P$ by a cyclic normal subgroup $C$ of order prime to $l$. Then every simple $k[G]$-module $E$ can be lifted (i.e., is the reduction mod $m$ of an A-free $A[G]$-module).

(In other words, $d$ maps $R_K^+(G)$ onto $R_k^+(G)$.)

Suppose $l \neq p$. Let $C_p$ be the $p$-Sylow subgroup of $C$, and let $E'$ be the vector subspace of $E$ consisting of those elements fixed by $C_p$. Since $C_p$ is a $p$-group,

module Ind$_{G_\beta}^{\text{G}}(\text{E}_\beta)$. Moreover, $G_\beta$ is the semidirect product of a subgroup of $P$ and the group $C$. If $E_\beta \neq E$, we have $G_\beta \neq G$, and the induction hypothesis applied to $G_\beta$ shows that $E_\beta$ can be lifted; the same is then true for $E$.

Thus we may assume that $E$ is an isotypic $k[\text{C}]$-module. Let $\rho$ denote the homomorphism from $k[\text{G}]$ into $\text{End}_k(\text{E})$ which defines the $k[\text{G}]$-module structure on $E$. The fact that $E$ is $k[\text{C}]$-isotypic is equivalent to saying that the image of $k[\text{C}]$ under $\rho$ is a field $k'$, which is a finite extension of $k$. The restriction of $\rho$ to $C$ is a homomorphism $\phi: C \rightarrow k'^*$, and $k'$ is generated over $k$ by $\phi$ (C). The module $E$ is thus endowed with the structure of a $k'$-vector space. Now choose an element $v \neq 0$ of $E$ invariant under $P$; again this is possible since $P$ is a $p$-group, cf. 8.3, prop. 26. For $x \in C$, $s \in P$, put $sx = sxs^{-1}$. We have

$$\rho(s)(\phi(x) \cdot v) = \rho(sxs^{-1})\rho(s) \cdot v = \phi(sx) \cdot v.$$

Hence the subspace $k'v$ of $E$ generated by the $\phi(x) \cdot v, x \in C$, is stable under $C$ and $P$, thus is equal to $E$. Hence $\text{dim}_{k'}\text{E} = 1$. This allows us to identify $E$ with $k'$ in such a way that $v$ becomes the unit element of $k'$. For all $t
