Let $X$ be any set and $E$ any subset of $X$. The function $\xi_E$ with domain $X$ and range contained in $\{0, 1\}$ such that

$$\xi_E(x) = \begin{cases} 1 \text{ if } x \in E, \\ 0 \text{ if } x \in X \cap E', \end{cases}$$

is called the characteristic function of $E$. It will always be clear from the context what the domain of $\xi_E$ is. Characteristic functions are very useful in analysis, and will be encountered frequently throughout this text. One particular characteristic function is used so much that it has a special symbol. The diagonal $D$ of $X \times X$ is defined as $D = \{(x, x) : x \in X\}$. The value of the characteristic function of $D$ at $(

a least upper bound, i.e., if $x, y \in X$, then there exists $z \in X$ such that $x \leq z, y \leq z$, and if $x \leq w, y \leq w$, then $z \leq w$.

(2.26) Exercise. Let $f$ be a function from $X$ to $Y$. Suppose that there is a function $g$ from $Y$ to $X$ such that $f \circ g(y) = y$ for all $y \in Y$ and $g \circ f(x) = x$ for all $x \in X$. Prove that $f$ is a one-to-one function from $X$ onto $Y$ and that $g = f^{-1}$.

§ 3. The axiom of choice and some equivalents

In the study of algebra, analysis, and topology one frequently encounters situations in which the tools of elementary set theory [as they have been informally presented in §§ 1 and 2] are too weak to permit constructions, proofs, or even definitions that one may need. In the early 1900's the German mathematician Ernst Zermelo propounded an innocent-appearing but actually very strong axiom, called the axiom of choice [Auswahlpostulat], which has many important consequences, and which has also excited vigorous controversy. In this section we take up the axiom of choice, establish the equivalence of four other assertions with it, and point out two important applications. Other applications of the axiom of choice will appear throughout the book.