Let $X$ be a topological space.

(i) If $f \in \mathfrak{M}(X)$ and $\alpha$ is a nonnegative real number, then $\alpha f \in \mathfrak{M}(X)$.

(ii) If $f, g \in \mathfrak{M}(X)$, then $\min \{f, g\} \in \mathfrak{M}(X)$.

(iii) If $\mathfrak{D}$ is a nonvoid subset of $\mathfrak{M}(X)$, then $\sup \{f : f \in \mathfrak{D}\}$ is a function in $\mathfrak{M}(X)$.

(iv)

$$[f(x_0) = \infty],$$ we infer that $f(x_0) = \sup \left\{ \varphi(x_0) : \varphi \in \mathfrak{C}_{00}^+(X), \varphi \leq f \right\}$. Since $x_0$ is arbitrary, $(v)$ is established.

(7.23) Exercise. (a) State and prove the analogue of (7.22) for upper semicontinuous functions.

(b) Let $X$ be a topological space admitting a nonclosed open set. Prove that $\mathfrak{M}^r(X)$, the real-valued lower semicontinuous functions on $X$, do not form a linear space. If every open subset of $X$ is closed, prove that $\mathfrak{M}^r(X)$ is a linear space.

(c) Prove that uniform limits of sequences in $\mathfrak{M}^r(X)$ are in $\mathfrak{M}^r(X)$.

(7.24) We now take up a famous and vitally important approximation theorem. The German mathematician Karl Weierstrass [1815—1897] published in 1885 a proof that polynomials with real coefficients are dense in the space $\mathfrak{C}^r([0, 1])$ in the topology induced by the uniform metric. We will prove a far-reaching generalization of this theorem due to the contemporary U.S. mathematician M. H. Stone. Every proof of the Stone-Weierstrass theorem requires some "hard" analysis. Our proof uses only a little such analysis, which is presented in the next theorem. We prove somewhat more than we need.