commutative as with rings. Finally we recall that a semigroup is a pair $(S, \alpha)$ satisfying all the axioms for a group except the one on the existence of inverses.

3.1 Example. Let $X$ be a topological space and let $\text{Vect}_F(X)$ be the set of isomorphism classes of $F$-vector bundles over $X$ where $F = \mathbf{R}, \mathbf{C}$, or $\mathbf{H}$. These vector bundles need not have the same dimension on each component of $X$. For $F = \mathbf{R}$ or $\mathbf{C}$ the set $\text{Vect}_F(X)$ admits a natural commutative semiring structure where $(\xi, \eta) \mapsto \xi \oplus \eta$ is the addition function and $(\xi, \eta) \mapsto \xi \otimes \eta$ is the multiplication function. For $F = \mathbf{H}$, the set $\text{Vect}_H(X)$ admits only a natural commutative semigroup structure, where $(\xi, \eta) \mapsto \xi \oplus \eta$ is the addition function. We used the same symbol for a vector bundle and for its isomorphism class.

Recall that a morphism from a semiring $S$ to a semiring $S'$ is a function $f: S \rightarrow S'$ of the underlying sets such that $f(a + b) = f(a) + f(b)$, $f(ab) = f(a)f(b)$, and $f(0) = 0$.

3.2 Example. For a pointed space $X$ we have a semiring morphism $rk: \text{Vect}_F(X) \rightarrow \mathbf{Z}$, the rank or dimension of the vector bundle on the component of $X$ containing the base point. For $\mathbf{H} = F, rk$ is only a semigroup morphism.

Now we consider for general semirings the process of passing from a semiring to a ring in the most efficient way. When applied to the semiring of natural numbers, this process yields the ring of integers. A similar discussion applies to the group completion of commutative semigroups.
