Let $G$ be a region and let $\varphi: G \to \mathbb{R}$ be a continuous function. $\varphi$ is a subharmonic function if whenever $\bar{B}(a; r) \subset G$,

$$\varphi(a) \leq \frac{1}{2\pi} \int_{0}^{2\pi} \varphi(a + re^{i\theta}) d\theta.$$

$\varphi$ is a superharmonic function if whenever $\bar{B}(a; r) \subset G$,

$$\varphi(a) \geq \frac{1}{2\pi} \int_{0}^{2\pi} \varphi(a + re^{i\theta}) d\theta.$$

The first comment that should be made is that $\varphi$ is superharmonic iff $-\varphi$ is subharmonic. Because of this, only the results on subharmonic functions will be given and it will be left to the reader to state the analogous result for superharmonic functions. Nevertheless, we will often quote results on superharmonic functions as though they had been stated in detail.

In the definition of a subharmonic function $\varphi$ it is possible to assume only that $\varphi$ is upper semi-continuous. However this would make it necessary to use the Lebesgue Integral in the definition instead of the Riemann Integral. So it is assumed that $\varphi$ is continuous when $\varphi$ is subharmonic even though there are certain technical advantages that accrue if only upper semi-continuity is assumed.

Clearly every harmonic function is subharmonic as well as superharmonic. In fact, according to Theorem 2.11, $u$ is harmonic iff $u$ is both subharmonic and superharmonic. If $\varphi_1$ and $\varphi_2$ are subharmonic then so is $a_1\varphi_1 + a_2\varphi_2$ if $a_1, a_2 \geq 0$.

It is interesting to see which of the results on harmonic functions also hold for subharmonic functions. One of the most important of these is the Maximum Principle.

3.2 Maximum Principle (Third Version). Let $G$ be a region and

Again, the proof is identical to that of Theorem 1.7 and will not be repeated here.