The image of $\overline{E}_1$ in $R_k(G)$ is independent of the choice of the stable lattice $E_1$.

(Two $k[G]$-modules $\overline{E}_1$ and $\overline{E}_2$ obtained by reduction of stable lattices $E_1$ and $E_2$ need not be isomorphic, cf. ex. 15.1. What the above theorem says is that they have the same composition factors.)

Let $E_2$ be a lattice of $E$ stable under $G$. We must show that $[\overline{E}_1] = [\overline{E}_2]$ in $R_k(G)$. We begin with a special case:

We have $mE_1 \subset E_2 \subset E_1$. Let $T$ be the $k[G]$-module $E_1/E_2$. Then we have an exact sequence

$$0 \rightarrow T \rightarrow \overline{E}_2 \rightarrow \overline{E}_1 \rightarrow T \rightarrow 0,$$

where the homomorphism $T \rightarrow \overline{E}_2$ is obtained from multiplication by a generator $\pi$ of the ideal $m$. Passing to $R_k(G)$, we have

called the decomposition homomorphism. It takes $R^+_K(G)$ into $R^+_k(G)$. The corresponding matrix $D$ (relative to the canonical bases of $R_K(G)$ and $R_k(G)$) is called the decomposition matrix. It is a matrix of type $S_k \times S_k$ with nonnegative integer coefficients. For $F \in S_k$ and $E \in S_k$ the corresponding coefficient $D_{FE}$ of $D$ is the number of times that $F$ appears in the reduction mod. $m$ of a stable lattice $E_1$ of $E$: thus

$$[\bar{E}_1] = \sum_F D_{FE}[F] \quad \text{in } R_k(G).$$

Remarks

(1) The hypothesis that $K$ be complete plays no role in the proof of th. 32 nor in the definition of the homomorphism $d$.

(2) There are analogous results for algebraic groups, cf. Publ. Sci. I.H.E.S. no. 34, 1968, pp. 37–52.

EXERCISES

15.2. Take $p = 2$ and $G$ of order 2. Let $E = K[G]$. Show that $E$ has stable lattices whose reductions are semisimple (isomorphic to $k \oplus k$) and others whose reductions are not semisimple (isomorphic to $k[G]$).

15.3. Let $E$ be a nonzero $K[G]$-module and $E_1$ a lattice in $E$ stable under $G$. Prove the equivalence of the following:

(i) The reduction $\bar{E}_1$ of $E_1$ is a simple $k[G]$-module.

(ii) Every lattice in $E$ stable under $G$ has the form $aE$ with $a \in K^*$. Show that these imply that $E$ is a simple $K[G]$-module.

15.4. (After J. Thompson.) Let $E$ be a $Z$-free $Z[G]$-module, with rank $n \geqslant
