The proof is left to

The Axiom of Choice and Cardinal Numbers

Cantor defined the cardinal number of a set $M$ to be "the general concept which, by means of our active faculty of thought, arises from the set $M$ when we make abstraction of the nature of its various elements $m$ and of the order in which they are given." He denoted this cardinal number by $\bar{M}$. The two bars indicate the two levels of abstraction needed to produce the cardinal number from $M$. With only one level of abstraction, that is, by only abstracting of the nature of its various elements, we obtain the ordinal number $\bar{M}$. Cantor's definition of cardinal number is clearly not an operational one. Indeed Cantor's words suggest that cardinal numbers are psychological entities rather than mathematical objects.

Frege, in 1884, and Russell, independently in 1903, removed cardinal numbers from the psychic realm by defining the cardinal number of a set $a$ to be the class, $\bar{a}$, of all sets that can be mapped one-to-one onto $a$. While this definition has a certain intuitive appeal it has the disadvantage that, at least relative to ZF theory, the objects produced are not sets but proper classes. This is the same problem that we faced with ordinal numbers and, as we did there, we will resolve the problem by defining the cardinal number $\bar{a}$ to be a particular set that can be mapped one-to-one onto $a$ and which will then serve as a representative of the class of all such sets. Let us review the situation for ordinal numbers.

The study of ordinal numbers is essentially the study of well-ordered sets. The appropriate mappings for such a study are the one-to-one-onto-order-preserving maps. Under such mappings well-ordered sets divide into equivalence classes, each of which contains exactly one ordinal number. More precisely, each equivalence class contains exactly one set that is transitive and well ordered by the $\in$-relation. From each equivalent class we took this special set as a representative, and we called these representatives ordinal numbers.

We propose to do a similar thing for cardinal numbers. For the study of cardinal numbers the basic mappings are simply the one-to-one-onto maps. Sets $a$ and $b$ are said to be equivalent (or equipollent) if there exists a function $f$ that maps $a$ one-to-one onto $b$.
