If

By assumption, $\mathfrak{p}^e$ is a primary ideal, and its radical $\mathfrak{P}$ is therefore a prime ideal. Hence, at least one of the $q$ factors on the left-hand side of (5) must belong to $\mathfrak{P}$. Now, $\mathfrak{p}^e$, and therefore also $\mathfrak{P}$, is invariant under all the $k$-automorphisms of $K$ (more precisely: under all the $k[X] -$ automorphism of $K[X]$ which are extensions of $k$-automorphisms of $K$), and the $k$-automorphisms of $K$ act transitively on the $q$ roots $c'_i$ of $G(T)$. Hence all the $q$ factors $A(X) - c'_i B(X)$ belong to $\mathfrak{P}$. Now, the $q$ roots $c'_i$ are distinct, since $G(T)$ is a separable polynomial. If $q$ were greater than 1, it would then follow that $B(X)$ belongs to $\mathfrak{P}$. Then some power of $B(X)$ would belong to $\mathfrak{p}^e$ and hence also to $\mathfrak{p}$, since $\mathfrak{p}^{ec} = \mathfrak{p}$. Hence $B(X)$ itself would belong to $\mathfrak{p}$, in contradiction with the fact that $B(x) \neq 0$. Hence $q$ must be equal to 1, and this proves that $\alpha \in k$.

We now assume that $k$ is q.m.a. in $F(\mathfrak{p})$. We consider an arbitrary extension $K$ of $k$ and we must prove that the extended ideal $\mathfrak{p}^e$ of $\mathfrak{p}$ in $K[X_1, X_2, \cdots, X_n]$ is primary. Let $K'$ be an intermediate field between $k$ and $K$ such that $K'$ is a pure transcendental extension of $k$ and $K$ is an algebraic extension of $K'$. By Theorem 35, the ideal $\mathfrak{p}' = \

We have $G(\xi) = 0$, i.e.,

$$\sum_{j=0}^{q-1} G_j(\xi)\alpha^j = 0.$$

If the coefficients $G_j(\xi)$ in (7) are not all zero, then (7) is a relation of algebraic dependence for $\alpha$ over $F(\mathfrak{p}) (= k(\xi))$ and it is of degree $< q$. However, the assumption that $k$ is q.m.a. in $F(\mathfrak{p})$ implies that the polynomial $f(T)$ remains irreducible in $F(\mathfrak{p})[T]$. This follows from the fact that $f(T)$ is a separable polynomial. In fact, if $f_1(T)$ is a factor of $f(T)$ in $F(\mathfrak{p})[T]$ and if we assume that the leading coefficient of $f_1(T)$ is 1, then the coefficients of $f_1(T)$ are elements of $F(\mathfrak{p})$ which are separable algebraic over $k$ (since these coefficients belong to a decomposition field of the separable polynomial $f(T)$) and therefore must belong to $k$. Thus $f_1(T)$ must divide $f(T)$ already in $k[T]$ and therefore must coincide with $f(T)$. From the irreducibility of $f(T)$ over $F(\mathfrak{p})$ follows that all the coefficients $G_j(\xi)$ in (7) must be zero. That signifies that the polynomials $G_j(X)$ belong to $\mathfrak{p}$. Hence, by (6), $G(X) \in \mathfrak{p}^e$, and consequently $F(X) \in \sqrt{\mathfrak{p}^e}$, since $G(X)$ is the $p^s$-th power of $F(X)$. This completes the proof of Theorem 38.

The preceding theorem can also be derived from two basic theorems on free joins of integral domains, namely Theorems 38 and 40 of Vol. I, Ch. III, § 15. We first observe that by the above lemma and by Theorem 38 of Vol.

observe that in the presence of condition (1), condition (2) can be replaced by the weaker condition (2') that $k$ be q.m.a. in $F$. For, if (1) and (2') hold and $\alpha$ is any element of $F$ which is algebraic over $k$, then also it follows from the very definition of separability in terms of linear disjointness (Vol. I, Ch. II, § 15, p. 113) that $k(\alpha)$, as a subfield of $F$, is also separable over $k$. Hence $\alpha$ is separable algebraic over $k$ and thus belongs to $k$. This shows that (2) holds.