Let $\mathfrak{p}$ be a prime ideal in a polynomial ring $R = k[X_1, X_2, \cdots, X_n]$. A necessary and sufficient condition that $\mathfrak{p}$ be absolutely prime is that the field $F(\mathfrak{p})$ be a regular extension of $k$.

Proof. It is clear that $\mathfrak{p}$ is absolutely prime if and only if $\mathfrak{p}$ is both quasi-absolutely prime and absolutely unramified. Our theorem is therefore a direct consequence of Theorems 37 and 38, in view of the remark just made above in regard to the equivalence of the conditions (2) and (2') (in presence of condition (1)).

Remark. The results derived in this section give us information not only about the behavior of a given prime ideal $\mathfrak{p}$ under various extensions $K$ of the ground field but also about the behavior of the various prime ideals $\mathfrak{p}$ in $R$ under a fixed extension $K$ of $k$. Thus we have shown that (1) if $K$ is a pure transcendental extension of $k$ then $\mathfrak{p}^e$ is prime for every $\mathfrak{p}$ (Theorem 35); (2) if $K$ is a separable extension of $k$ then $\mathfrak{p}^e$ is an intersection of prime ideals for every $\mathfrak{p}$ (Corollary of Lemma); (3)

of the additive group of $M$, such that, for every pair of integers $(q, r)$, we have

$$R_r M_q \subset M_{q+r}.$$

The elements of $M_q$ are said to be homogeneous of degree $q$. Given any element $x \in M$, we can write, in a unique way,

$$x = \sum_{- \infty}^{+ \infty} x_q,$$

where $x_q \in M_q$ and where all terms, except a finite number, are zero. The element $x_q$ is called the homogeneous component of degree $q$ of $x$. The notation $M_q$ for the additive group of homogeneous elements of degree $q$ of $M$ will be used without further warning.

A submodule $N$ of $M$ is said to be homogeneous if the relation $x \in N$ implies that all the homogeneous components of $x$ belong to $N$.

The homogeneous submodules of $R$, where $R$ is considered as a module over itself, are obviously its homogeneous ideals (§2). As in the case of ideals (Theorem 7, §2) one proves that, in order for a submodule $N$ of a graded module $M$ to be homogeneous, it is necessary and sufficient that $N$ be generated by homogeneous elements of $M$. It is a straightforward matter to verify that a homogeneous submodule $N$ of a graded module $M$ is itself a graded module, and that the difference module $M-N$ is also a graded module. The proof is the same as that of Lemma 1, part (b), §2.

Given two graded $R$-modules $M$ and $M'$ and an integer $d$, a homomorphism $\theta$ of $M$ into $M'$ is said to be homogeneous of degree $d$ if $\theta(M_q) \subset M'_{d+q}$ for every $q$ (i.e., if the image of any homogeneous element of degree $q$ of $M$ is a homogeneous element of degree $d+q$ in $M'$). For example, if $a_d$ is a homogeneous element of degree $d$ in $R$, the mapping $x