An integrally closed local domain in which the ideal of non-units is the only proper prime ideal is a discrete valuation ring of rank 1.

This follows from §5, Theorem 9, Corollary 3.

Corollary 2. If $R$ is an integrally closed noetherian domain and $\mathfrak{p}$

also in the general case. If $w \in K$, $w \neq 0$, we write $w = w_1/w_2$, $w_i \in R$. If $v_p(w_1) \geq v_p(w_2)$ for all $p$ in $S$, then in view of the relations

$$Rw_1 = \bigcap_{p \in S} p^{(v_p(w_1))}$$

$$Rw_2 = \bigcap_{p \in S} p^{(v_p(w_2))},$$

it follows that $Rw_1 \subset Rw_2$ and hence $w_1/w_2 \in R$. This proves (2). The last part of the corollary is now obvious.

We now go back to the study of general valuations and we add first some remarks about isolated subgroups, which we shall presently make use of.

Let $\Delta$ be an isolated subgroup of $\Gamma$. It is immediately seen that the canonical homomorphism of $\Gamma$ onto $\Gamma/\Delta$ defines a total ordering in $\Gamma/\Delta$, in the following fashion: an element of $\Gamma/\Delta$ shall be, by definition, non-negative if it corresponds to a non-negative element of $\Gamma$. From now on, when we speak of $\Gamma/\Delta$ as a totally ordered group we mean that $\Gamma/\Delta$ has been ordered in the above fashion.

In the canonical homomorphism of $\Gamma$ onto $\Gamma/\Delta$, the isolated subgroups of $\Gamma$ which contain $\Delta$ correspond in (1, 1) fashion to the isolated subgroups of $\Gamma/\Delta$. Since every isolated subgroup of $\Gamma$ either contains or is contained in $\Delta$, it follows that if $\xi$ is the rank of $\Delta$ and $\eta$ is the rank of $\Gamma/\Delta$, then the rank of $\Gamma$ is $\xi + \eta$.

In §3, we have defined specialization of places. The valuation-theoretic interpretation of this concept leads to the notion of composite valuations. Let $v$ be a valuation of $K$, of rank $> 1$. There exists then another valuation $v_1$ of $K$ such that $R_v < R_{v_1}$. Let $\mathcal{P}$ and

$R_{v_1}$ respectively. We first observe that $E_1$ is the full inverse image of $\Delta$ under $v^{-1}$. For if $x$ is any element of $E_1$, then $x=y/z$, where $y$ and $z$ are elements of $R_v$, not in $\mathfrak{P}$ (since $R_{v_1}$ is the quotient ring of $R_v$ with respect to $\mathfrak{P}$). Then $v(z)$ is a non-negative element of $\Gamma$ which does not belong to $\mathfrak{P}v$, and hence, by the definition of $\Delta$, $v(z)$ must belong to $\Delta$. Similarly for $v(y)$. Since $\Delta$ is a group, it follows that $v(x) \in \Delta$. Conversely, if $x$ is an element of $K'$ such that $v(x)$ belongs to $\Delta$, then neither $v(x)$ nor $v(1/x)$ belongs to $\mathfrak{P}v$. Since $\mathfrak{P}$ is the full inverse image of $\mathfrak{P}v$ under $v^{-1}$, it follows that neither $x$ nor $1/x$ can belong to $\mathfrak{P}$. Hence $x$ is a unit in $R_{v_1}$. This establishes our assertion that $E_1$ is the full inverse image of $\Delta$ under $v^{-1}$.

We can therefore assert that

(a) the restriction of $v$ to $E_1$ is a homomorphism of the multiplicative group $E_1$ onto the additive group $\Delta$, and the kernel of this homomorphism is $E$.

Now, $v$ and $v_1$ are homomorphisms of $K'$ onto $\Gamma$ and $\Gamma_1$ respectively, with kernels $E$ and $E_1$. Since $E_1 \supset E$, it follows that $v^{-1}v_1$ is a homomorphism of $\Gamma$ onto $\Gamma_1$. By (a), the kernel of this homomorphism is precisely the isolated subgroup $\Delta$. Hence $\Gamma_1$ and $\Gamma/\Delta$ are isomorphic as groups. If

cular, in algebraic geometry) are valuations of finite rank (see §3, Definition 1, Corollary 1), and we shall now derive some properties of such valuations.

An archimedean totally ordered (additive) group $\Gamma$ is one satisfying the following condition: if $\alpha$ and $\beta$ are any two elements of $\Gamma$ and $\alpha > 0$, then there exists an integer $n$ such that $n\alpha > \beta$. Let $\Gamma$ be archimedean and let $\Delta$ be an isolated subgroup of $\Gamma$. It follows at once from the above definition that if $\Delta$ contains a positive element $\alpha$ then $\Delta$ coincides with $\Gamma$, contrary to the fact that an isolated subgroup of $\Gamma$ is, according to our definition, a proper subgroup of $\Gamma$. Hence (0) is the only isolated subgroup of $\Gamma$, and $\Gamma$ is therefore of rank 1. Conversely, suppose that $\Gamma$ is a totally ordered group of rank 1, and let $\alpha$ be a positive element of $\Gamma$. The set of all elements $\pm \beta$, where $\beta$ is a non-negative element of $\Gamma$ such that $n\alpha > \beta$ for a suitable $n$ (depending on $\beta$), is a segment and a subgroup of $\Gamma$, and this set does not consist only of the element 0, for $\alpha$ belongs to the set. Since $\Gamma$ is of rank 1, it follows that the above set coincides with $\Gamma$, and hence $\Gamma$ is archimedean. We have thus proved that an ordered group is archimedean if and only if it is of rank 1.

The following well-known argument shows that every archimedean ordered abelian group $\Gamma$ is isomorphic to a subgroup of the ordered additive group of real numbers (and therefore valuations of rank 1 are frequently referred to as real valuations).

We fix a positive element $\alpha$ of $\Gamma$. If $\beta$ is any element of $\Gamma$ we divide the set of all rational numbers $m/n (n > 0)$ into two classes $C_1$ and $C_2$, as follows: $m/n \in C_1$ if $m\alpha < n\beta$, and

K and h arbitrary elements $\alpha_1, \alpha_2, \cdots, \alpha_h$ of $\Gamma_1, \Gamma_2, \cdots, \Gamma_h$ respectively, there exists an element $u$ of $K$ such that

(1) $v_i(u - u_i) = \alpha_i, \quad i = 1, 2, \cdots, h.$