Let $X$ be a compact Hausdorff space and let $\xi$ be a complex Borel measure on $X$. Then the mapping

$$f \rightarrow \int_X f d\xi, \quad f \in \mathcal{C}(X),$$

is a linear functional on the space $\mathcal{C}(X)$ of continuous complex-valued functions on $X$ such that

$$\left| \int_X f d\xi \right| \leq \int_X |f| |d|\xi|, \quad f \in \mathcal{C}(X).$$

Problems

A. Show that a closed subset $F$ of a locally compact Hausdorff space $X$ is compact if and only if there exists a topologically bounded open set $U$ in $X$ such that $F \subset U$.

B. Let $X$ be a locally compact Hausdorff space satisfying the second axiom of countability, and let $\hat{X}$ denote the one-point compactification of $X$ (Prob. 3W). Show that $X$ is $\sigma$-compact, and use this fact to show that $\hat{X}$ also satisfies the second axiom of countability. Conclude that $\hat{X}$ and $X$ are both metrizable. Finally, in the converse direction, show that a locally compact metrizable space $X$ satisfies the second axiom of countability if and only if $X$ is $\sigma$-compact.

C. (Berberian and Jakobsen [8]). Let $X$ be a locally compact Hausdorff space, and let $\mathcal{K}$ denote the collection of all compact subsets of $X$. Show that the $\sigma$-ring $\mathbf{S}(\mathcal{K})$ is a $\sigma$-ideal (Prob. 6I) in the $\sigma$-ring $\mathbf{B}$ of Borel subsets of $X$, and use this fact to conclude that $\mathbf{S}(\mathcal{K})$ consists precisely of those Borel sets in $X$ that are $\sigma$-compact. (Hint: Let $\mathbf{T}$ denote the collection of subsets $T$ of $X$ with the property that $E \cap T \in

(iii) Show similarly that if each set $E_n$ of a countable collection $\{E_n\}$ of Borel sets is regular with respect to $\mu$, then the union $\bigcup_n E_n$ is also regular with respect to $\mu$. (Hint: Sets of infinite measure are trivially outer regular.)

(iv) Conclude that the collection $R$ of all regular Borel sets of finite measure with respect to $\mu$ is a ring of sets, and that $R$ is, in fact, a $\sigma$-ring if $\mu(X) < +\infty$. (In particular, then, this is true if $X$ is compact.)

G. Provide a proof for Proposition 10.3. (Hint: Use the results of the preceding problem to show that if $E$ denotes any one set in $\mathcal{C}$, then the collection of all Borel sets $M$ such that $M \subset E$ and $M$ is regular with respect to $\mu$ is a $\sigma$-ring containing the trace $\mathcal{C}_E$ and therefore containing the $\sigma$-ring $S(\mathcal{C}_E) = (S(\mathcal{C}))_E$ (Prob. 6D). Recall that every set in $S(\mathcal{C})$ is contained in the union of some countable collection of sets in $\mathcal{C}$ (Prob. 6I).)

H. Derive Proposition 10.8 from Proposition 10.7. (Hint: See Example 7N.)

I. Let $\xi$ be a regular complex Borel measure on a compact Hausdorff space $X$. Prove that the total variation of $\xi$ is given by

$$\sup \left| \int_X f d\xi \right|,$$

where the supremum is taken over the collection of all continuous functions $f$ on $X$ such that $|f| \leq 1$. (The reader should compare this result with Problem 8V.) (Hint: Use a partition of unity; see Example 3G.)

J. Suppose we set $a = 1$ in Example C. Determine which Borel subsets of $W$ are regular with respect to the measure $\mu_1$ defined there, and which are not. Show

note the Borel measure on $X_{\gamma}$ corresponding to Lebesgue-Borel measure on $[0, 1]$ under the mapping $\varphi_{\gamma}$, and let $\mu$ denote the direct sum of the family of measures $\{\mu_{\gamma}\}$. According to Problem K the space $X$ is a metrizable locally compact Hausdorff space, and the restriction $\mu_0$ of $\mu$ to the $\sigma$-ring of Borel subsets of $X$ is a Borel measure on $X$. Determine which Borel sets in $X$ are regular with respect to $\mu_0$ and which are not. (Hint: Every open subset of $X$ that meets uncountably many of the subspaces $X_{\gamma}$ has infinite measure.) Find a closed set $F$ and an open set $U$ in $X$, both of which are regular with respect to $\mu_0$ such that $U \subset F$ but such that $F \setminus U$ fails to be regular. Thus the regular sets with respect to a Borel measure need not form a ring, or even a quasiring (Prob. 6J).

This construction, which is essentially due to S. K. Berberian [7], is really much more illuminating than the one given in Example C. Here we have a measure space that is simple and natural in every way, except of course that it is quite large, and yet there are many Borel sets that fail to be regular. The message is clear: For very large locally compact Hausdorff spaces (even metrizable ones), the requirement of regularity for a Borel measure, as we have defined it, is not only quite restrictive, it may even be unnatural. The following six problems introduce a notion that is less restrictive than regularity, but is still strong enough to yield useful results.

M. A Borel measure $\mu$ on a locally compact Hausdorff space $X$ will be said to be semi-regular if every Borel set in $X$ is inner regular with res
...
