The characteristic function of the random walk is

$$\phi(\theta) = \sum_{x \in R} P(0,x) e^{ix \cdot \theta}, \quad \theta \in E.$$

Thus $\phi(\theta)$ is nothing but a special kind of Fourier series, special in that its Fourier coefficients are non-negative and their sum over $R$ is

¹ The material of this section is well known. More detailed expositions are in [18], [23], [35], [73], and [84], for the one-dimensional case, and the extension to dimension $d \geq 2$ is nowhere difficult. For a deeper study of the theory of Fourier series,

one. The term "characteristic function" is customarily used in probability theory for Fourier series, or for Fourier integrals of probability measures, which are of this special type.

Many important properties of characteristic functions are in fact general properties of Fourier series. After establishing the orthogonality of the exponential functions in P1, we shall record, in P2, a very weak form of Parseval's theorem, which in its usual strong form amounts to the assertion that the exponential functions form a complete orthonormal set. Then in P3 we shall derive the convolution and inversion theorems for Fourier series which are elementary as well as general. From that point on, most of this chapter will deal with special properties of characteristic functions (properties which do depend on the non-negativity of the coefficients). Only in section 9, P9.1, will we return to a general principle, the Riemann Lebesgue Lemma, which will find important applications in several later chapters.

Our first task is to set up convenient notation for integration on $E$, and in particular on the cube $C$ in $E$ with center at the origin and sides of length $2\pi$.