If $\mathbf{G}$ is a finite group of order $g$, then

$$g = \sum_{\mathbf{A} \subset \mathbf{G}} \text{Ind}_{\mathbf{A}}^{\mathbf{G}}(\theta_{\mathbf{A}}),$$

where $\mathbf{A}$ runs through all the cyclic subgroups of $\mathbf{G}$.

(In this formula, the letter $g$ denotes the constant function equal to $g$.)

Put $\theta'_{\mathbf{A}} = \text{Ind}_{\mathbf{A}}^{\mathbf{G}}(\theta_{\mathbf{A}})$

The induction hypothesis gives $\theta_B \in \mathbb{R}(B)$ for $B \neq A$, hence $\text{Ind}_B^A(\theta_B)$ belongs to $\mathbb{R}(A)$; on the other hand, it is clear that $a \in \mathbb{R}(A)$ and so it follows that $\theta_A$ belongs to $\mathbb{R}(A)$.

Application to the proof of (i) $\Rightarrow$ (ii)

First observe that, if $A'$ is contained in a conjugate of $A$, the image of $\text{Ind}_A^G$ is contained in that of $\text{Ind}_A^G$. Hence we can assume that $X$ is the family of all cyclic subgroups of $G$. Propositions 27 and 28 then show that

$$g = \sum_{A \in X} \text{Ind}_A^G(\theta_A), \quad \text{with} \quad \theta_A \in \mathbb{R}(A).$$

Thus the element $g$ belongs to the image of $\text{Ind}$. Since this image is an ideal of $\mathbb{R}(G)$, cf. 9.1, it contains every element of the form $g\chi$, with $\chi \in \mathbb{R}(G)$, which proves (ii') (and even more, since we have an explicit denominator viz. the order of $G$).

Exercise

9.8. If $A$ is cyclic of order $a$, put $\lambda_A = \varphi(a)r_A - \theta_A$, where $\varphi(a)$ is the number of generators of $A$, and $r_a$ is the character of the regular representation. Show that $\lambda_A$ is a character of $A$ orthogonal to the unit character [apply ex. 9.1]. Show that, if $A$ runs over the set of cyclic subgroups of a group $G$ of order $g$, we have

$$\sum_{A \subset G} \text{Ind}_A^G(\lambda_A) = g(r_G - 1),$$

where $r_G$ is the character of the regular representation of $G$ [use prop. 27].

[Application (Aramata–Brauer): Let $F$ be a finite extension of

CHAPTER 10
A theorem of Brauer

In sections 10.1 through 10.4 the letter $p$ denotes a prime number.

10.1 $p$-regular elements; $p$-elementary subgroups

Let $x$ be an element of a finite group $G$. We say that $x$ is a $p$-element (or is $p$-unipotent) if $x$ has order a power of $p$; we say that $x$ is a $p'$-element (or is $p$-regular) if its order is prime to $p$.

Each $x \in G$ can be written in a unique way $x = x_u x_r$ where $x_u$ is $p$-unipotent, $x_r$ is $p$-regular, and $x_u$ and $x_r$ commute; moreover, $x_u$ and $x_r$ are powers of $x$. This can be seen by decomposing the cyclic subgroup generated by $x$ as a direct product of its $p$-component and its $p'$-component. The element $x_u(\text{resp. } x_r)$ is called the $p$-component (resp. the $p'$-component) of $x$.

A group $H$ is said to be $p$-elementary if it is the direct product of a cyclic group $C$ of order prime to $p$ with a $p$-group $P$. Such a group is nilpotent and its decomposition $C \times P$ is unique: $C$ is the set of $p'$-elements of $H$, and $P$ is the set of $p$-elements.

Let $x$ be a $p'$-element of a finite group $G$, let $C$ be the cyclic subgroup generated by $x$, and let $Z(x)$ be the centralizer of $x$ (the set of all $s \in G$ such that $sx = xs$). If $P$ is a Sylow $p$-subgroup of $Z(x)$, the group $H = C \cdot P$ is a $p$-elementary subgroup of $G$, which is said to be associated with $x$; it is unique up to conjugation in $Z(x
