If a random walk satisfies conditions (a) through (d) of P1, then for any finite subset $A$ of $R$

(1) $\lim_{|z| \to \infty} |x| H_A(x,y) = \frac{1}{2\pi\sigma^2} E_A^*(y), \quad \lim_{|z| \to \infty} |x| H_A(x) = \frac{C(A)}{2\pi\sigma^2},$

and

(2) $\lim_{|z| \to \infty} \frac{H_A(x,y)}{H_A(x)} = \frac{E_A^*(y)}{C(A)}$.

Observe that part (2) is a far weaker statement than (1). It does not depend at all on the full strength of P1, but will hold whenever the Green function has the property

$$\lim_{|z| \to \infty} \frac{G(x,y)}{G(x,0)} = 1, \quad y \in R.$$

E1 It was observed by Ciesielski and Taylor ([14], 1962) that two interesting random variables associated with the Brownian motion process have the same probability distribution: the time until $d$-dimensional Brownian motion first leaves the unit sphere has the same distribution as the total time spent by $(d + 2)$-dimensional Brownian motion in the unit sphere. (This makes sense, Brownian motion in dimension $d + 2 \geq 3$ being transient. Incidentally both Brownian motions must start at the origin, for the theorem to hold.)

We shall take the case $d = 1$, and use P1 to prove an analogous theorem for random walk. For one-dimensional random walk, let $T_n$ denote the first time outside the interval $[-n,n]$. When the random walk has mean 0 and finite variance $\sigma^2$, and starts at the origin, it was shown in T23.2 that

(1) $\lim_{n \to \infty} P_0 \

so that $N_r$ is the total time spent in the sphere $[x \mid |x| \leq r]$. ($N_r$ is finite, since the random walk is transient.) We shall show that

(2) $$\lim_{r \to \infty} P_0 \left[ N_r > \frac{r^2 x}{\sigma^2} \right] = 1 - F(x),$$

with $\sigma^2$ as defined in P1, and $F(x)$ the same distribution function as in equation (1) above.

The proof of (1) in section 23 was carried out by the method of moments. Referring to the justification given there, it will therefore suffice to prove that for $p \geq 1$

(3) $$\lim_{r \to \infty} E_0 \left[ \left( \frac{\sigma^2}{r^2} N_r \right)^p \right] = p! \frac{\pi}{2} \left( \frac{8}{\pi^2} \right)^{p+1} \sum_{k=0}^{\infty} \frac{(-1)^k}{(2k+1)^{2p+1}},$$

these limits being the moments of $F(x)$, given in P23.3. The main idea of the proof of (3) will be clear if we consider the cases $p = 1$ and $p = 2$.

Letting $p = 1$,

(4) $$E_0 [N_r] = E_0 \left[ \sum_{k=0}^{\infty} \chi_r(x_k) \right] = E_0 \left[ \sum_{x \mid |x| \leq r} \sum_{k=0}^{\infty} \delta(x, x_k) \right]$$

$$= \sum_{x \mid |x| \leq r} \sum_{k=0}^{\infty} P_k(0,x) = \sum_{x \mid |x| \leq r} G(0,x).$$

Using P1 we obtain, asymptotically as $r \to \infty$,

(5) $$E_0 [N_r] \sim \frac{1}{2\pi\sigma^2} \sum_{x \mid |

The dominant term in (6) is of course the one of order $r^4$, and the method by which it was derived generalizes, to give for arbitrary $p \geq 1$,

$$E_0[(N_r)^p] \sim p! \sum_{|x_1| \leq r} \dots \sum_{|x_p| \leq r} G(0,x_1)G(x_1,x_2) \dots G(x_{p-1},x_p)$$

$$\sim p!\left(\frac{r^2}{2\pi\sigma^2}\right)^p \int_{|\alpha_1| \leq 1} \dots \int_{|\alpha_p| \leq 1} \frac{d\alpha_1}{|\alpha_1|} \frac{d\alpha_2}{|\alpha_2 - \alpha_1|} \dots \frac{d\alpha_p}{|\alpha_p-1 - \alpha_p|}.$$

Let us denote the Newtonian potential kernel by $K(\alpha,\beta)$, for $\alpha,\beta$ in the unit sphere of three-dimensional Euclidean space $E$. Then

$$|\alpha - \beta|^{-1} = K(\alpha,\beta) = K_1(\alpha,\beta), K_{p+1}(\alpha,\beta) = \int_{|\alpha| \leq 1} K_p(\alpha,\gamma)K(\gamma,\beta) d\gamma,$$

are the iterates of the kernel $K$, restricted to the unit sphere, and equation (7) may be written in the form

$$E_0[N_r^p] \sim p!\left(\frac{r^2}{2\pi\sigma^2}\right)^p \int_{|\alpha| \leq 1} K_p(0,\alpha) d\alpha.$$

Comparing equation (8) with equation (3), which we are striving to prove, it is seen that (3) is equivalent to

$$\int_{|\alpha| \leq 1} K_p(0,\alpha) d\alpha = \frac{4}{\pi}\left(\frac{16}{\pi}\right)^p \sum_{n=0}^{\infty} \frac{(-1)^n}{(2n+1)^{

and from $|\beta| > |\alpha| = r$. The second part is conveniently evaluated at $|\alpha| = 0$ (since it is constant!) and in this way one gets

(10) $$Kf(\alpha) = \int_{|\beta| \leq 1} \frac{f(\beta)}{|\alpha - \beta|} d\beta$$
$$= \frac{4\pi}{r} \int_{0}^{r} \tilde{f}(\rho) \rho^2 d\rho + 4\pi \int_{r}^{1} \tilde{f}(\rho) \rho d\rho,$$

if $|\alpha| = r$ and $f(\beta) = \tilde{f}(\rho)$ when $|\beta| = \rho$.

Suppose now that $f$ is a spherically symmetric eigenfunction of $K$, i.e., that $f = \lambda Kf$ on the unit ball, for some $\lambda \neq 0$. It is convenient to write $r\tilde{f}(r) = \phi(r)$, for then it follows from equation (10) that $f = \lambda Kf$ assumes the simple form

(11) $$\phi(r) = 4\pi \lambda \int_{0}^{1} \phi(\rho) \min(\rho,r) d\rho, \quad 0 \leq r \leq 1.$$

In other words we are looking for the eigenfunctions of the integral operator $4\pi \min(\rho,r)$ which has every desirable property (it is symmetric, positive, and completely continuous; hence its eigenfunctions form a complete orthonormal set, and Mercer's theorem applies). Differentiating (11) one gets

(12) $$\phi''(r) + 4\pi \lambda \phi(r) = 0, \quad 0 \leq r \leq 1,$$

and the boundary conditions are easily seen to be

(13) $$\phi(0) = \phi'(1) = 0.$$

The solutions of (12) and (13) are

(14) $$\lambda_n = \frac{\pi}{16} (2n + 1)^2, \quad \phi_n(r) = \sqrt{2} \

Hence $\psi_p$ is the result of applying the $(p - 1)$st iterate of $4\pi \min (\rho, r)$ to the function $\psi_1(r) \equiv 1$. By Mercer's theorem (see P21.3)

$$\psi_p(r) = \sum_{n=0}^{\infty} \int_0^1 \frac{\phi_n(r)\phi_n(\rho)}{(\lambda_n)^{p-1}} d\rho.$$

Finally,

$$\int_{|\alpha| \leq 1} K_p(0, \alpha) d\alpha = 4\pi \int_0^1 \psi_p(r) r dr$$

$$= \sum_{n=0}^{\infty} \frac{4\pi}{(\lambda_n)^{p-1}} \int_0^1 \phi_n(r) r dr \int_0^1 \phi_n(\rho) d\rho,$$

and straightforward computation using (14) shows that (9) is true. That proves the limit theorem in equation (2) for the time $N_r$ spent in a sphere of radius $r$ by the three-dimensional random walk.

A still deeper application of P1 yields a characterization of the infinite transient sets (all finite sets are of course transient). The following criterion (for simple random walk) was recently discovered (1959) by Itô and McKean [46].