An $F$-vector bundle is called a real vector bundle if $F = R$, a complex vector bundle if $F = C$, and a quaternionic vector bundle if $F = H$. The $U$-isomorphism $h: U \times F^k \rightarrow p^{-1}(U)$ is called a local coordinate chart of $\xi$.

Examples 2(2.1), 2(2.5), and 2(2.6) admit the structure of a vector bundle in a natural way.

1.2 Example. The $k$-dimensional product bundle over a space $B$ is the bundle $(B \times F^k, p, B)$ with the vector space structure of $F^k$ defining the vector space structure on $b \times F^k = p^{-1}(b)$ for $b \in B$. The local triviality condition is realized by letting $U = B$ and $h = 1$.

1.3 Example. The tangent bundle $\tau(S^n)$ has a natural real vector space structure on each fibre since it is a subspace of $\mathbf{R}^{n+1}$. In the quotient bundle $\tau(RP^n)$ there is a vector space structure on each fibre. As for local triviality, let $U_i$ be the open subset of $x \in S^n$ with $x_i \neq 0, 0 \leq i \leq n$, and let $u_i: \mathbf{R}^n \rightarrow \mathbf{R}^{n+1}$ be the linear injection $u_i(x_1, \ldots, x_n) = (x_1, \ldots, x_i, 0, x_{i+1}, \ldots, x_n)$. Then $h_i: U_i \times \mathbf{R}^n \rightarrow p^{-1}(U_i) \subset E(\tau(S^n))$, where $h_i(b, x) = (b, v_b(u_i(x))$ [see 2(4.6)] has the desired properties. Also, this construction proves that $\tau(RP^n)$ is locally trivial.

1.4 Example. The function $\pi: G_k(F^m) \times F^m \rightarrow F^m$, where $\pi(V, x)$ is the orthogonal projection of $x$ into $V$, is a map. For $H \subset \{1, 2, \ldots, m\}$, a subset of $k$ elements, we have a linear map $u_H: F^k \rightarrow F^m$ by placing 0 in each coordinate not in $H$. With these maps, we prove that $\gamma_k^m = (E, p, G_k(F^m))$ is locally trivial. Since $E$ is the subspace of
