If the $r$ relations (58) hold for the $k$ units $\varepsilon_1, \varepsilon_2, \ldots, \varepsilon_k$ with some real $\gamma_m$, which are not all zero, then $r$ such relations also hold with rational integers $\gamma_m$, which are not all zero.

Obviously it is enough to prove this for those units which are not roots of unity. Suppose we choose a number $q$ such that the $r$ equations among the units $\varepsilon_1, \varepsilon_2, \ldots, \varepsilon_{q-1}$

$$\sum_{m=1}^{q-1} \alpha_m \log|\varepsilon_m^{(i)}| = 0 \quad (i=1, \ldots, r)$$

hold only for $\alpha_1 = \cdots = \alpha_{q-1} = 0$ and on the other such that between the $q$ units such a system

$$\sum_{m=1}^{q} \beta_m \log|\varepsilon_m^{(i)}| = 0 \quad (i=1, 2, \ldots, r)$$

holds with real $\beta_1, \ldots, \beta_q$ not all vanishing. Thus $2 \leq q \leq k$, and by the assumption about $q$ we necessarily have $\beta_q \neq 0$ and the $q-1$ quotients $\beta_1/\beta_q, \ldots, \beta_{q-1}/\beta_q$ in (59) are uniquely determined. Lemma (b) will be proved once we show that these $q-1$ quotients $\beta_m/\beta_q$ ($m=1, 2, \

all have absolute value $< 1$, since for the corresponding $\eta$ we have

$$\left| \log |\eta^{(i)}| \right| \leq \sum_{m=1}^{q-1} \left| \log |\varepsilon_m^{(i)}| \right| \quad (i=1,2,\ldots,n)$$

and by Lemma (a) there can only be finitely many integers of the field with this property. Let $H$ be the number of distinct systems $\rho$ with $|\rho_i| \leq 1$. On the other hand, the set of all systems $(\rho_1, \ldots, \rho_{q-1})$ appearing in (61) has the property that along with $(\rho_1, \ldots, \rho_{q-1})$ the system

$$(N\rho_1 - n_1, N\rho_2 - n_2, \ldots, N\rho_{q-1} - n_{q-1}),$$

where $N, n_1, n_2, \ldots, n_{q-1}$ are arbitrary rational integers, also occurs in this set. Now for each $N$ the $n_1, \ldots, n_{q-1}$ can be chosen so that for all numbers $|N\rho_i - n_i| \leq \frac{1}{2}$ and for different values of $N$, if $\rho_1$ is irrational, the numbers $N\rho_1 - n_1$ always have different values. Thus, infinitely many systems $(\rho_1, \ldots, \rho_{q-1})$ are obtained, where all $|\rho_i| < 1$, contrary to what was proved above. Hence neither $\rho_1$ nor $\rho_2, \ldots, \rho_{q-1}$ can be irrational, so all $\alpha_m$ in (60) are rational, and the lemma is proved.

Moreover, we obtain at the same time, with respect to the denominators which may appear in the $\rho_m$, that there exists a fixed rational integer $M \neq 0$, which depends only on $\varepsilon_1, \ldots, \varepsilon_{q-1}$ but not on

Moreover, from (c) we have:
