Let $\epsilon_1 > 0$, $m$ and $A$ be given. Then there exist positive integers $k$ and $M$ such that

$$\left| \frac{q_n}{F_n} - 1 \right| \leq \epsilon_1 \quad \text{for all sufficiently large } n,$$

where

$$q_n = \mathbf{P}[\mathbf{T} = n, |\mathbf{S}_k| > A \text{ and } \mathbf{S}_{k+j} = \mathbf{S}_k \text{ for some } m \leq j \leq M].$$

Proof: Take $\epsilon$ in P6 to be $\epsilon = \epsilon_1^2$ and choose $M$ so that P6 holds. P6 implies that for every $\delta > 0$, and sufficiently large $n$,

$$\sum_{k=1}^{n-M} \mathbf{P}[\{|\mathbf{S}_k| \leq A \text{ or } \mathbf{S}_{k+j} \neq \mathbf{S}_k \text{ for } m \leq j \leq M\} \cap \{\mathbf{T} = n\}] \leq (\epsilon_1^2 + \delta)nF_n,$$

which shows that there are at least $\epsilon_1 n$ values of $k$ for which

$$\mathbf{P}[\{|\mathbf{S}_k| \leq A \text{ or } \mathbf{S}_{k+j} \neq \mathbf{S}_k \text{ for } m \leq j \leq M\} \cap \{\mathbf{T} = n\}] \leq \epsilon_1 F_n.$$

If we pick such a value of $k$ in the definition of $q_n$ (which depends on $k$), then

$$(1 - \epsilon_1)F_n \leq q_n \

according to T5.1, which is crucial for the proof. We choose $m$ so that

(1) $|U_{k+1} - U_k| \leq \frac{\epsilon_1}{4} U_k$ for $k \geq m$,

and $A$ so large that

(2) $P[|S_j| \geq A$ for some $j \leq M+1] \leq \frac{\epsilon_1}{4} \min_{m \leq k \leq M+1} U_k$.

To simplify the notation let

$P[S_{k+j} = a, S_{k+r} \neq 0$ for $r = 1, \ldots, j-1$ $|S_k = a| = c_{k,j}(a) = c_{k,j}$

$P[T = n-k-j; S_p \neq a$ for $p = 1, 2, \ldots, M-j$ $|S_0 = a| = d_{n-k,j}(a,M) = d_{n-k,j}^3$

Then, decomposing $q_n$ according to the possible values of $S_k$ and according to the last time $k+j$ when $S_{k+j} = S_k$,

$q_n = \sum_{|a| > A} P[S_k = a; T > k] \sum_{j=m}^{M} c_{k,j} d_{n-k,j}$.

A similar decomposition for $\tilde{q}_{n+1}$ yields

$\tilde{q}_{n+1} = \sum_{|a| > A} P[S_k = a; T > k] \sum_{j=m}^{M} c_{k,j+1} d_{n-k,j}$,

so that

(3) $q_n - \tilde{q}_{n+1} = \sum_{|a| > A} P[S_k = a; T > k] \sum_{j=m}^{M} (c_{k,j} - c_{k,j+1}) d_{n-k,j}$.

To estimate this difference observe that

$c_{k,j} = P[S_j = 0; S_r \neq -a$ for $r =

In the same way one proves

(5) $|c_{k,j+1} - U_{j+1}| \leq \frac{\epsilon_1}{4} U_j, \quad m \leq j \leq M.$

Combining (4) and (5), we have

$$|c_{k,j+1} - c_{k,j}| \leq \frac{\epsilon_1}{2} U_j + |U_{j+1} - U_j|,$$

and now one concludes from (1) that

$$|c_{k,j+1} - c_{k,j}| \leq \frac{3\epsilon_1}{4} U_j.$$

Using (4) again, we obtain

(6) $|c_{k,j+1} - c_{k,j}| \leq \frac{3\epsilon_1}{4} \left(1 - \frac{\epsilon_1}{4}\right)^{-1} c_{k,j} \leq \epsilon_1 c_{k,j},$$

at least if, as we may assume, $\epsilon_1$ is sufficiently small.

Applying (6) to equation (3) we have

$$|q_n - \tilde{q}_{n+1}| \leq \epsilon_1 \sum_{|a| > A} P[S_k = a; T > k] \sum_{j=m}^{M} c_{k,j} d_{n-k,j} = \epsilon_1 q_n,$$

which proves P8.

We are now ready to complete the proof of T2. By definition $\tilde{q}_{n+1} \leq F_{n+1}$, and so by P8 and P7,

$$F_{n+1} \geq \tilde{q}_{n+1} \geq (1 - \epsilon_1) q_n \geq (1 - \epsilon_1)^2 F_n$$

for large enough $n$, which amounts to saying that

$$\lim_{n \to \infty} \frac{F_{n+1}}{F_n} \geq 1.$$

But an obvious modification of P7 gives

$$\left| \frac{\tilde{q}_{n+1}}{F_{n+1}} - 1 \right| \leq \epsilon_1$$

so that

That implies

$$\lim_{n \to \infty} \frac{F_{n+1}}{F_n} \leq 1,$$

which completes the proof of T2. In view of the remarks preceding P5, we have also completed the proof of T1.

Remark: One of the possible extensions of T1 was mentioned in Chapter III. It concerns the limit of the ratios

$$\frac{P_z[T_B > n]}{P_0[T > n]},$$ as $n \to \infty$.

The step from T1 to the theorem (proved in [60]) that these ratios have a limit, as $n \to \infty$, for every finite set $B$, requires considerable effort. As the discussion at the end of section 16 might lead one to expect, the difficulty consists in showing that the ratios $R_n/R_{2n}$ are bounded for every recurrent random walk. This is done in [60] by using very delicate estimates concerning the dispersion function of P. Lévy ([71], section 16).

Other aspects of the asymptotic behavior of the sequences $R_n, U_n,$ and $F_n$ are still shrouded in mystery, giving rise to challenging conjectures. Kesten has shown ([61]) that every strongly aperiodic recurrent one-dimensional random walk in the domain of attraction of a symmetric stable law (i.e., satisfying

$$0 < \lim_{\theta \to 0} |\theta|^{-\alpha}[1 - \phi(\theta)] = Q < \infty$$

for some $\alpha$, $1 \leq \alpha \leq 2)$ has the property that

(1) $$\lim_{n \to \infty} \frac{1}{F_n} \sum_{k=0}^{n} F_k F_{n-k} = 2.$$

He conjectures that (1) holds for every strongly aperiodic recurrent random walk. This conjecture is related, in an obvious way, to the random variables

$$T_k = \text{time of the } k^{\text{th}} \text{ return to } 0.$$

Equation (1) simply states that $P_0[T_2 = n] / P_0[T_1 = n]$ tends to 2 as $n \to \infty$,

Problems

1. For one-dimensional aperiodic recurrent random walk with absolute moment of order $3 + \delta$ for some $\delta > 0$, show that

$$\lim_{x \to \infty} \left[ a(x) - \frac{|x|}{\sigma^2} \right]$$

exists and is finite. Is this true if only $\sigma^2$ is finite? (To obtain a sharp result, use problem 2 in Chapter II.)

2. Here and in problem 3 the random walk is one dimensional and aperiodic, with a characteristic function $\phi(\theta)$ such that

$$0 < \lim_{\theta \to 0} \frac{1 - \phi(\theta)}{|\theta|^\alpha} = Q < \infty$$

for some $\alpha$, $1 \leq \alpha \leq 2$. Show that all such random walks are recurrent. Prove that

$$\lim_{|x| \to \infty} P_0[T_{-x} < T_x] = 1/2,$$

where $T_x$ is the time of the first visit to $x$.

3. Continuation. Show that

$$\lim_{|x| \to \infty} P_0[T_x < T_{2x}] = 2^{\alpha-2}.$$

4. Extend T32.2 by showing that

$$\lim_{n \to \infty} \frac{F_{n+1}}{F_n} = 1$$

for every strongly aperiodic recurrent random walk in the plane.

5. Here and in the next problem the random walk is one dimensional and aperiodic, with mean 0 and $\sigma^2 < \infty$. Use P32.3 to conclude that the ratios $R_n/R_{2n}$ are bounded in $n$. Then use the discussion at the end of Chapter III to prove that

$$\lim_{n \to \infty} \frac{P_z[T_B > n]}{P_0[T > n]} = \lim_{y \to +\infty} g_B(x,y) = \frac{1}{2} \left[ \lim_{y \to +\infty} g_B(x,y) + \lim_{y \to -\infty} g_B(x,y) \right]$$

for

where $x \neq 0$ is an arbitrary point in $R$ (but not the origin). Show that either $f(x) \equiv 0$ for $x \neq 0$ or $f(x) > 0$ for all $x \neq 0$, and characterize those random walks which give $f(x) \equiv 0$.

7. The mean square distance of a random walk $x_n$ from the origin, subject to the condition of no return to the origin in time $n$, is

$$D_n = \mathbf{E}_0[|x_n|^2 |\mathbf{T} > n] = \frac{1}{R_n} \mathbf{E}_0[|x_n|^2; \mathbf{T} > n].$$

Suppose that the random walk is genuinely $d$-dimensional, with mean vector zero and second moment $m_2 = \mathbf{E}_0[|x_1|^2] < \infty$. When the dimension $d = 1$, prove that

$$D_n \sim 2nm_2 = 2\mathbf{E}_0[|x_n|^2] \text{ as } n \to \infty,$$

whereas for dimension $d \geq 2$

$$D_n \sim nm_2 = \mathbf{E}_0[|x_n|^2] \text{ as } n \to \infty.$$

Hint: To obtain these asymptotic relations, first derive the identity

$$\mathbf{E}_0[|x_n|^2; \mathbf{T} > n] = (R_0 + R_1 + \cdots + R_{n-1})m_2, \quad n \geq 1.$$

8. Prove that the potential kernel $A(x,y)$ of a recurrent random walk determines the transition function uniquely.

Hint: In the spirit of problem 13, Chapter VI, show that for every subset $B \subset R$, $\Pi_B(x,y)$ is determined by $A(x,y)$. This follows from T11.1 and T30.2 in all cases except for left-, or right-continuous random walk. (But even then $A(x,y)$ does determine $\Pi_B(x,y)$, according to the discussion

10. For still another characterization of capacity define the energy dissipated by a finite set $A$ (or the expected area swept out by the set $A$) as

$$E_n(A) = \sum_{x \in R} P_x[T_A \leq n].$$

Investigate whether $E_n(A) - E_n(B)$ may be normalized appropriately so as to approximate $C(A) - C(B)$ for arbitrary recurrent random walk.

Hint: Consider first the asymptotic Abel sums, showing that

$$\sum_{n=0}^{\infty} t^n [E_n(A) - E_n(\{0\})] \sim \left[ \sum_{n=0}^{\infty} R_n t^n \right]^2 C(A) \text{ as } t \neq 1.$$

Here, as usual, $R_n = P_0[T_0 > n]$. Conclude that

$$\lim_{n \to \infty} \frac{E_n(A) - E_n(B)}{\sum_{k=0}^{n} R_k R_{n-k}} = C(A) - C(B)$$

whenever this limit exists. (S. Port has shown [S23] that it exists for arbitrary recurrent random walk.)

11. Prove, using the properties of $a(x)$, that for an arbitrary recurrent random walk the expected number of distinct points visited between successive visits to zero is always infinite.

12. Prove that the potential kernel of arbitrary two-dimensional recurrent random walk satisfies

(i) $$\lim_{|x| \to \infty} a(x) = \infty.$$

13. Continuation. Prove that (i) also holds in one dimension when $\sigma^2 < \infty$. However, when $\sigma^2 = \infty$, show that either (i) holds, or

(ii) $$\lim_{x \to +\infty} a(x) = M < \infty, \lim_{x \to -\infty} a(x) = +\infty,$$

or

(iii) $$\lim_{x \to +\infty} a(x) = +\infty, \lim_{x \to -\infty} a(x) = M < \infty.$$

Note: The exact criteria for this classification are still unknown.

1. Ahlfors, L. V., Complex analysis, McGraw-Hill Book Co., Inc., New York, 1953.
2. Baxter, G., An analytic approach to finite fluctuation problems in probability, *J. d'Analyse Math.* 9, 31–70, 1961.
3. Baxter, G., A norm inequality for a “finite-section” Wiener-Hopf equation, *Ill. J. Math.* 7, 97–103, 1963.
4. Blackwell, D., Extension of a renewal theorem. *Pacific J. Math.* 3, 315–320, 1953.
5. Bochner, S., Lectures on Fourier integrals, Princeton University Press, Princeton, N.J., 1959.
6. Borel, E., Les probabilités dénombrables et leurs applications arithmétiques, *Rend. Circ. Mat. Palermo* 27, 247–271, 1909.
7. Brelot, M., Éléments de la théorie classique du potentiel, Les cours de Sorbonne, Paris, 1959.
8. Choquet, G., and J. Deny, Sur l'equation $\mu = \mu * \sigma$, *Comptes Rendus Ac. Sc. Paris* 250, 799–801, 1960.
9. Chung, K. L., Markov chains with stationary transition probabilities, J. Springer, Berlin, 1960.
10. Chung, K. L., On the renewal theorem in higher dimensions, *Skand. Aktuarietidskrift* 35, 188–194, 1952.
11. Chung, K. L., and P. Erdös, Probability limit theorems assuming only the first moment, *Mem. Am. Math. Soc.* 6, 1951.
12. Chung, K. L., and W. H. J. Fuchs, On the distribution of values of sums of random variables

17. Cox, D. R., and W. L. Smith, Queues, Methuen & Co., London, 1961.
18. Cramér, H., Mathematical methods of statistics, Princeton University Press, Princeton, N.J., 1946.
19. Darling, D. A., The maximum of sums of stable random variables, Trans. Am. Math. Soc. 83, 164–169, 1956.
20. Darling, D. A., and M. Kac, On occupation times for Markoff processes, Trans. Am. Math. Soc. 84, 444–458, 1957.
21. Derman, C., A solution to a set of fundamental equations in Markov chains, Proc. Am. Math. Soc. 5, 332–334, 1954.
22. Donsker, M., An invariance principle for certain probability limit theorems, Mem. Am. Math. Soc. 6, 1951.
23. Doob, J. L., Stochastic processes, John Wiley and Sons., Inc., New York, 1953.
24. Doob, J. L., Discrete potential theory and boundaries, J. Math. and Mech. 8, 433–458, 1959.
25. Doob, J. L., J. L. Snell and R. E. Williamson, Application of boundary theory to sums of independent random variables, Contr. to Probability and Statistics (Hotelling Anniversary Volume) Stanford University Press, Stanford, Calif., pp. 182–197, 1960.
26. Dudley, R. M., Random walk on Abelian groups, Proc. Am. Math. Soc. 13, 447–450, 1962.
27. Dvoretzky, A., and P. Erdös, Some problems on random walk in space, Second Berkeley Symp. on Statistics and Probability, pp. 353–368, 1951.
28. Erdös, P., A problem

37. Halmos, P. R., Measure theory, D. Van Nostrand Co., Inc., Princeton, N.J., 1950.
38. Halmos, P. R., Finite-dimensional vector spaces, D. Van Nostrand Co. Inc., Princeton, N.J., 1958.
39. Hardy, G. H., Divergent Series, Clarendon Press, Oxford, England, 1949.
40. Harris, T. E., Branching processes, J. Springer, Berlin, 1963.
41. Hausdorff, F. Summationsmethoden und Momentfolgen, I, II, Math. Zeitschrift 9, 74–109 and 280–299, 1921.
42. Hewitt, E., and L. J. Savage, Symmetric measures on Cartesian products, Trans. Am. Math. Soc. 80, 470–501, 1955.
43. Hoeffding, W., On sequences of sums of independent random vectors, Fourth Berkeley Symp. on Statistics and Probability Vol. II, pp. 213–226, 1961.
44. Hunt, G. A., Some theorems on Brownian motion, Trans. Am. Math. Soc. 81, 294–319, 1956.
45. Hunt, G. A., Markoff chains and Martin boundaries, Ill. J. Math. 4, 313–340, 1960.
46. Itô, K., and H. P. McKean, Jr., Potentials and the random walk, Ill. J. Math. 4, 119–132, 1960.
47. Itô, K., and H. P. McKean, Jr., Diffusion processes and their sample paths, J. Springer, Berlin, 1965.
48. Kac, M., Random walk and the theory of Brownian motion, Am. Math. Monthly 54, 369–391, 1947.
4

59. Kesten, H., Random walks with absorbing barriers and Toeplitz forms, *Ill. J. Math.* 5, 267-290, 1961.

60. Kesten, H., and F. Spitzer, Ratio theorems for random walk, *Journal d'Analyse Math.* 11, 285-322, 1963.

61. Kesten, H., Ratio theorems for random walk II, *Journal d'Analyse Math.* 11, 323-379, 1963.

62. Khinchin, A. I., Sur la loi des grands nombres, *Comptes Rendus Ac. Sci. Paris* 188, 477-479, 1929.

63. Kiefer, J., and J. Wolfowitz, On the characteristics of the general queueing process with applications to random walk, *Ann. Math. Stat.* 27, 147-161, 1956.

64. Kingman, J. F. C., and S. Orey, Ratio limit theorems for Markov chains, *Proc. Am. Math. Soc.*, 15, 907-910, 1964.

65. Kochen, S. B., and C. J. Stone, A note on the Borel-Cantelli problem *Ill. J. Math.*, to appear in 1964.

66. Kolmogorov, A. N., Grundbegriffe der Wahrscheinlichkeitsrechnung, J. Springer, Berlin, 1933.

67. Kolmogorov, A. N., Anfangsgrunde der Theorie der Markoffschen Ketten mit unendlich vielen möglichen Zuständen, *Mat. Sbornik N.S.* 1, 607-610, 1936.

68. König, H., Neuer Beweis eines klassischen Tauber-Satzes, *Archiv der Math.* 9, 278-281, 1960.

69

79. Nevanlinna, R. H., Eindeutige analytische Funktionen, 2nd ed., J. Springer, Berlin, 1953.

80. Orey, S., Potential kernels for recurrent Markov chains, *J. Math. Anal. and Appl.*, to appear in 1964.

81. Paley E. A. C., and N. Wiener, Fourier transforms in the complex domain, *Am. Math. Soc. Coll. Publ.*, XIX, 1934.

82. Pollaczek, F., Über eine Aufgabe der Wahrscheinlichkeitstheorie I-II, *Math. Zeitschrift* 32, 64-100 and 729-750, 1930.

83. Polya, G., Über eine Aufgabe der Wahrscheinlichkeitrechnung betreffend die Irrfahrt im Strassennetz, *Math. Ann.* 84, 149-160, 1921.

84. Rényi, A., Wahrscheinlichkeitrechnung, D.V.d. Wissenschaften, Berlin, 1962.

85. Rényi, A., Legendre polynomials and probability theory, *Ann. Univ. Sc. Budapestiniensis III-IV*, 247-251, 1960-61.

86. Riesz, F., Sur les fonctions surharmoniques et leur rapport à la theorie du potentiel 2, *Acta Math.* 54, 1930.

87. Riesz, F., and B. Sz.-Nagy, Lecons d'Analyse Fonctionelle, Kiadó, Budapest, 1952.

88. Rosén, B., On the asymptotic distribution of sums of independent identically distributed random variables, *Arkiv för Mat.* 4, 323-332, 1962.

89. Smith, W. L., A frequency function form of the central limit theorem. *Proc. Cambridge Phil. Soc.*, 49, 462-472,

99. Waerden, B. L. van der, Algebra II, 4th Ed., J. Springer, Berlin, 1959.

100. Watanabe, T., On the theory of Martin boundaries induced by countable Markov processes, Mem. Coll. Science, University Kyoto, Series A 33, 39–108, 1960.

101. Watanabe, T., Probabilistic methods in Hausdorff moment problem and Laplace-Stieltjes transform, J. Math. Soc. of Japan, 12, 192–206, 1960.

102. Watanabe, T., On a theorem of F. L. Spitzer and C. J. Stone, Proc. Japan Academy 37, 346–351, 1961.

103. Watson, G. N., A treatise on the theory of Bessel functions, 2nd Ed., Cambridge University Press, 1944.

104. Watson, G. N., Three triple integrals, Oxford Qu. J. of Math. 10, 266–276, 1939.

105. Widom, H., Toeplitz matrices, Math. Assoc. of America Studies in Mathematics, Vol. 3, 179–209, 1965.

106. Zygmund, A., Trigonometric Series, I, II, Cambridge University Press, 1959.

1. Breiman, L., Probability, Addison-Wesley, 1968.
2. Brunel, A. and D. Revuz, Marches Recurrentes au sense de Harris sur les groupes localement compactes I, Ann. Sc. Ecole Norm. Sup. 7, 273-310, 1974.
3. Bucy, R. S., Recurrent sets, Ann. Math. Stat. 36, 535-545, 1965.
4. Chung, Kai Lai, A course in probability theory, 2nd ed. Academic Press, 1974.
5. Darling, D. A. and P. Erdös, On the recurrence of a certain chain, Proc. Am. Math. Soc. 19, 336-338, 1968.
6. Doney, An analogue of the renewal theorem in higher dimensions, Proc. London Math. Soc. 16, 669-684, 1966.
7. Dym, H. and H. P. McKean, Fourier series and integrals, Academic Press, New York, 1972.
8. Dynkin E. B. and A. A. Yushkevich, Markov processes—theorems and problems, Plenum Press, New York, 1969.
9. Feller, W., An introduction to probability theory and its applications, Vol. II, 2nd ed. John Wiley and Sons, New York, 1971.
10. Flatto, L. and J. Pitt, Recurrence criteria for random walks on countable Abelian groups, III, J. Math. 18, 1-20, 1974.
11. Heyde, C. C., Revisits for transient random walk, Stoch. Proc. Appl. 1, 33-52, 1973.
12. Jain, N. C. and S. Orey, On the range of a random walk, Israel J. Math. 6, 373-380, 1968.
13. Jain,

18. Kesten, H., A ratio limit theorem for symmetric random walk, *J. d'Analyse Math.* 23, 199-213, 1970.

19. Kesten, H., Sums of independent random variables—without moment conditions, *Ann. Math. Stat.* 43, 701-732, 1972.

20. Kesten, H. and F. Spitzer, Random walk on countably infinite Abelian groups, *Acta Math.* 114, 237-265, 1965.

21. Ney, P. and F. Spitzer, The Martin boundary for random walk, *Trans. Am. Math. Soc.* 121, 116-132, 1966.

22. Ornstein, D. S., Random walks I and II, *Trans. Am. Math. Soc.* 138, 1-43; and 45-60, 1969.

23. Port, S. C., Limit theorems involving capacities for recurrent Markov chains, *J. Math. An. Appl.* 12, 555-569, 1965.

24. Port, S. C., Limit theorems involving capacities, *J. Math. Mech.* 15, 805-832, 1966.

25. Port, S. C. and C. J. Stone, Potential theory of random walks on Abelian groups, *Acta Math.* 122, 19-114, 1969.

26. Stone, C., On the potential operator for one dimensional recurrent random walks, *Trans. Am. Math. Soc.* 136, 413-426, 1969.

Abel's theorem, 199
Abelian groups, 92, 281
Absorption problem for simple random walk, 237
random walk with mean 0, $\sigma^2 < \infty$, 244
Actuarial science, 174
A. e. convergence, 24
Aperiodic random walk, 20, 67
Arc-sine law, 227, 233, 258
Area swept out by a set, 394

Bachelier, L., 270
Baxter, G., 174, 220, 271
Bernoulli random walk definition, 2
exponential bound, 45
Green function, 8, 12
regular functions, 131
Bernstein's estimate, 45
Bessel functions, 104, 235, 236
Bessel's inequality, 57
Beta function, 256
Biorthogonal system, 271
Birkhoff's ergodic theorem, 38, 53
Blackwell, D., 195, 282, 284
Borel, É., 32
Borel-Cantelli lemma, 317
Boundary, 327
Branching process, 234
Brownian motion, 40, 173, 219, 270, 312, 320

Cantor's diagonal process, 277, 347
Capacity definitions (transient random walk), 300, 303, 341
electrostatic, 40
inequalities, 304
logarithmic (recurrent random walk), 366, 393, 394
of finite sets, 40, 301
of infinite sets, 305
Capacitory potential, 300

Catalan's constant, 124
Cauchy distribution, 156
Central limit theorem, 64

Distribution function, 63
Domain of attraction, 391
Dominated convergence theorem, 25, 58
Doob, J. L., 192, 298, 327
Dudley, R. M., 95
Dvoretzky, A., 38

Eigenfunction expansion, 242
Eigenvalues of quadratic forms, 70 for simple random walk, 239 distribution of, 272
Elliptic integral, 103
Entrance probability, 290
Equilibrium charge for recurrent random walk, 146, 377 transient random walk, 300
Equilibrium potential for recurrent random walk, 146 transient random walk, 300
Erdős, P., 38, 41, 99, 232, 270
Ergodic theory, 32
Escape probability, 290
Euler's constant, 124, 127
Excessive function, 323
Expectation, 26
Exponential bound for Bernoulli sums, 45, 385, 387
Exponential regular function, 340
Extension theorem, 26
Exterior Fourier series, 179, 220

Factorization, 180
Fatou's lemma, 84
Favorable game, 217, 227
Fejér representation, 182
Feller, W., 18, 99, 195, 224, 225, 237, 288
Finite set capacity of, 301 energy dissipated by, 394 volume swept out by, 40, 341
Fluctuations, 218
Fourier series, 54
Fourier transform, 63
Fraction of points visited, 271
Friedrichs, K., 258
Fubini's theorem, 25

Function excessive, 32

quadrant, 157, 173
triangle, 172
asymptotic behavior, 293, 312, 359
Hitting time, 29, 106
of exterior of interval, 242, 244, 262
half-line, 189, 191, 195, 196
single point, 377
Hoeffding, W., 343
Hunt, G. A., 159, 327, 334

Ideal, 65
Images, method of, 154
Imbedded random walk, 257
Independent functions, 25
random variables, 27
Infinite transient set, 339
Inner function, 179, 220
product, 248
Integrable function, 25
Interior Fourier series, 179, 220
Interval absorption outside, 237
Invariance principle, 270
Inventory, 174
Isomorphism, 65
Isotropic random walk, 308
Itô, K., 173, 316, 321, 339

Kac, M., 159, 171, 231, 232, 237, 270, 272
Karamata's theorem, 225, 382
Katz, M., 232
Kemeny, J. G., 120, 343
Kemperman, J. H. B., 174, 185, 233
Kesten, H., 40, 255, 256, 333, 378, 391
Kninchin, A. I., 22
Kiefer, J., 209
Kolmogorov, A. N., 24, 32, 99
König, H.,

Mean of random walk, 21
Mean recurrence time, 99
Mean square distance, 393
Measurable function, 24
Measure theory, 24
Mercer's theorem, 242, 268, 315
Method of moments, 233, 263
Minimum principle, 373
Minimal regular functions, 340
Minimal solution of Poisson's equation, 296
Minkowski's lemma, 70
Mittag-Leffler distribution, 231
Module, 65
Moments, method of, 233, 263
Moment problem, 263, 338
Morera's theorem, 180

Nagy, B. Sz., 242
Newtonian potential kernel, 307, 314
Ney, P., 341
Normal distribution, 53

Occupation time problems, 231, 256
Orey, S., 46, 288
Ornstein, D., 23
Orthogonal polynomials, 247
Orthogonality of characters, 92
eigenfunctions, 241
exponentials, 55
polynomials, 247
Outer function, 179, 220

Parseval's identity, 56
Permutation cyclic, 384 of coordinates, 298
Persistent random walk, 7
Plus operator, 220
Poisson's equation, 136, 294, 367 minimal solution, 296
Poisson kernel, 185
Poisson process, compound, 235
Pollaczek, F., 174
Pollard, H., 99
Polya's theorem, 52

Population in branching process, 234
Positive partial sums, number of, 219
Potential kernel, 123 asymptotic behavior, 123, 124, 358, 392 determines

occupation time of, 53
Random variable, 26
expectation of, 26
Range of random walk, 35, 52, 342
strong law, 38
weak law, 35
Ratio ergodic theorem
strong, 40, 49
weak, 10
Rational numbers
random walk on, 95
Rayleigh, Lord, 104
Rectangle,
random walk restricted to, 270
Recurrence criteria, 23, 82, 83, 85
Recurrent random walk
definition, 7
existence of potential kernel, 343, 352
Recurrent set, 275, 296, 300
characterization of, 316, 321
Red (or green) points, 52, 272
Reflection principle, 154
Regular function, 130, 276, 294
for transient kernel, 323
integral representation for, 337, 341
nonexistence of, 329
Renewal theorem, 99, 100, 103, 201, 203, 282, 284, 288
Rényi, A., 224, 235, 237
Reproducing kernel, 250
Reversed random walk, 111
Riemann approximating sum, 88, 227, 261, 268
Riemann Lebesgue lemma, 85, 96, 127, 355
Riesz, F., 242, 324
Riesz decomposition
of excessive functions, 324, 326, 331, 337
Right continuous random walk, 21, 33, 289
see also left continuous random walk
Robin's constant, 147
Rosén, B., 199
Rouché's theorem, 186

Strongly aperiodic random walk, 42, 75
Subgroup, 65, 339
Superharmonic function, 323
Symmetric random walk, 73, 87, 169, 182, 192, 204, 223, 224
Szegö, G., 247

Täcklind, S., 217
Tauber’s theorem, 199
Taylor, J., 312
Temperature, 158
Theta function, 273
Three dimensional random walk
Green function, 103, 308
regular functions, 332
transient sets, 316, 321
Time dependent behavior, 159
Time of first visit to a finite set, 391, 393
a point, 377, 392
Trace of transition matrix, 272
Traffic, 174
Transient kernel, 322
Transient random walk, 7
Green function of, 274
Transient set, 275, 296, 300
characterization of, 316, 321
Transition function, 1

asymptotic behavior of, 72
Triangular lattice, 66
Two-dimensional recurrent random walk, 113
Type I and II random walk, 344

Van der Pol, B., 128
Vector module, 65
Vibrating string, 241

Wald’s lemma, 191
Watanabe, T., 271, 327, 334
Watson, G. N., 103
Weak convergence, 63
Weierstrass’ approximation theorem, 272
Weight function, 249
Whipple, F. J. W., 149, 150, 154
Whitman, W., 40, 53
Widom, H., 212
Wiener, N.,

Graduate Texts in Mathematics
(continued from page ii)

66 WATERHOUSE Introduction to Affine Group Schemes.
67 SERRE. Local Fields.
68 WEIDMANN Linear Operators in Hilbert Spaces
69 LANG. Cyclotomic Fields II.
70 MASSEY Singular Homology Theory.
71 FARKAS/KRA. Riemann Surfaces. 2nd ed.
72 STILLWELL Classical Topology and Combinatorial Group Theory 2nd ed
73 HUNGERFORD. Algebra
74 DAVENPORT Multiplicative Number Theory 3rd ed.
75 HOCHSCHILD. Basic Theory of Algebraic Groups and Lie Algebras
76 IITAKA. Algebraic Geometry.
77 HECKE. Lectures on the Theory of Algebraic Numbers
78 BURRIS/SANKAPPANAVAR. A Course in Universal Algebra.
79 WALTERS. An Introduction to Ergodic Theory.
80 ROBINSON. A Course in the Theory of Groups. 2nd ed.
81 FORSTER. Lectures on Riemann Surfaces.
82 BOTT/TU Differential Forms in Algebraic Topology.
83 WASHINGTON. Introduction to Cyclotomic Fields 2nd ed.
84 IRELAND/ROSEN A Classical Introduction to Modern Number Theory. 2nd ed.
85 EDWARDS Fourier Series. Vol. II. 2nd ed
86 VAN LINT. Introduction to Coding Theory. 2nd ed
87 BROWN. Cohomology of Groups.
88 PIERCE. Associative Algebras.
89 LANG. Introduction to Algebraic and Abelian Functions 2nd ed
90 BRØNDSTED An Introduction to Convex Polytopes
91 BEARDON On the Geometry of Discrete Groups.
92 DIESTEL. Sequences and Series in Banach Spaces.
93 DUBROVIN/FOMENKO/NOVIKOV Modern Geometry—Methods and Applications. Part I. 2nd ed.
94 WARNER. Foundations of Differentiable Manifolds and Lie Groups.
95 SH

129 FULTON/HARRIS Representation Theory
A First Course
Readings in Mathematics
130 DODSON/POSTON. Tensor Geometry.
131 LAM. A First Course in Noncommutative Rings.
132 BEARDON. Iteration of Rational Functions
133 HARRIS. Algebraic Geometry: A First Course.
134 ROMAN. Coding and Information Theory
135 ROMAN. Advanced Linear Algebra.
136 ADKINS/WEINTRAUB. Algebra: An Approach via Module Theory.
137 AXLER/BOURDON/RAMEY Harmonic Function Theory. 2nd ed.
138 COHEN A Course in Computational Algebraic Number Theory.
139 BREDON. Topology and Geometry.
140 AUBIN Optima and Equilibria. An Introduction to Nonlinear Analysis.
141 BECKER/WEISPFENNING/KREDEL Gröbner Bases. A Computational Approach to Commutative Algebra.
142 LANG. Real and Functional Analysis. 3rd ed.
143 DOOB. Measure Theory.
144 DENNIS/FARB. Noncommutative Algebra.
145 VICK. Homology Theory An Introduction to Algebraic Topology 2nd ed
146 BRIDGES Computability: A Mathematical Sketchbook.
147 ROSENBERG. Algebraic $K$-Theory and Its Applications.
148 ROTMAN. An Introduction to the Theory of Groups. 4th ed.
149 RATCLIFFE. Foundations of Hyperbolic Manifolds.
150 EISENBUD. Commutative Algebra with a View Toward Algebraic Geometry
151 SILVERMAN Advanced Topics in the Arithmetic of Elliptic Curves.
152 ZIEGLER. Lectures on Polytopes.
153 FULTON. Algebraic Topology A First Course.
154 BROWN/PEARCY An Introduction to Analysis.
155 KASSEL. Quantum Groups.
156 KECHRIS. Classical Descriptive Set Theory.
157 MALLI

195 NATHANSON Elementary Methods in Number Theory
196 OSBORNE Basic Homological Algebra
197 EISENBUD/HARRIS. The Geometry of Schemes.
198 ROBERT A Course in $p$-adic Analysis
199 HEDENMALM/KORENBLUM/ZHU Theory of Bergman Spaces
200 BAO/CHERN/SHEN. An Introduction to Riemann–Finsler Geometry
201 HINDRY/SILVERMAN. Diophantine Geometry An Introduction.

202 LEE Introduction to Topological Manifolds.
203 SAGAN The Symmetric Group Representations, Combinatorial Algorithms, and Symmetric Function. 2nd ed.
204 ESCOFIER Galois Theory
205 FÉLIX/HALPERIN/THOMAS Rational Homotopy Theory.
206 Murty Problems in Analytic Number Theory
Readings in Mathematics

This book is devoted to the study of random walk on the lattice points of ordinary Euclidean space. The theory of random walks, a central part of the theory of Markov chains, is connected with methods from harmonic analysis on the one hand and from potential theory on the other. Prerequisites for the book are some knowledge of two or three of the following areas: probability theory, real variables and measure, analytic functions, Fourier analysis, differential, and integral operators. More than 100 pages of examples and problems illustrate and clarify the presentation.

"... This book certainly covers almost all major topics in the theory of random walk. It will be invaluable to both pure and applied probabilists, as well as to many people in analysis. References for the methods and results involved are very good. A useful interdependence guide is given. Excellent choice is made of examples, which are mostly concerned with very concrete calculations. Each chapter contains complementary material in the form of remarks, examples and problems which are often themselves interesting theorems."

—T. Watanabe, Mathematical Reviews

ISBN 0-387-95154-7
www.springer-ny.com