If $(X, S)$ is a measurable space, and if $\mu$ and $\nu$ are $\sigma$-finite measures on $(X, S)$, then there exists a unique decomposition of $\nu$ into the sum of two measures $v_1$ and $v_2$ on $(X, S)$ such that $v_1 \ll \mu$ and $v_2 \perp \mu$. The decomposition $v = v_1 + v_2$ is called the Lebesgue decomposition of $\nu$ with respect to $\mu$.

Let $(X, S, \mu)$ be a measure space, and for each pair of sets $E_1, E_2$ in $S$ let us write $E_1 \sim E_2$ to indicate that $E_1$ and $E_2$ are almost equal $[\mu]$, i.e., that $\mu(E_1 \nabla E_2) = 0$. It is clear that $\sim$ is an equivalence relation on $S$. We shall denote by $[E]$ the equivalence class of a measurable set $E$ with respect to the relation $\sim$, and denote by $\dot{S}$ the collection of all equivalence classes into which $S$ is thus partitioned. Note that if $E_1 \sim E_2$, then $\mu(E_1) = \mu(E_2)$. Thus a function $\dot{\mu}$ is unambiguously defined on $\dot

(X, S, $\mu$). A measure space is said to be separable if its associated metric space is separable. (The completeness of the measure space $(X, S, \mu)$ has nothing to do with the completeness of its associated metric space; see Problem U.)

The terminology “measure ring” has an easily explained origin. The system $\dot{S}$ associated with a measure space $(X, S, \mu)$ is, in fact, a Boolean ring if $\wedge$ is interpreted as multiplication and $\nabla$ as addition. As was remarked in Chapter 6, such rings were studied initially in [63].

Example G. Let $(\mathbb{R}^n, S, \mu_n)$ be the measure space consisting of Lebesgue measure on the Lebesgue measurable sets in $\mathbb{R}^n$, and let $(\mathbb{R}^n, B, \mu_n | \mathbf{B})$ be Lebesgue–Borel measure on $\mathbb{R}^n$. Then each equivalence class in $(\dot{S}, \dot{\mu}_n)$ contains exactly one equivalence class in the measure ring $(\dot{B}, (\mu_n | \mathbf{B}))$ (Prob. 8H). Thus the measure rings, as well as the associated metric spaces, of these two measures spaces are virtually identical. More generally, the measure ring, and the associated metric space of any measure space $(X, S, \mu)$ may be identified with the measure ring and associated metric space, respectively, of the completion of $(X, S, \mu)$ (Prob. 8Q).

Example H. Let $(X, S, \mu)$ be a measure space, and let $\mathbf{R}$ be any ring of measurable sets of finite measure with respect to $\mu$ that generates $\mathbf{S}$ as a $\sigma$-ring. Then, according to Problem 8M, $\dot{R} = \{[A] \in \dot{S} : A \in \mathbf{R}\}$ is dense in the metric space $(\dot{S}_{\mathcal{F}}, \rho)$ associated with $(X, S, \mu)$. Thus, for instance, the set of equivalence classes of all finite unions of (half-open) cells in $\mathbb{R}^n$ is dense in the metric space associated with Leb

Example I. For each fixed point $a$ in $\mathbb{R}^n$ let us write $T_a$ for the translation that carries each $x$ in $\mathbb{R}^n$ to $T_a(x) = x + a$, and if $E$ is a subset of $\mathbb{R}^n$ let us also write $E + a$ for $T_a(E)$. Since

$$(E + a) \nabla (F + a) = (E \nabla F) + a$$

for all subsets $E$ and $F$ and every point $a$, it is clear that the mapping $\dot{T}_a$ defined by $\dot{T}_a([E]) = [E + a]$ for each Lebesgue measurable set $E$ is an isometry on the metric space $(\dot{\mathbf{S}}_\mathcal{F}, \rho)$ associated with Lebesgue measure on $\mathbb{R}^n$.

Suppose now that $H$ is a half-open cell in $\mathbb{R}^n$:

$$H = [a_1, b_1) \times \cdots \times [a_n, b_n).$$

If $U$ is an open cell slightly larger than $H$, and $K$ a closed cell slightly smaller than $H$, then there is a neighborhood $V$ of the origin in $\mathbb{R}^n$ such that if $x \in V$, then $K \subset H + x \subset U$, and therefore such that $H \nabla (H + x) \subset U \setminus K$ for every $x$ in $V$. Thus for any given $\varepsilon > 0$ there exists a neighborhood $V$ of the origin such that $\rho([H], \dot{T}_x([H]) < \varepsilon$ for every $x$ in $V$. Consider next the ring $H_l$ of sets generated by all half-open cells of the form (5). If $A$ is an element of $H_l$, then $A$ is the union $H_1 \cup \cdots \cup H_k$ of such cells (Ex. 6D), and since

$$\rho([A], [A + x]) \leq \rho([H_1], [H_1 + x]) + \cdots + \rho([H_k], [H_k +

for every $x$ in $\mathbb{R}^n$. Thus the function $f_E(x) = \rho([E], \dot{T}_x([E]))$ is uniformly approximable by uniformly continuous functions of the form $f_A, A \in \mathbf{H}_l$, and it follows that $f_E$ is also uniformly continuous on $\mathbb{R}^n$.

It is in terms of measure rings that we define the notion of isomorphism appropriate to measure spaces.
