Let $A$ be a noetherian ring, $E$ a finite $A$-module, $F$ a submodule of $A$, and $m$ an ideal in $A$. There exists an integer $k$, depending only on $A$, $E$, $F$ and $m$, such that $m^n E \cap F = m^{n-k}(m^k E \cap F)$ for every $n \geq k$.

Proof. The fact that Theorem 4' implies Theorem 4 is clear. For proving Theorem 4' we introduce an indeterminate $X$, and consider the set $A'$ of polynomials $\sum_i m_i X^i$ with $m_i \in m^i$; this set is clearly a subring of $A[X]$, and even a noetherian ring, for, if $\{a_1, \ldots, a_q\}$ is a finite basis of the ideal $m$, we have $A' = A[a_1 X, \ldots, a_q X]$. We consider also the set $E'$ of formal sums $z_0 + z_1 X + \cdots + z_j X^j$ where $z_i \in m^i E$; it is an additive group for coefficientwise addition, and even an $A'$-module if we set $(m_i X^i)(z_j X^j) = m_i z_j X^{i+j}$ and extend this multiplication by linearity (it may be observed that $E'$ is isomorphic with the tensor product $A' \otimes E$ (Vol. I, Ch. III, §14), but we

B of A which is a finite A-module. Then, since $m^n B$ is the ideal $(mB)^n$ of B, the m-topology of B (B being considered as an A-module) coincides with the $(mB)$-topology of the ring B. Thus A, with its m-topology, is a topological subspace of B, when B is considered with its $(mB)$-topology.

It may be noticed that, if m and $m'$ are two ideals of a ring A for which there exist exponents a and b such that $m \supset m'^a$ and $m' \supset m^b$ (i.e., two ideals with the same radical, in the noetherian case), then the m-topology and the $m'$-topology coincide on every A-module.

Let A be a ring, m an ideal in A, and E an A-module. We suppose that A and E are Hausdorff spaces for their m-topologies, i.e., that $\bigcap_{n=0}^{\infty} m^n = (0)$ and that $\bigcap_{n=0}^{\infty} m^n E = (0)$. As metric spaces, A and E may be completed; call $\hat{A}$ and $\hat{E}$ their completions. The uniformly continuous mappings $(a, b) \rightarrow a + b, (x, y) \rightarrow x + y, (a, b) \rightarrow ab, (a, x) \rightarrow ax$ from $A \times A, E \times E, A \times A, A \times E$ into A, E, A, E, respectively, may be extended in a unique way, by continuity, to uniformly continuous mappings from $\hat{A} \times \hat{A}, \hat{E} \times \hat{E}, \hat{A} \times \hat{A}$ and $\hat{A} \times \hat{E}$ into $\hat{A}, \hat{E}, \hat{A}, \hat{E}$. We write these extended mappings additively and multiplicatively, as the old ones. Since algebraic identities are preserved by passage to the limit, these mappings define in $\hat{A}$

the right-hand side tends to 0 as $n$ tends to infinity. Hence $y = \sum_j b_j x_j$, and our assertion is proved.