Let $\mathcal{E}$ be a normed space with dual space $\mathcal{E}^*$, and let $j$ denote the natural embedding of $\mathcal{E}$ in the second dual $\mathcal{E}^{}$ (Prop. 15.6). The space $\mathcal{E}$ is said to be reflexive if $j$ maps $\mathcal{E}$ onto $\mathcal{E}^{}$, i.e., if the only bounded linear functionals on $\mathcal{E}^*$ are those defined by elements $x$ of $\mathcal{E}$ according to the formula

$$f \rightarrow f(x), \quad f \in \mathcal{E}^*.$$

If $\mathcal{E}$ is reflexive then $j$ is an isometric isomorphism between $\mathcal{E}$ and $\mathcal{E}^{}$ (Prop. 15.6), and it follows that $\mathcal{E}$ is necessarily complete (Prop. 12.7). A reflexive Banach space $\mathcal{E}$ may be viewed as being identical with its own second dual (that is, $\mathcal{E}$ and $\mathcal{E}^{}$ may be identified via the natural embedding $j$) so that $\mathcal{E}$ and $\mathcal{E}^*$ become the dual spaces of one another. Reflexive Banach spaces constitute a special, particularly well-behaved, class of Banach spaces.

Example A. Let $\mathcal{E}$ be a finite dimensional Banach space, and let $\{x_j\}_{j=1}^n$ be a basis for $\mathcal{E}$. For each $i=1, \ldots, n

linear functional $f_i$ on $\mathcal{E}$ such that $f_i(x_j) = \delta_{ij}, j = 1, \ldots, n$ (Ex. 2B), and it is easy to see that $\{f_i\}_{i=1}^n$ is a basis for $\mathcal{E}^*$. (If $f \in \mathcal{E}^*$ then $f(x_i) = \alpha_i, i = 1, \ldots, n$, if and only if $f = \sum_{i=1}^n \alpha_i f_i$. The basis $\{f_i\}_{i=1}^n$ is called the basis dual to the given basis $\{x_j\}_{j=1}^n$.) It follows that $\dim \mathcal{E}^* = n = \dim \mathcal{E}$. Hence, by the same token, $\dim \mathcal{E}^* = n$ also, and since the natural embedding $j$ of $\mathcal{E}$ into $\mathcal{E}^*$ has rank $n$ (Prob. 2G), it follows that $j$ is onto. Thus every finite dimensional Banach space is reflexive.

Example B. If $1 < p < +\infty$, and if we use the formula set forth in Example 14C to identify $(\ell_p)^*$ with $(\ell_q)$, where $q$ denotes the Hölder conjugate of $p$, then we must simultaneously identify $(\ell_q)^* = (\ell_p)^{}$ with $(\ell_p)$. It is not very difficult to check that under these identifications the natural embedding of $(\ell_p)$ in itself becomes the identity mapping on $(\ell_p)$. (We shall return to this point in Example H.) Thus $(\ell_p)$ is reflexive for $1 < p < +\infty$. On the other hand, the dual of $(\ell_1)$ may be identified with $(\ell_\infty)$ (Ex. 14B), and the latter is not a separable space (Ex. 11H), whence it follows that $(\ell_1)^{} = (\ell_\infty)^*$ is not separable either (Prob. 14R). Since $(\ell_1)$ itself is separable, this shows
