For an arbitrary set $X$ and an arbitrary family $\mathcal{E}$ of subsets of $X$, let $\mathcal{S}(\mathcal{E})$ denote the intersection of all $\sigma$-algebras of subsets of $X$ that contain $\mathcal{E}$. Clearly $\mathcal{S}(\mathcal{E})$ is a $\sigma$-algebra. Thus $\mathcal{S}(\mathcal{E})$ is the smallest $\sigma$-algebra of subsets of $X$ containing $\mathcal{E}$. If $X$ is a topological space, let $\mathcal{B}(X)$

(b) It is possible actually to construct a very large class of $\lambda$-measurable sets, the so-called analytic sets, which includes all Borel sets as well as $\epsilon$ other sets. The interested reader is referred to the discussions of analytic sets in S. Saks, Theory of the Integral [2nd Edition, Monografie Matematyczne, Warszawa-Lwów, 1937], Chapter III, and in W. Sierpiński, General Topology [2nd Edition, Univ. of Toronto Press, Toronto, 1956], Chapter VII.

(10.22) Exercise. (a) Let $X, a, E_a$, and $\varepsilon_a$ be as in (9.19). Prove that $M_{\varepsilon_a} = \mathcal{P}(X)$.

(b) Let $X$ be a locally compact Hausdorff space, let $\{x_n\}_{n=1}^{\infty}$ be a countable [possibly finite] subset of $X$, and let $(\alpha_n)_{n=1}^{\infty}$ be a sequence of positive numbers such that $\sum_{n=1}^{\infty} \alpha_n < \infty$. Let $I(\varphi) = \sum_{n=1}^{\infty} \alpha_n \varphi(x_n)$ for all $\varphi \in \mathfrak{C}_{00}(X)$. Prove that: $I$ is a nonnegative linear functional on $\mathfrak{C}_{00}(X)$; the corresponding measure $\iota$ is $\sum_{n=1}^{\infty} \alpha_n \varepsilon_x_n; M_i = \mathcal{P}(X)$.

(c) Extend (b) to the case in which $\sum_{n=1}^{\infty} \alpha_n = \infty$. Find extra conditions on $\{x_n\}_{n=1}^{\infty}$ necessary and sufficient for $I$ to be finite for all $\varphi \in \mathfrak{C}_{00}(X)$, and prove the second and third assertions of part (b) for the new $I$ and $\iota$, under the hypothesis that $X$ is $\sigma$-compact.

The proof of the next theorem gives a method of "constructing" the $\sigma$-algebra generated by a

in $S$. Since $A = \bigcup_{0 \leq \alpha < \Omega} \mathcal{E}_x$, we have proved that $A \subset S$. It is trivial that $\mathcal{E} \subset A$, and so to complete the proof we need only to show that $A$ is a $\sigma$-algebra. Since $\varnothing \in \mathcal{E}_0$, we have

$$X = (\varnothing' \cup \varnothing \cup \varnothing \cup \cdots) \in \mathcal{E}_1 \subset A.$$

Now let $A \in A$. There is an $\alpha < \Omega$ such that $A \in \mathcal{E}_\alpha$; hence $A' = (A' \cup A' \cup \cdots) \in \mathcal{E}_\alpha^* \subset \mathcal{E}_\beta$ for every $\beta > \alpha$, and therefore $A' \in A$. Next let $(A_n)_{n=1}^{\infty}$ be a sequence of elements of $A$. For each $n \in N$, there is an $\alpha_n < \Omega$ such that $A_n \in \mathcal{E}_{\alpha_n}$. Apply (4.49.iv) to find a $\beta < \Omega$ such that $\alpha_n < \beta$ for each $n \in N$. Then

$$\bigcup_{n=1}^{\infty} A_n \in \left( \bigcup_{n=1}^{\infty} \mathcal{E}_{\alpha_n} \right)^* \subset \mathcal{E}_\beta \subset A.$$

Therefore $A$ is a $\sigma$-algebra and $A = S$.

By hypothesis, we have $\bar{\mathcal{E}}_0 = \epsilon \geq 2$. Considering the ways in which the sets $\bigcup_{n=1}^{\infty} A_n \in \mathcal{E}_1$ can be formed [at most 2$\epsilon$ choices for each $A_n$], we see that $\bar{\mathcal{E}}_1 \leq (2\epsilon)^{\aleph_0} = \epsilon^{\aleph_0}$ [(4.32), (4.

as in § 9, no general facts or methods are known. For Lebesgue outer measure $\lambda$ on $\mathcal{P}(R)$, however, it is reasonably simple to find non-$\lambda$-measurable sets. We begin with a simple fact about $\lambda$.