If $M$ and $N$ are subsets of a linear space $\mathcal{E}$, then $M$ is said to absorb $N$ if there exists a positive number $k$ large enough so that $N \subset \lambda M$ for every $\lambda$ such that $|\lambda| \geq k$. (Thus a subset $A$ of $\mathcal{E}$ is absorbing in the sense defined in Chapter 14 if and only if it absorbs every singleton.) A subset $

Example Q. Every compact subset of a separated locally convex space $\mathcal{E}$ is bounded. Indeed, if $V$ is an absolutely convex neighborhood of 0 in $\mathcal{E}$, then the sequence $\{nV^\circ\}_{n=1}^{\infty}$ is a nested open covering of $\mathcal{E}$. Hence if $K$ is a compact set in $\mathcal{E}$, then some one set $nV$ contains $K$. In particular, every convergent sequence in $\mathcal{E}$ is bounded.

Example R. If $\mathcal{E}$ is an arbitrary separated locally convex topological linear space, then a subset $B$ of $\mathcal{E}$ is bounded with respect to the weak topology on $\mathcal{E}$ if and only if it is weakly bounded, i.e., if and only if each functional $f$ in $\mathcal{E}^*$ is bounded on $B$. Indeed it is obvious that if $B$ is bounded with respect to the weak topology on $\mathcal{E}$, then this condition must be satisfied since the weak neighborhood $U(f; 1)$ must absorb $B$ for each $f$ in $\mathcal{E}^*$ (cf. Chapter 15(2)). Suppose, on the other hand, that $B$ is weakly bounded. Every weak neighborhood of 0 in $\mathcal{E}$ contains a neighborhood of the form $U = (f_1, \ldots, f_n; \varepsilon)$, and if $K$ is chosen so that $|f_i(x)| \leq K$ for all $x$ in $B$ and $i = 1, \ldots, n$, then $B \subset \lambda U$ whenever $|\lambda| \geq K/\varepsilon$, which shows that $U$ absorbs $B$. It should be noted that this example shows, in general, that if $\langle \mathcal{E}, \mathcal{F} \rangle$ is a dual pair then a nonempty subset $M$ of $\mathcal{E}$ is bounded in the weak topology if and only if $\sup_{x \in M} |\langle x, y \rangle| < +\infty$ for each $y$ in $\mathcal{F}$.

The notion of boundedness leads at once to

The foregoing discussion shows that if $\langle \mathcal{E}, \mathcal{F} \rangle$ is a dual pair and $M$ is a subset of $\mathcal{E}$, then $M^0$ is an absorbing absolutely convex subset of $\mathcal{F}$ if and only if $M$ is weakly bounded. If $M$ is a weakly bounded subset of $\mathcal{E}$, then the Minkowski function $\sigma$ of $M^0$ is a pseudonorm on $\mathcal{F}$ called the pseudonorm associated with $M$. A trivial calculation shows that if $M \neq \emptyset$, then $\sigma$ is given by the formula

$$\sigma(y) = \sup_{x \in M} |\langle x, y \rangle|, \quad y \in \mathcal{F}.$$

(The pseudonorm associated with the empty subset of $\mathcal{E}$ is identically zero.) Moreover, it is clear that $M^0$ is the closed unit ball with respect to $\sigma$, and that a net $\{y_\lambda\}$ in $\mathcal{F}$ is convergent to a limit $y$ with respect to $\sigma$ if and only if $\{y_\lambda\}$ converges uniformly to $y$ on $M$ (with the elements of $\mathcal{F}$ identified with functionals on $\mathcal{E}$ in the standard way). Thus we are lead to the following terminology.
