The points $z = -2, -4, \ldots$ are called the trivial zeros of $\zeta$ and the strip $\{z: 0 \leq \text{Re} z \leq 1\}$ is called the critical strip.

We now are in a position to state one of the most celebrated open questions in all of Mathematics. Is the following true?

The Riemann Hypothesis. If $z$ is a zero of the zeta function in the critical strip then $\text{Re} z = \frac{1}{2}$.

It is known that there are no zeros of $\zeta$ on the line $\text{Re} z = 1$ (and hence none on $\text{Re} z = 0$ by the

product of powers of the prime numbers $p_1, \ldots, p_n$ alone. (The reason that no number $n_j^{-z}$ has a coefficient in this expansion other than 1 is that the factorization of $n_j$ into the product of primes is unique.) By letting $n \to \infty$ the result is achieved.

Exercises

1. Let $\xi(z) = z(z-1)\pi^{-\frac{1}{2}}z(\zeta(z))\Gamma(\frac{1}{2}z)$ and show that $\xi$ is an entire function which satisfies the functional equation $\xi(z) = \xi(1-z)$.

2. Use Theorem 8.17 to prove that $\sum p_n^{-1} = \infty$. Notice that this implies that there are an infinite number of primes.

3. Prove that $\zeta^2(z) = \sum_{n=1}^{\infty} \frac{d(n)}{n^z}$ for $\text{Re } z > 1$, where $d(n)$ is the number of divisors of $n$.

4. Prove that $\zeta(z)\zeta(z-1) = \sum_{n=1}^{\infty} \frac{\sigma(n)}{n^z}$, for $\text{Re } z > 1$, where $\sigma(n)$ is the sum of the divisors of $n$.

5. Prove that $\frac{\zeta(z-1)}{\zeta(z)} = \sum_{n=1}^{\infty} \frac{\varphi(n)}{n^z}$ for $\text{Re } z > 1$, where $\varphi(n)$ is the number of integers less than $n$ and which are relatively prime to $n$.

6. Prove that $\frac{1}{\zeta(z)} = \sum_{n=1}^{\infty} \frac{\mu(n)}{n^z}$ for $\text{Re } z > 1$, where $\mu(n)$ is defined as follows. Let $n = p_1^{k_1}p_2^{k_2} \ldots p_m^{k_m}$ be the factorization of $n$ into a product of primes $p_1, \ldots, p_m$ and suppose that these primes are distinct. Let $\mu(1)