Let $k$ be an integrally closed subring of a field $K$. The Riemann surface $S$ of $K/k$ is a $T_1$-space if and only if one of the following

positive transcendence degree over $k$, and compounding $v_0$ with a non-trivial valuation of the residue field of $v_0$ we would find a valuation of $K/k$ which has rank greater than 1. Suppose now that $k$ is a proper ring. Let $\mathfrak{p}$ be any proper prime ideal of $k$. If the quotient ring $k_\mathfrak{p}$ is not a valuation ring then there exists a valuation $v'$ of the quotient field of $k$ which has center $\mathfrak{p}$ in $k$ and which is of the second kind with respect to $k$ (Theorem 10, §5). The residue field $\Delta$ of $v'$ is then of positive transcendence degree over the quotient field $k^\star$ of $k/\mathfrak{p}$. Compounding $v'$ with a non-trivial valuation of $\Delta/k^\star$ and extending the resulting composite valuation to a valuation of $K$ we find a valuation $v$ in $S$ which has rank $>1$, in contradiction with the preceding theorem. Hence $k_\mathfrak{p}$ is a valuation ring, and the corresponding valuation of the quotient field of $k$ must be of rank 1. Finally, $K$ must be an algebraic extension of the quotient field of $k$, for in the contrary case $S$ would contain valuations of rank $>1$, extensions of non-trivial valuations of the quotient field of $k$. This completes the proof.

Even in the special case in which $S$ is a $T_1$-space it need not be a Hausdorff space. Without attempting to give a complete classification of Hausdorff Riemann surfaces we shall make here only the following three observations:

(A) In the case (1) of Theorem 39 the Riemann surface $S$ is never a Hausdorff space. For, let $\mathfrak{o} = k[x_1, x_2, \cdots, x_n]$ and $\mathfrak{o}' = k[x'_1, x'_2, \cdots, x'_m]$ be two finitely generated subrings of

$K = k[1/x]$, where $x$ is a suitable element of $k$, characterized by the property that it belongs to all the prime ideals $\mathfrak{p}$ of $k$, different from the zero ideal. However, the above condition may not be sufficient.

(C) If $k$ is a proper ring of the type described in case (2) of Theorem 39 and if $K$ is any (finite or infinite) algebraic extension of the quotient field $L$ of $k$, then a sufficient condition for the Riemann surface of $K/k$ to be a Hausdorff space is that $k$ have only a finite number of prime ideals. The statement is obvious if $K$ is a finite extension of $L$, for in that case the $T_1$-space $S$ has only a finite number of elements. In the infinite case, given two distinct elements $v'_1$ and $v'_2$ of $S$, there exists a field $F$ between $L$ and $K$, finite over $L$, such that the restrictions $v_1$ and $v_2$ of $v'_1$ and $v'_2$ to $F$ are distinct elements of the Riemann surface $S^\star$ of $F/k$. By the finite case, the elements $v_1$ and $v_2$ can be separated in $S^\star$ by two disjoint basic open sets. Taking the inverse images of these two open sets, under the restriction map $v' \rightarrow v = \text{restriction of } v'$ in $F(v' \in S, v \in S^\star)$, we find in $S$ two basic open sets which are disjoint and separate $v'_1$ and $v'_2$.

Our next object is to prove the following theorem: