Let $\Gamma$ be any graph with $\iota(\Gamma) < 2$. If $\gamma(\Gamma) \geq 4$, then $\chi_0(\Gamma) \leq 4$; if $\gamma(\Gamma) \geq 6$, then $\chi_0(\Gamma) \leq 3$. (Cf. B7 and B8.)

Quite possibly the reader will immediately recognize that C14 differs from Heawood's formula [h.7] only insofar as $\nu_2(Z_1, \ldots, Z_m) - \nu_1 + \nu_0$ stands in place of the Euler characteristic. The relationship between these two parameters is considered in the next section.

VIID The Euler Characteristic and Genus of a Graph

Prerequisite to an understanding of this and the next section are some basic point-set topology and an acquaintance with the classification of surfaces. (This material is not presumed for the other sections of this text.) In particular, it will be

Γ is a connected component of the complement in S of the image of the topological imbedding of Γ. If every such region is homeomorphic to an open disk, the topological imbedding is called a 2-cell imbedding. By abuse of terminology, the vertices and edges of Γ are identified with the images under a topological imbedding of their corresponding subspaces in a topological realization of Γ. If R is a region, the set of edges, each of which belongs to the boundary of both R and some region other than R, corresponds to a cycle of Γ, called the cycle of R.

We begin by indicating rather intuitively how an arbitrary graph Γ always has a topological imbedding in some orientable surface. Consider a topological realization of Γ in 3-space and "thicken" it in the sense that edges become rods. Clearly Γ can be topologically imbedded on the surface of such a structure.

The genus η(Γ) of the graph Γ is the genus of the orientable surface S of least genus such that Γ can be topologically imbedded in S. An imbedding of Γ in an orientable surface of genus η(Γ) is called a minimal imbedding. The Euler characteristic ε(Γ) of Γ is the Euler characteristic of the surface S of greatest Euler characteristic such that Γ can be topologically imbedded in S. An imbedding of Γ in a surface of Euler characteristic ε(Γ) is called a simplest imbedding. Clearly ε(Θ) ≥ ε(Γ) and η(Θ) ≤ η(Γ) for any subgraph Θ of Γ.

We next indicate how a minimal imbedding of a connected graph is always a 2-cell imbedding. If there were a region R of the imbedding which were not a 2-cell, one could imbed a closed loop (homeomorphic image of a 1-sphere) which is homotopically nontrivial in S so that it lies entirely within R and hence is disjoint from the realization of Γ. Now cut S along this loop and cap off both ends with disks. We have produced a surface T with η(T) < η(S) = η(Γ), and yet Γ is topologically imbedded in T, which is absurd. A similar argument clearly can be used to
