Let $A$ be a regular local ring of dimension $d$, $\mathfrak{m}$ its maximal ideal, $\mathfrak{b}$ an ideal in $A$, $q$ the dimension of $A/\mathfrak{b}$, and $\{\mathfrak{v}_j\} (1 \leq j \leq h)$ a finite family of non-maximal prime ideals in $A$. Then there exists a regular system of parameters $\{u_1, \cdots, u_d\}$ of $A$ such that the ideal $(\mathfrak{b}, u_1, \cdots, u_q)$ is primary for $\mathfrak{m}$, and that $u_1 \notin \mathfrak{v}_j$ for every $j$.

Proof of the lemma. We proceed by induction on $q$, the case $q=0$ being trivial. Let $q \neq 0$. We denote by $\mathfrak{v}_i, i=h+1, h+2, \cdots, k$, the isolated prime ideals of $\mathfrak{b}$; these prime ideals are distinct from $\mathfrak{m}$. From the family $\{\mathfrak{v}_i, \mathfrak{v}_j\}$ of prime ideals we extract those which are not contained in any other ideal of the family. Let $\{\mathfrak{p}_s\}$ be this reduced family. For every $s$, we have $\mathfrak{m}^2 \notin \mathfrak{p}_s$, whence we can find an element $c_s$ such that $c_s \in \mathfrak{m}^2$, $c_s \in \mathfrak{p}_t$ for every $t \neq s$ and $c_s \notin \mathfrak{p}_s$. Now we fix an element $x$ of $\

20 (§ 9), the rings $A/\mathfrak{p}$ and $B/(\mathfrak{p} \cap B)$ have the same dimension. As the dimension of the former is $d-r$, $B/(\mathfrak{p} \cap B)$ has also dimension $d-r$. Now, $B$ itself has dimension $d-r$, since it is a power series ring in $d-r$ variables over a field. Since $\mathfrak{p} \cap B$ is prime, this implies, by Theorem 20 (§ 9), that $\mathfrak{p} \cap B = (0)$.

We have already seen that $A/\mathfrak{p}$ is a finite module over $B/(\mathfrak{p} \cap B) = B$. More precisely, $A/\mathfrak{p}$ is generated by any system of elements $\{y'_j\}$ whose residue classes modulo $\sum_{i=r+1}^{d}(A/\mathfrak{p})\bar{u}_i$ generate $(A/\mathfrak{p})/\sum_{i=r+1}^{d}(A/\mathfrak{p})/\bar{u}_i$ over $K$ (Theorem 7, § 3). An equivalent form of this condition on the elements $y'_j$ is the following: the $y'_j$ are the $\mathfrak{p}$-residues of elements $y_j$ of $A$ whose residue classes modulo $(\mathfrak{p}, u_{r+1}, \cdots, u_d)$ generate $A/(\mathfrak{p}, u_{r+1}, \cdots, u_d)$ over $K$. We may thus take for elements $y_j$ the element 1 and a finite number of suitable monomials in $u_1, \cdots, u_r$. Therefore we have $A/\mathfrak{p} = B[u'_1, \cdots, u'_r]$ ($u'_i$: $\mathfrak{p}$-residue of $u_i$), whence $A = \mathfrak{p} + B[u_1, \cdots, u_r]$.

The elements $

ideal $S(\mathfrak{p} \cap S)$ has dimension zero. Then, since $S(\mathfrak{p} \cap S)$ is thus a maximal ideal in the polynomial ring $L[u_1, \cdots, u_r]$ in $r$ variables, it may be generated by exactly $r$ elements (VII, § 7, Theorem 24). Our proof will thus be complete if we show that $\mathfrak{p}A_{\mathfrak{p}}$ is generated by $S(\mathfrak{p} \cap S)$.

Now this is immediate. The relations $\mathfrak{a} \subset \mathfrak{p}$ and $A = \mathfrak{a} + B[u_1, \cdots, u_r]$ show that $\mathfrak{p} = \mathfrak{a} + (\mathfrak{p} \cap B[u_1, \cdots, u_r])$, whence $\mathfrak{p}A_{\mathfrak{p}} = \mathfrak{a}A_{\mathfrak{p}} + (\mathfrak{p} \cap B[u_1, \cdots, u_r])A_{\mathfrak{p}}$. Since $\mathfrak{a}$ is generated by the elements $a_i$ which lie in $\mathfrak{p} \cap S$, and since $\mathfrak{p} \cap B[u_1, \cdots, u_r]$ is obviously also in $\mathfrak{p} \cap S$, we have $\mathfrak{p}A_{\mathfrak{p}} = (\mathfrak{p} \cap S)A_{\mathfrak{p}}$, and this proves Theorem 28.

REMARK. For every prime ideal $\mathfrak{p}$ in the power series $A = K[[x_1, \cdots, x_d]]$, $A_{\mathfrak{p}}$ is a regular local ring. The corresponding statement for a polynomial ring $A = K[x_1, \cdots, x_d]$ and a prime ideal $\mathfrak{p}$ of $A$ is easier to prove. If $q$ is the dimension of $\mathfrak

since $\mathfrak{p} \supset \mathfrak{a}$. We may thus assume that $A$ is a complete ring. We suppose that one of the associated prime ideals $\mathfrak{p}$ of $\mathfrak{a}$ has dimension $<d-r$, and from this we shall derive a contradiction. In the local ring $A_{\mathfrak{p}}$, the ideal $\mathfrak{p}A_{\mathfrak{p}}$ admits the maximal ideal $\mathfrak{p}A_{\mathfrak{p}}$ as an associated prime ideal. By Theorem 28 $A_{\mathfrak{p}}$ is a regular local ring. The dimension $n$ of $A_{\mathfrak{p}}$ is $>r$, since we have assumed that $\mathfrak{p}$ has dimension $<d-r$, and $\mathfrak{a}A_{\mathfrak{p}}$ is an ideal generated by $r$ elements. Furthermore, since every isolated prime ideal of $\mathfrak{a}$ has dimension $d-r$ (Vol. I, Ch. IV, § 14, Theorem 30), every isolated prime ideal of $\mathfrak{a}A_{\mathfrak{p}}$ has dimension $n-r$. Thus, with a change in notations, we have to prove that the following situation is impossible: we have a regular local ring $A$ of dimension $n$, an ideal $\mathfrak{a} = (a_1, \cdots, a_r)$ in $A$, of dimension $n-r$, generated by $r$ elements, $r < n$, and the maximal ideal $m$ of $A$ is an associated prime ideal of $\mathfrak{a}$.

Since a principal ideal in a local ring of dimension $q$ has either dimension $q-1$ or dimension $q$, the dimensions of the ideals $(a_1, \cdots, a_r)$, $(a_1, \cdots, a_{r-1})$, $\cdots, (a_1)$, (0) form a sequence of integers such that the difference of two consecutive terms is 0 or 1. Since the dimension of $\mathfrak{a}$ is $n-r$, and since the dimension of