Informal comments in lieu of proof. For each (small) set $A$ define a (perhaps large) set $A\Omega$ “inductively” by

$$a \in A\Omega \text{ for all } a \in A$$

whenever $\omega \in \Omega_n$ and $(p_i: i \in n)$ is an $n$-tuple in $A\Omega$ then $(p_i: i

where $E_1$ consists of the equations $\text{Sup}_n(af) = \text{Sup}_n(bf)$ indexed by each instance of a pair $a, b:n \rightarrow m$ of surjections; $E_2$ is the single equation $\text{Sup}_1(x) = x$; and $E_3$ consists of the equations $\text{Sup}_p(\text{Sup}_m(\Gamma_i f):i \in p) = \text{Sup}_n(f)$, where $(m \xrightarrow{\Gamma_i} n:i \in p)$ is a family of functions such that the union of the images covers all of $n$. (Of course, each side in any of the above equations is a natural transformation in accordance with the Definition 5.34; $E_1$ is trying to say (and does!) that $\text{Sup}_n(f) = \text{Sup}_n(g)$ whenever $f, g:n \rightarrow X$ have the same image).

Define a new operator domain $\Omega'$ by $\Omega'_n = \{\text{Inf}_n\}$ and define $\Omega'$-equations $E'$ by substituting “Inf” for “Sup” in each of the equations in $E$ above. Since supremum in a partially ordered set $(X, \leq)$ is the same thing as infimum in the partially ordered set $(X, \geq)$, our interpretation of the operators in 5.47 was biased, and we may be comfortable in viewing complete semilattices as $(\Omega', E')$-algebras as well. It is now clear that complete lattices is a full subcategory of $(\Omega \cup \Omega', E \cup E')$-algebras, and all that is missing is the guarantee that the Sup operators induce the same partial order as the Inf operators, that is that “$\text{Sup}_2(x, y) = y$ if and only if $\text{Inf}_2(x, y) = x$.” The equational way to say this is the well known absorptive laws:

$$\text{Inf}_2(x, \text{Sup}_2(x, y)) = x$$
$$\text

complemented. To this end, adjoin a single unary operator, $c$, to the operator domain of 5.47 and impose the equations of 5.47 together with four new ones:

$$\text{Inf}_2(\text{Sup}_2(x, y), z) = \text{Sup}_2(\text{Inf}_2(x, z), \text{Inf}_2(y, z))$$
$$\text{Sup}_2(\text{Inf}_2(x, y), z) = \text{Inf}_2(\text{Sup}_2(x, z), \text{Sup}_2(y, z))$$
$$\text{Sup}_2(x, cx) = \text{Inf}_\emptyset$$
$$\text{Inf}_2(x, cx) = \text{Sup}_\emptyset$$

To check that we really have a Boolean algebra here, sceptics should note that $x + y = \text{Inf}_2(\text{Sup}_2(x, y), c \text{ Inf}_2(x, y))$.

With the help of exercise 19, it is not hard to prove, as is certainly suggested by 5.5, that the class of $n$-ary operations of any equational presentation contains a subalgebra freely generated by $n$, i.e., with the universal property of 4.12 with respect to algebras and homomorphisms (although is not necessarily a genuine algebra because it may be built on a large set). It suffices to show, then, that the assumption that we have a complete Boolean algebra $F$ and a function $\eta: \aleph_0 \longrightarrow F$ with the universal property

$$\aleph_0 \longrightarrow F$$

that every function $f: \aleph_0 \longrightarrow C$ to a complete Boolean algebra $C$ extends uniquely to a complete Boolean homomorphism $\psi: F \longrightarrow C$, leads to the conclusion that $F$ admits a surjection to every ordinal number. In fact, by 4.12 and 4.14 this proves immediately that complete Boolean algebras is not $\mathbf{T}$-presentable.

Since the image of $\psi$ (as above) is a complete Boolean subal

the product topology. If $(S_n:n \in \mathbf{N})$ is a sequence of subsets of $\alpha$ then $\{f \in X : f_n \in S_n\}$ is closed since it is the cartesian product of the closed sets $S_n$. For $n \in \mathbf{N}$ and $S \subset \alpha$, $A_{n,S} = \{f \in X : f_n \in S\}$ is a typical subbasic open set; as mentioned above, it is also closed. As all clopen sets are regular open sets, $A_{n,S}$ is a regular open set. In particular, for $n \in \mathbf{N}$ and $\beta < \alpha$, $A_{n,\beta} = \{f \in X : f_n = \beta\}$ is a regular open set. For $n$, $m \in \mathbf{N}$, $B_{n,m} = \{f \in X : f_n \leq f_m\}$ is closed (use nets) as is its complement (use nets again), so $B_{n,m}$ is a regular open set. Let $\mathcal{B}$ be the complete Boolean subalgebra of regular open sets generated by the countable family of all $B_{n,m}$'s and all $A_{n,\beta}$'s (for finite ordinals $\beta$), where "subalgebra generated by" means "the intersection of all containing subalgebras"). No proper subalgebra of $\mathcal{B}$ contains this countable family. Since the $A_{0,\beta}$ are pairwise distinct, the proof is completed by proving that all $A_{0,\beta} \in \mathcal{B}$. To do this we will establish "for all $n \in \mathbf{N}$, $A_{n,\beta} \in \mathcal{B}$" for each $\beta < \alpha$ by transfinite induction. We already know this for finite $\beta$, which provides the basis. Now suppose this is true for $\beta < \gamma$; we must prove it for $\gamma$.

Fix $n \in \mathbf{N}$. As $\cup(A_{n,\beta} : \beta < \gamma) = \{f \in X : f_n < \gamma\}$ is clopen,

formally, a set of sets $x$ is $\in$-transitive if whenever $y \in x$ and $z \in y$ then $z \in x$. An ordinal is a set of sets $x$ such that $x$ is $\in$-transitive and such that for all $y \in x$, $y$ is $\in$-transitive. If $x, y$ are ordinals then (using the “axiom of regularity”) exactly one of “$x \in y$,” “$x = y$,” “$y \in x$” occurs ([Monk 9.9]) so that the class Ord of all ordinals is linearly ordered via $x \leqslant y$ if $x = y$ or $x \in y$. If $X$ is a nonempty set of ordinals then $\cap \{x : x \in X\}$ is an ordinal and is in $X$ ([Monk 9.10]); in particular, $X$ has a least element. Further, for ordinals $x, y, x \leqslant y$ holds if and only if $x \subset y$.

Every ordinal $x$ satisfies $x = \{y : y\}$ is an ordinal and $y < x$ ([Monk 9.13 (iii)]). This establishes the (first) principle of transfinite induction [Monk 10.1]: to define a function on an ordinal $x$ it suffices to define $f(y)$ for all $y < x$. We used this in 5.48. An ordinal $x$ is a successor ordinal if $x$ has form $s(y)$ (i.e., “$x-1$ exists”) and $x$ is a limit ordinal if $x \neq 0$ and $x$ is not a successor ordinal. $\omega$ is the smallest limit ordinal. The (second) principle of transfinite induction [Monk 10.4] asserts: to define a function $f$ on an ordinal $x$ it suffices to define $f(0)$, to define $f(y+1)$ in terms of $f(y)$ whenever $y+1 < x$ and to define $f(y

Paradox: it is easy to prove that the set Ord is an ordinal ([Monk 9.7]). Thus Ord $\in$ Ord, i.e. Ord $<$ Ord, which is impossible. Also, the Russell Paradox: let $R$ be the set of all sets of sets $x$ such that $x \notin x$; then $R$ is a set of sets, but if $R \in R$ then $R \notin R$ whereas if $R \notin R$ then $R \in R$. The way these paradoxes are resolved is by insisting that certain "classes" such as Ord and $R$ above are "impedicatively defined" (that is, there is obvious "self-definition" in phrases such as "the ordinal of all ordinals" and "the set of all sets of sets") and are not bona fide sets. For example, Ord is not really an ordinal because it is not a set.

To truly resolve the crises of the preceding paragraph would lead us far afield from the subject matter of this book. We refer the reader to [Mac Lane '71, I.6] for a description of some related problems and of the "one universe" set theory that is adequate for our needs. (See also [Fraenkel, Bar Hillel and Levy '73, II.7].) In brief, there is a "universe" $U$ modelling the "set of all sets." A small set is an element of $U$. A subset of $U$ which is not an element of $U$ is a large set. Thus Ord and $R$ above are large sets. Any set which admits an injection from or a surjection to every cardinal is a large set. A cartesian product of a family of small sets indexed by a small set is a small set; on the other hand, the cartesian product of all small sets is a large set. A priori, there is no reason why $O_X(\mathbf{T})$ or $O_X(T)$ need be small sets, but this is proved in 5.5. The class of operations of an operator domain as in 5.34 will be a large set unless there exists a cardinal $N$ such that $\Omega_n = \varnothing$ whenever $n > N$. The intended

His five axioms for a collection of subsets $U$ of a set to be an "ideale verdichtungstelle" are: (1) every superset of an element of $U$ is again in $U$; (2) if $A, B$ are disjoint and if their union is in $U$ then $A \in U$ or $B \in U$; (3) the intersection of two elements of $U$ is again in $U$; (4) $U$ is maximal with respect to properties (1)–(3); (5) the intersection of all elements of $U$ is empty. See [Bell and Slomson '71] for the use of ultrafilters in model theory (and Chapters 5, 6 there for details concerning the structure of ultrafilters per se). The axiom of choice, which is equivalent to Zorn's lemma, was used to prove the "ultrafilter theorem" (every filter is contained in an ultrafilter) used in 5.27. There exist models of (Zermelo-Frankel) set theory in which (1) the ordinal $\omega$ has no nonprincipal ultrafilters or (2) every infinite set has at least one nonprincipal ultrafilter but the ultrafilter theorem fails or (3) the ultrafilter theorem holds but the axiom of choice fails. See [Jech '73, page 82, page 132, Theorem 7.1]. Since one expects any "actual construction" of a nonprincipal ultrafilter to build one on $\omega$ in any model of set theory, it is popular to assert that "it is impossible to construct any example of a nonprincipal ultrafilter"; at this writing, however, this assertion is only a conjecture.

The characterization of topological concepts in the language of ultrafilter convergence can be found in [Choquet '48]; we thank H. R. Fischer and O. Wyler for pointing out this reference.

Infinitary universal algebra begins with the founding paper [Birkhoff '35] where algebraic recursion is assumed without comment. A number of works have been devoted to a rigorous construction of free $\Omega$-algebras when $\Omega$ is infinitary but bounded: [