If $G$ is an open set then $\gamma$ is homologous to zero, in symbols $\gamma \approx 0$, if $n(\gamma; w) = 0$ for all $w$ in $\mathbb{C} - G$.

Using this notation, Corollary 6.10 says that $\gamma \sim 0$

5. Evaluate the integral $\int \frac{dz}{z^2+1}$ where $\gamma(\theta) = 2|\cos 2\theta| e^{i\theta}$ for $0 \leq \theta \leq 2\pi$.

6. Let $\gamma(\theta) = \theta e^{i\theta}$ for $0 \leq \theta \leq 2\pi$ and $\gamma(\theta) = 4\pi - \theta$ for $2\pi \leq \theta \leq 4\pi$. Evaluate $\int \frac{dz}{z^2+\pi^2}$.

7. Let $f(z) = [(z-\frac{1}{2}-i) \cdot (z-1-\frac{3}{2}i) \cdot (z-1-\frac{i}{2}) \cdot (z-\frac{3}{2}-i)]^{-1}$ and let $\gamma$ be the polygon $[0, 2, 2+2i, 2i, 0]$. Find $\int_{\gamma} f$.

8. Let $G = \mathbb{C} - \{a, b\}$, $a \neq b$, and let $\gamma$ be the curve in the figure below.

(a) Show that $n(\gamma; a) = n(\gamma; b) = 0$.

(b) Convince yourself that $\gamma$ is not homotopic to zero. (Notice that the word is “convince” and not “prove”. Can you prove it?) Notice that this example shows that it is possible to have a closed curve $\gamma$ in a region such that $n(\gamma; z) = 0$ for all $z$ not in $G$ without $\gamma$ being homotopic to zero. That is, the converse to Corollary 6.10 is false.

9. Let $G$ be a region and let $\gamma_0$ and $\gamma_1$ be two closed smooth curves in $G$. Suppose $\gamma_0 \sim \gamma_1$ and $\Gamma$ satisfies (6.2). Also suppose that $\gamma_t(s) = \Gamma(s,t)$ is smooth for each $t$. If $w \in \mathbb{C} - G$ define $h(t) = n(\gamma_t; w

§7. Counting zeros; the Open Mapping Theorem

In this section some applications of Cauchy’s Integral Theorem are given. It is shown how to count the number of zeros inside a curve; also, using some information on the existence of roots of an analytic equation, it will be proved that a non-constant analytic function on a region maps open sets onto open sets.