Among the simply connected regions there are only two equivalence classes; one consisting of $\mathbb{C}$ alone and the other containing all the proper simply connected regions.

Exercises

1. Let $G$ and $\Omega$ be open sets in the plane and let $f: G \rightarrow \Omega$ be a continuous function which is one-one, onto, and such that $f^{-

8. Let $r_1, r_2, R_1, R_2$, be positive numbers such that $R_1/r_1 = R_2/r_2$; show that ann $(0; r_1, R_1)$ and ann $(0; r_2, R_2)$ are conformally equivalent.

9. Show that there is an analytic function $f$ defined on $G = \text{ann}(0; 0, 1)$ such that $f'$ never vanishes and $f(G) = B(0; 1)$.

§5. The Weierstrass Factorization Theorem

The notion of convergence in $H(G)$ can be used to solve the following problem. Given a sequence $\{a_k\}$ in $G$ which has no limit point in $G$ and a sequence of integers $\{m_k\}$, is there a function $f$ which is analytic on $G$ and such that the only zeros of $f$ are at the points $a_k$, with the multiplicity of the zero at $a_k$ equal to $m_k$? The answer to the question is yes and the result is due to Weierstrass.

If there were only a finite number of points, $a_1, \ldots, a_n$ then $f(z) = (z-a_n)^{m_1} \ldots (z-a_n)^{m_n}$ would be the desired function. What happens if there are infinitely many points in this sequence? To answer this we must discuss the convergence of infinite products of numbers and functions.

Clearly one should define an infinite product of numbers $z_n$ (denoted by $\prod_{n=1}^{\infty} z_n$) as the limit of the finite products. Observe, however, that if one of the numbers $z_n$ is zero, then the limit is zero, regardless of the behavior of the remaining terms of the sequence. This does not present a difficulty, but it shows that when zeros appear, the existence of an infinite product is trivial.