The valuation ring $R_v$ is noetherian if and only if the value group $\Gamma$ of $v$ is the additive group of integers.

Proof. We first show that if $R_v$ is noetherian then $v$ must be of rank 1. For suppose that $v$ is of rank greater than 1. Since the null-group is an isolated subgroup of $\Gamma$, there must exist an isolated subgroup $\Delta$ different from (0). Fix a positive element $\alpha$ in $\Delta$. Then $\alpha < 2\alpha < \cdots < n\alpha < \cdots$. Since $\Delta$ is a proper subgroup of $\Gamma$ we can find in $\Gamma$ a positive element $\beta$ which does not belong to $\Delta$. Since $\Delta$ is a segment and since the elements $n\alpha$ belong to $\Delta$, it follows that $\beta > n\alpha, n = 1, 2, \cdots$. We thus have in $\Gamma$ a strictly descending sequence $\beta, \beta - \alpha, \beta - 2\alpha, \cdots$ of positive elements. Such a sequence determines an infinite strictly descending sequence of segments of $\Gamma$, and therefore, by Theorem 15, we have an infinite strictly ascending sequence

the maximal ideal $\mathfrak{M}_v$ of $R_v$. Then any element of $R_v$ which is not divisible by $t$ is a unit. A familiar and straightforward argument shows that no element of $R_v$ (different from zero) can be divisible by all powers of $t$ (if $x = t^n a_n, a_n \in R_v, n = 1, 2, \cdots$, then the principal ideals $(a_1), (a_2), \cdots, (a_n), \cdots$ would form a strictly ascending chain). It follows that every element $x$ of $R_v, x \neq 0$, can be put (uniquely) in the form $at^n$, where $n \geq 0$ and $a$ is a unit. This shows that the principal ideals $(t^n), n = 1, 2, \cdots$, are all the proper ideals of $R_v$. Hence the maximal ideal $(t)$ of $R_v$ is the only proper prime ideal of $R_v$, whence $v$ is of rank 1. Furthermore, it is immediately seen that if $K'$ denotes, as usual, the multiplicative group of the field $K$ and $E$ is the set of units in $R_v$, then the quotient group $K'/E$, written additively, is isomorphic to the group of integers. The given valuation $v$ is necessarily equivalent to the valuation $v'$ obtained by setting $v'(at^n) = n$, if $a$ is a unit.

A valuation of rank 1 is said to be discrete if its value group is the additive group of integers. Thus, Theorem 16 states that a valuation ring $R_v$ is noetherian if and only if $v$ is a discrete valuation of rank 1.