Let $A$ be a local domain satisfying condition (D). Then $A'$ is a semi-local ring. Furthermore, if, for every maximal ideal $m$ of $A'$, the local ring $A'_m$ and all its residue class rings $A'_m/\mathfrak{p}$ ($\mathfrak{p}$ prime) satisfy (D), then the ring $c(A')$ is canonically isomorphic to $c(A')'$.

Proof. Condition (D) applied to $A$, i.e., the existence of an element $d \neq 0$ in $A$ such that $dc(A)' \subset c(A)$, implies that $c(A)'$ is contained in a finite $c(A)$-module, whence it is itself a finite $c(A)$-module since $c(A)$ is noetherian. Therefore $c(A)'$ is a complete semi-local ring, and $c(A)$ is a topological subspace of $c(A)'$ (Theorem 15, §6).

On the other hand, since no element $\neq 0$ of $A$ is a zero divisor in $c(A)$ (Corollary 6 to Theorem 11, §4), the total quotient ring $S$ of $c(A)$ contains the quotient field $K$ of $A$. We have $K \cap c(A) = A$, since, if an element $a/b$ ($a, b \in A$) of $K$ belongs to $c(A)$, we have $a

integral over $\sum B_i$. Writing component-wise an equation of integral dependence for $x$ over $\sum B_i$, we see that $x_i$ is integral over $B_i$ for every $i$, whence that $x_i \in B_i$ and that $x \in \sum B_i$.

We now prove that every $B_i$ is an integrally closed domain. We know (§7, remark to Corollary 2 to Theorem 18) that $B_i$ is isomorphic to the completion of $A'_{m_i}$, $m_i$ denoting one of the maximal ideals of $A'$. Since $A'$ is an integrally closed domain, so is $A'_{m_i}$. For completing the proof it suffices to notice that, by the hypotheses, Lemma 2 may be applied to $A'_{m_i}$.

In order to be able to apply Lemmas 1, 2, 3 to the local rings of algebraic geometry (which we call, for short, "algebro-geometric local rings"), it suffices to make sure that, given an algebro-geometric local ring $A$, then $A$ itself, all the rings $A/\mathfrak{p}$ ($\mathfrak{p}$: prime) and all the rings $A'_{m}/\mathfrak{p}'$ ($A'$ integral closure of $A$, $m$ maximal ideal in $A'$, $\mathfrak{p}'$ prime ideal in $A'_{m}$) satisfy condition (D). It is easily seen that all these local rings are algebro-geometric. In fact

(a) As to $A/\mathfrak{p}$, we write $A = B_q$, where $B$ is a finite integral domain $k[x_1, \cdots, x_n]$ and $\mathfrak{q}$ a prime ideal in $B$. Then $B_1 = B/(\mathfrak{p} \cap B)$ is a finite integral domain, $\mathfrak{p} \cap B$ is contained in $\mathfrak{q}$, and $A/\mathfrak{p}$ is isomorphic to $(B_1)_{q_1}$, where $\mathfrak{q}_1 =

separating transcendence basis of $k(y)/k$ is the same thing as a $p$-basis of $k(x)$ (if the characteristic $p$ of $k$ is $\neq 0$). By the lemma on p. 198 it is therefore sufficient that for each $j=1, 2, \cdots, r+1$ the elements $\zeta_1, \cdots, \zeta_{j-1}$ of $\mathfrak{P}$ have the following properties: the ideal $\mathfrak{D}\zeta_0 + \mathfrak{D}\zeta_1 + \cdots + \mathfrak{D}\zeta_{j-1}$ (where $\zeta_0 = y_0$) is of dimension $r+1-j$, $\mathfrak{P}$ contains none of the isolated prime ideals $\mathfrak{P}_i$ of this ideal, and $\zeta_0, \zeta_1, \cdots, \zeta_{j-1}$ are $p$-independent elements of $k(y)$. Assume $\zeta_0, \zeta_1, \cdots, \zeta_{j-1}$ have already been constructed (note, for $j=0$, that $y_0 \notin \mathfrak{P}$ and is a transcendental over $k(x)$). Let $u$ and $v$ be homogeneous elements of $\mathfrak{D}$ such that $u \notin \bigcup \mathfrak{P}_i, u \in \mathfrak{P}; v \in \mathfrak{P}, v \in \bigcap \mathfrak{P}_i$ and $v \notin k(y_0, \zeta_1, \cdots, \zeta_{j-1})(y^p)$ (the existence of $v$ follows from the fact that the elements of every non-zero ideal in $\mathfrak{D}$ generate $k(y)$ over $k$). Let $p^a g, p^b h$, be the degree of $u$ and $v$ respectively (where $p \neq a, p \neq b$). If $a < b$ we set $\zeta_j

L. The integral closure $(\hat{A})'$ of $\hat{A}$ is the integral closure of $\varphi(\hat{B})$ in $Z$, since $\hat{A}$ is integral over $\varphi(\hat{B})$. Furthermore $Z$ is a direct summand of the total quotient ring $T$ of $\hat{I}$. Theorem 16 (§6) shows that $T$ is a finite dimensional vector space over $L$, and that, if $\{a_1, \cdots, a_q\}$ is a basis of the quotient field $k(x)$ of $I$ over the quotient field $k(z)$ of $B$, then it is also a basis of $T$ over $L$. Lemma 4 will be proved if we prove the existence of an element $d \neq 0$ of $B$ such that $d(\hat{B})' \subset \hat{I} ((\hat{B})' = integral closure of \hat{B}$ in $T$): for, applying the projection $\varphi$ and noticing that any element of $Z$ which is integral over $\varphi(\hat{B})$ is the projection of an element of $T$ which is integral over $\hat{B}$, we get $\varphi(d) \cdot \varphi(\hat{B})' \subset \hat{A}$, i.e., $\varphi(d)(\hat{A})' \subset \hat{A}$, and we have $\varphi(d) \in A$, $\varphi(d) \neq 0$.

For proving the existence of $d$, we may assume that the basic elements $a_i$ belong to $I$. The trace mapping $T_{k(x)/k(z)}$ extends in a unique way to an $L$-linear mapping $\tau$ of $T$ into $L$. Since $k(x)$ is separable over $k(z)$, there exist elements $a'_1, \cdots, a'_q$ of $k(x)$ such that $\tau(a_i a'_j) = \delta_{ij}$ for all $i, j$ (Vol. I, Ch. V, §11, proof of Theorem 30). Now, if $y$ is an element of $T$ that is integral over $\hat{B}$, we see