If $W$ is any proper subvariety of $V$, defined and irreducible over $k$, then there exist prime divisors of $K/k$ having center $W$ on $V$. If we denote by $M_W$ the set of all these prime divisors then

(1) $\bigcap_{\mathcal{P} \in M_W} K_{\mathcal{P}} = \text{integral closure of } \varnothing(W; V)$.

Proof. If $\dim W=r-1$, then everything has already been proved: $M_W$ is non-empty, by Theorem 32, and (1) follows from Theorem 8, § 5, since every valuation of $K/k$ with center $W$ is necessarily a prime divisor. If $\dim W<r-1$, all the elements of $M_W$ are prime divisors of the second kind with respect to $V$, and our theorem asserts not only that $M_W$ is non-empty but also that the set $M_W$ is sufficiently ample as to insure that the intersection of the valuation rings $K_{\mathcal{P}}, \mathcal{P} \in M_W$, is the same as the intersection of all the valuation rings of valuations $v$ having center $W$ (this latter intersection being equal to the integral closure of the local ring $\varnothing(W, V)$, by Theorem 8, § 5).

Let $\mathfrak{p}$ be the prime ideal of $W

We give another (indirect) proof of the above assertion, which does not make use of the existence theorem for valuations. Assume that our assertion is false and that consequently there exists for each $i=1, 2, \cdots, h$ an element $\xi_i$ in $R$ such that $\xi_i \notin \mathfrak{p}$ and $\xi_i \in R'_i w_i$. Let $\xi = \xi_1 \xi_2 \cdots \xi_h$. Then also $\xi \notin \mathfrak{p}$ and $\xi \in R'_i w_i$, $i=1, 2, \cdots, h$. We can therefore write $\xi$ in the form $\xi = w_i \varphi_i(w_1, w_2, \cdots, w_h)/w_i'_i$, where $\varphi_i$ is a form in $w_1, w_2, \cdots, w_h$, of degree $\nu_i$, with coefficients in $R$. Letting $\nu = \max\{\nu_i\}$, we have

$$\xi w_i'^{-1} = \psi_i(w_1, w_2, \cdots, w_h), \quad i=1, 2, \cdots, h,$$

where $\psi_i$ is a form of degree $\nu$, with coefficients in $R$. It follows that the product of $\xi$ with every monomial $w_1^{\alpha_1} w_2^{\alpha_2} \cdots w_h^{\alpha_h}$ of degree $\alpha_1 + \alpha_2 + \cdots + \alpha_h = (\nu-2)h+1=N$ is equal to a form of degree $N+1$ in $w_1, w_2, \cdots, w_h$, with coefficients in $R$. This implies that $\xi \mathfrak{p}^N \subset \mathfrak{p}^{N+1}$. Since $\xi \notin \mathfrak{p}$, this relation implies the relation $\mathfrak{m}^N = \mathfrak{m}^{N+1}$, where $\mathfrak{m}$ is the maximal ideal in the quotient ring $R_\mathfrak{p}$, in contradiction with Vol.

8). Then $v(y) > 0$, $v$ is finite on $R'$, and if $\mathfrak{p}'$ denotes the center of $v$ in $R'$ then $y \in \mathfrak{p}'$ and $\mathfrak{p}' \cap R = \mathfrak{p}$. By the first part of the theorem, as applied to $R'$ and $\mathfrak{p}'$ instead of to $R$ and $\mathfrak{p}$, there exists a prime divisor $v^\star$ of $k(V)/k$ which is finite on $R'$ and has center $\mathfrak{p}'$. Then $v^\star$ is also finite on $R$, has center $\mathfrak{p}$ in $R$ (since $\mathfrak{p}' \cap R = \mathfrak{p}$) and furthermore $v^\star(z) < 0$ since $y \in \mathfrak{p}'$ and thus $v^\star(y) > 0$. Thus, we have found a prime divisor of center $W$ such that the valuation ring of that prime divisor does not contain $z$. This establishes (1) and completes the proof of the theorem.

We now go back to the prime divisors of $K/k$ which are of the first kind with respect to $V$. We denote by $S$ the set of these prime divisors. Let $\bar{R}$ be the integral closure of the coördinate ring $R = k[V]$ of $V/k$. Every prime divisor $v$ in $S$ is also finite on $\bar{R}$, the center of $v$ in $\bar{R}$ is a minimal prime $\bar{\mathfrak{p}}$ in $\bar{R}$, and the quotient ring $\bar{R}_\mathfrak{p}$ is the valuation ring of $v$. Conversely, if $\bar{\mathfrak{p}}$ is any minimal prime ideal in $\bar{R}$, then $\bar{R}_\mathfrak{p}$ is a discrete valuation ring of rank 1 (Theorem 16, Corollary 2, § 10) since $\bar{R}$ is noetherian, and if $v_\mathfrak{p}$

are irreducible $(r-1)$-dimensional subvarieties of $V/k$ and the $m_i$ are integers. We write $\Gamma > 0$ if all the $m_i$ are non-negative, and we say then that $\Gamma$ is a non-negative divisor. We write $\Gamma > 0$ ($\Gamma$ - a positive divisor) if $\Gamma > 0$ and $\Gamma \neq 0$. If now $w$ is any function in $K$, $w \neq 0$, then we can associate with $w$ a well-defined divisor on $V$, namely the divisor

$$(w) = \Sigma v_W(w) \cdot W,$$

where the sum is extended to all the irreducible $(r-1)$-dimensional subvarieties of $V/k$ (the above sum is, of course, finite since the number of $W$'s for which $v_W(w) \neq 0$ is finite). The divisor $(w)$ defined in (3) is called the divisor of the function $w$. Then $(w) > 0$ if and only if $w \in \bar{R}$ and $(w) = 0$ if and only if $w$ is a unit in $\bar{R}$.

The above definitions refer to the affine variety $V$. That a function $w$ may have no polar prime divisors on $V$ without being a "constant" (i.e., without belonging to the ground field $k$ or to the algebraic closure of $k$ in $K$) is due precisely to the fact that our definitions refer to an affine variety $V/k$. In this frame of reference one loses track of the prime divisors "at infinity." The "correct" definitions are obtained if one deals with projective varieties. We shall do that in the next chapter (VII, § 4). However, even without introducing explicitly projective spaces and varieties in the projective space, we can arrive already here at the desired "correct" definition of the divisor of a function in the following fashion:

If $n$ is the dimension of the affine ambient space of our variety $V$, let $x_1, x_2, \cdots, x_n$ be the coördinates of the general point

In fact, if $v(x_i) < 0$, then $v$ is not finite on $R_0$ and therefore $v \notin S_0$. On the other hand, if $v \in S_i$ and $v(x_i) \geq 0$, then also $v(x_j) \geq 0, j=1, 2, \cdots, n$, for $x_j = x_i \cdot x_j^i$ if $j \neq i$; whence $v$ is finite on $R_0$. Furthermore, we must now have $v(x_i) = 0$ (since $v(x_i^i)$ is non-negative), and hence the $v$-residue of $x_i$ is different from zero. The relations $x_j = x_i \cdot x_j^i (j \neq i)$ show therefore that the field generated over $k$ by $v$-residues of the $x_j^i (j=1, 2, \cdots, n)$ coincides with the field generated over $k$ by the residues of $x_1, x_2, \cdots, x_n$. This shows that the center of $v$ in $R$ also has dimension $r-1$, whence $v \in S_0$. We have therefore shown that there is only a finite number of prime divisors in $S^\star$ which do not belong to $S_0$. These are the prime divisors "at infinity" with respect to $V$.

We now can proceed as we did in the case of an affine variety, except that the set $S^\star$ now replaces the set $S_0(=S)$. If now a function $w$ in $K$, $w \neq 0$, has no polar divisors, i.e., if we have $v(w) \geq 0$ for all $v$ in $S^\star$, then $w$ must be a constant, i.e., $w$ is algebraic over $k$. For, $w$ must then belong to the integral closure of each of the $n+1$ rings $R_i$. On the other hand, given any valuation $v$ of $K/k$, the valuation ring $K_v$ must contain at least one

EXAMPLE 1. Valuations of maximum rational rank. Let $K = k(x_1, x_2, \cdots, x_r)$, where $x_1, x_2, \cdots, x_r$ are algebraically independent over $k$, and let $\alpha_1, \alpha_2, \cdots, \alpha_r$ be arbitrary, rationally independent real numbers. If $t$ is a parameter and we carry out the formal substitution $x_i \rightarrow t^{\alpha_i}$, then every monomial in $x_1, x_2, \cdots, x_r$ yields a power of $t$, and distinct monomials yield distinct powers of $t$ (since the $\alpha_i$ are rationally independent). If $f(x_1, x_2, \cdots, x_r)$ is any polynomial in $k[x_1, x_2, \cdots, x_r]$, then $f(t^{\alpha_1}, t^{\alpha_2}, \cdots, t^{\alpha_r})$ is a sum of powers of $t$, say, $ct^\beta + \text{terms of degree} > \beta$, where $c \neq 0$, $\beta = n_1\alpha_1 + n_2\alpha_2 + \cdots + n_r\alpha_r$, and the $n_i$ are non-negative integers. If we set $v(f) = \beta$, then $v$ is a mapping of $k[x_1, x_2, \cdots, x_r]$ (the zero excluded) onto a group $\Gamma$ of real numbers, where $\Gamma = J\alpha_1 + J\alpha_2 + \cdots + J\alpha_r$ ($J$ = the additive group of integers). Note that $\Gamma$ is the direct sum of the $r$ free cyclic groups $J\alpha_i$. We have $v(fg) = v(f) + v(g)$, $v(f+g) \geq \min\{v(f), v(g)\}$, and hence $v$ can be extended to a valuation $v$ of the field $K$ (§ 9, Theorem 14). The above group $\Gamma$ is the value group of $v$, and thus $v$ is non-dis

$\alpha_2/n!, \cdots, \alpha_r/n!$. Since $\Gamma$ is a subgroup, of finite index, of $\frac{1}{n!} \Gamma'$, also $\Gamma$ must possess a basis of $r$ elements $\tau_1, \tau_2, \cdots, \tau_r$, as asserted (Vol. I, Ch. IV, § 15, Lemma 2).

Example 2. Generalized power series expansions. Consider formal power series $z(t) = a_0 t^{y_0} + a_1 t^{y_1} + \cdots + a_n t^{y_n} + \cdots$, where the coefficients $a_n$ are in $k$ and the exponents $y_n$ are real numbers such that $y_0 < y_1 < \cdots$, and $\lim y_n = \infty$. These power series with the usual formal rules for addition and multiplication form a field $k\{t\}$. This field admits a natural valuation $V$, of rank 1, defined by setting $V(z(t)) = y_0$, if $a_0 \neq 0$. Any isomorphism of $k(x_1, x_2, \cdots, x_r)$ into $k\{t\}$ will therefore yield a rank 1 valuation of $k(x_1, x_2, \cdots, x_r)$. Any such isomorphism is obtained by choosing for each variable $x_i$ a power series $z_i(t)$ in $k\{t\}$ such that the $r$ power series $z_1(t), z_2(t), \cdots, z_r(t)$ are algebraically independent. The valuations thus obtained are all zero-dimensional and have $k$ as residue field. In particular, if the $z_1(t), z_2(t), \cdots, z_r(t)$ are power series with integral exponents, so that the "one-dimensional arc" $x_i = z_i(t)$ ($i = 1, 2, \cdots, r$) is analytic and does not lie on any proper algebraic subvariety of the affine $r$-space, then we get a discrete zero-dimensional valuation of $k(x_1, x_2

ideal $p$ is minimal, in which case $v'$ is necessarily the prime divisor of center $p$.

Example 3. Real valuations with preassigned value group. Let

$$z_i(t) = a_{0i}t^{y_{0i}} + a_{1i}t^{y_{1i}} + \cdots + a_{ni}t^{y_{ni}} + \cdots,$$

where we assume that the power series $z_i(t)$ are algebraically independent. MacLane and Schilling have proved (see their joint paper "Zero-dimensional branches of rank 1 on algebraic varieties," Annals of Mathematics, v. 40 (1939), pp. 507–520) that if all the $a_{ni}$ are $\neq 0$, if $k$ is of characteristic zero and if the exponents $y_{ni}$ are rational linear combinations of $s+1$ given real numbers $1, \tau_1, \tau_2, \cdots, \tau_s$, then the field $k(t, t^{\tau_1}, t^{\tau_2}, \cdots, t^{\tau_s}, z_1(t), z_2(t), \cdots, z_r(t))$ has in the natural valuation $V$ a value group generated by $1, \tau_1, \tau_2, \cdots, \tau_r$ and all the exponents $y_{ni}$ of the given $r$ series $z_i(t)$. From this result one can easily obtain the existence of a rank 1 valuation of $k(x_1, x_2, \cdots, x_r)$ with any preassigned value group $\Gamma$ of rational rank $s+1$ less than $r$. For, let $1, \tau_1, \tau_2, \cdots, \tau_s$ be $s+1$ rationally independent elements of $\Gamma$ (we may assume, as we did, that one of these real numbers is 1). Since every element of $\Gamma$ is rationally dependent on $1, \tau_1, \tau_2, \cdots, \tau_s, \Gamma$ is a denumerable set. We can therefore find $r-s-1$ power series $z_i(t

that the ideal $q_h$ generated by $u_1, u_2, \cdots, u_h$ in $R_h = k[u_1, u_2, \cdots, u_h]$ is the unit ideal. Now, we have $u_i \in k[u_{i+1}, u_{i+2}]$, for all $i$, and furthermore $u_i$ belongs to the ideal generated by $u_{i+1}, u_{i+2}$ in $k[u_{i+1}, u_{i+2}]$. It follows that $R_h = k[u_{h-1}, u_h]$ and that $q_h = R_h(u_{h-1}, u_h)$. Since $u_{h-1}, u_h$ are algebraically independent over $k$, the relation $1 \in q_h$ is impossible.

Since $q$ is a proper (maximal) ideal, there exists a valuation $v$ of $k(x_1, x_2)$ such that $v$ is non-negative on $R$ and has center $q$ in $R$. Let $v$ be such a valuation. Since $v(u_{i+2}) > 0$, it follows that $v(u_i - c_i u_{i+1}^m) > v(u_{i+1}^m)$, whence $v(u_i) = m_i v(u_{i+1})$. In particular,

(1) $v(u_1) = m_1 m_2 \cdots m_s v(u_{s+1})$.

Since $m_1 m_2 \cdots m_s \to \infty$, it follows that $v$ is non-discrete, therefore of rank 1, and necessarily of rational rank 1, for (1) shows that $v$ cannot be isomorphic with a direct product of two free cyclic groups. If we normalize the value group $\Gamma$ of $v$ by setting $v(u_1) = 1$, then (1) shows that $\Gamma$ contains all the rational numbers having denominator $m_1 m_2 \cdots m_s$, $s = 1, 2, \cdots$. We shall now show that $\Gamma$ is actually the set of all rational numbers of the form $\frac{n}{m_

assertion concerning the value group $\Gamma$ we have only to show the following: if $f(u_1, u_2)$ is any polynomial in $k[u_1, u_2]$, then for $h$ sufficiently large we will have $f(u_1, u_2) = u_h^n f_h(u_h, u_{h+1})$, $f_h(0, 0) \neq 0$. To show this, we fix a positive integer $m$, sufficiently large, so as to satisfy the inequality $v(u_1^m) \geq v(f(u_1, u_2))$, and we set $\xi = u_1^m / f(u_1, u_2)$. Then $\xi \in K_t$ and hence, by (2), $\xi \in (R_h)_{q_h}$, for large $h$, i.e., we have

(3) $u_1^m / f(u_1, u_2) = A(u_h, u_{h+1}) / B(u_h, u_{h+1})$, $B(0, 0) \neq 0$.

Now, $u_1$, as a polynomial in $u_h, u_{h+1}$, has the form $u_1 = u_h^o \varphi(u_h, u_{h+1})$, where $\varphi(0, 0) \neq 0$. It follows then from (3) that

$$f(u_1, u_2) A(u_h, u_{h+1}) = u_h^{om} B(u_h, u_{h+1}) [\varphi(u_h, u_{h+1})]^m$$

$$= u_h^{om} C(u_h, u_{h+1})$$

$C(0, 0) \neq 0$,

and therefore, if $f(u_1, u_2)$ is expressed as a polynomial in $u_h, u_{h+1}$, its only irreducible factor which vanishes at $u_h = u_{h+1} = 0$ (if $f(u_1, u_2)$ has such a factor) must be $u_h$. In other words, $f$ must be of the form $u_h^n f_h(u

jugates of $w$ over $k(x_1)$: $w_i = a_1^{(i)}x_1 + a_2^{(i)}x_1^2 + \cdots + a_{n-1}^{(i)}x_1^{n-1}$. Let $f(t) = \prod_{i=1}^{g} (t-w_i)$, $\xi = f(x_2) = F(x_1, x_2) \in k[x_1, x_2]$. Then $F(x_1, z(x_1)) = a_nx_1^n \cdot (1 + \text{terms of degree } > 1) \cdot \prod_{i=2}^{g} \{(a_1 - a_1^{(i)})x_1 + \cdots + (a_{n-1} - a_{n-1}^{(i)})x_1^{n-1} + a_nx_1^n + \cdots\}$, which shows that the leading term of the power series $F(x_1, z(x_1))$ is of the form $a_nbx_1^h$, $h \geq n$, where $b$ is an element of the field $k(a_1, a_2, \cdots, a_{n-1})$. Since $a_nb$ is the residue of $\xi/x_1^h$, it follows that $a_n$ belongs to the residue field of $v$.

[It now follows a posteriori that our branch is non-algebraic, since the residue field of a zero-dimensional, rank 2, valuation of $k(x_1, x_2)$ is always finitely generated over $k$, by Theorem 31, Corollary, § 14.]

In the following example, $k$ may be algebraically closed, and we are dealing with a function field $k(x_1, x_2, x_3)$ of three independent variables. In this case we can construct a 1-dimensional valuation whose residue field is not a finitely generated extension of $k$ (contrary to what happens in the case of prime divisors; see § 14, Theorem 31). We simply set, for instance: $x_3 = x_