If a local domain $A$ satisfies condition (D), then it is analytically unramified.

Proof. Let $a$ be a nilpotent element of $\hat{A}$. For every element $x \neq 0$ of $A$, we have that $x$ is not a zero-divisor in $\hat{A}$ (Corollary 6 to Theorem 11, §4), whence $a/x$ is an element of the total quotient ring of $\hat{A}$. Since we have $(a/x)^q = 0$ for some exponent $q$, $a/x$ is integral over $\hat{A}$. Using condition (D), we see that $da/x \in \hat{A}$, $d$ being an element $\neq 0$ of $A$ independent of $x$. Therefore the element $da$ belongs to all the principal ideals $\hat{A}x$ ($x \in A$, $x \neq 0$). If $A$ is not a field, we fix an element $y \neq 0$ in the maximal ideal $m$ of $A$, and we apply the above result to the principal ideals $\hat{A}y^n$, $n=1, 2, \cdots$. We then have $da \in \hat{A}m^n$ for every $n$, whence $da=0$, and therefore $a=0$ since $d$ is not

this has been proved. Then it will follow that $\bar{\mathfrak{p}}_i$ is a prime ideal of height 1 of $\hat{A}$, and that the ideals which are primary for $\bar{\mathfrak{p}}_j$ are its symbolic powers. Hence we will have

(1) $\hat{A}d = \bigcap_j \bar{\mathfrak{p}}_j^{(s(j))}$.

We denote by $v_j$ the normalized valuation of $\hat{A}_{\mathfrak{p}_j}$ and by $w_j$ the function on $\hat{A}$ defined by $w_j(x) = v_j(\varphi_j(x))$, $\varphi_j$ denoting the canonical homomorphism of $\hat{A}$ into $\hat{A}_{\mathfrak{p}_j}$. The function $w_j$ takes the value $+\infty$ on the kernel of $\varphi_j$, and satisfies the same relations as a valuation does:

(2) $w_j(xy) = w_j(x) + w_j(y), \quad w_j(x+y) \geq \min(w_j(x) w_j(y))$.

Furthermore the symbolic power $\bar{\mathfrak{p}}_j^{(s)}$ is the set of all elements $x$ of $\hat{A}$ such that $w_j(x) \geq s$; it follows that $s(j) = w_j(d)$. This being so, we come back to the element $z$ of $(\hat{A})'$, and write an equation of integral dependence for $z$ over $\hat{A}$:

(3) $z^n + a_{n-1}z^{n-1} + \cdots + a_1z + a_0 = 0 \quad (a_i \in \hat{A})$.

The element $y = dz$ belongs to $\hat{A}$ and we have

(4) $-y^n = a_{n-1}dy^{n-1} + \cdots + a_1d^{n-1}y + d^n a_0$.

If we set $w_j(y) = \alpha$ and $w_j(d) = \beta$, (2) shows that

$n\alpha \

since $A_p$ is a discrete valuation ring, $\mathfrak{p}$ is an isolated primary component of $Aa$, and there exists an element $x''$ of $A$ such that $x'' \notin \mathfrak{p}$ and $x''\mathfrak{p} \subset Aa$. Since $x''$ is not a zero divisor mod $\hat{A}_p$ (Corollary 6 to Theorem 11, § 4), we have $x'' \notin \bar{\mathfrak{p}}, \dagger$ whence the element $x = x'x''$ does not belong to $\bar{\mathfrak{p}}$. On the other hand we have $x\bar{\mathfrak{p}} = x''x' \bar{\mathfrak{p}} \subset x''\hat{A}_p \subset \hat{A}_a$. Denoting by $\varphi$ the canonical homomorphism of $\hat{A}$ into $\hat{A}_p$, we deduce that $\varphi(x)\bar{\mathfrak{p}}\hat{A}_p \subset \varphi(a)\hat{A}_p$. Since $x \notin \bar{\mathfrak{p}}, \varphi(x)$ is a unit in $\hat{A}_p$, and, since $a \in \mathfrak{p} \subset \bar{\mathfrak{p}}$, the last relation shows that the maximal ideal $\bar{\mathfrak{p}}\hat{A}_p$ is the principal ideal generated by $\varphi(a)$. Therefore $\hat{A}_p$, and similarly every $\hat{A}_p_j$, is a discrete valuation ring.

Now we prove that we not only have $\hat{A}_p = \bigcap \bar{\mathfrak{p}}_j$, but also

$$\hat{A}_p^{(n)} = \bigcap_j \bar{\mathfrak{p}}_j^{(n)}.$$

This we prove by induction on $n$. The proof of the inclusion $\mathfrak{p}^{(n)} \subset \bar{\mathfrak{p}}_j^{(n)}$ is straightforward (we recall that $\mathfrak{p} = A

and 1 (since $e$ and $1-e$ would then both be non-units). Hence $S$ is a field, and $\hat{A}$ has no zero divisors. This completes the proof of Lemma 2.

REMARK. We have only used the hypothesis (D) for $A$ and for the factor rings $A/\mathfrak{p}$, where $\mathfrak{p}$ is a prime ideal of $Ad$.

In the next lemma we use, for avoiding typographical complications, the notation $c(B)$ for the completion of a semi-local ring $B$, and the notation $R'$ for the integral closure of a ring $R$ in its total quotient ring.