The Chern character is stable, and it can be viewed as a morphism $ch: K(-) \rightarrow H^{\text{ev}}(-, \mathbf{Q})$.

8.3 Example. Under the bijection $m: [\text{Vect}_R^+(-), H^{\text{ev}}(-, \mathbf{Z})]_{+, \times} \rightarrow Z^\pm[[t]]$, the Euler class corresponds to $t$. By the uniqueness statement, this need be checked only on 2-plane bundles where it is clear. Similarly, the total Pontrjagin class corresponds to $1 + t^2$ and the top Pontrjagin class to $t^2$.

If the first vertical arrow represents the function induced by $\varepsilon_0$, restriction of scalars from $\mathbf{C}$ to $\mathbf{R}$, there is the following commutative diagram from Theorem (7.1).

$$
\begin{array}{c}
[\text{Vect}(-), H^{\text

8.6 Examples. For complex vector bundles, the $L$-genus is defined to be the characteristic class corresponding to $t/\tanh t$, the $A$-genus is defined to be the characteristic class corresponding to $t/\sinh t$, and the Todd class is the characteristic class corresponding to $t/1 - e^{-t}$. For real oriented vector bundles, the $\hat{A}$-genus is the characteristic class corresponding to $(t/2)/(\sinh t/2)$. For manifolds these characteristic classes are evaluated on the top class of the manifold to give a number, also called the $L$-genus, $A$-genus and $\hat{A}$-genus respectively.

9. Bott Periodicity and Integrality Theorems

In this section we relate the Chern character to the complex periodicity and prove the Bott integrality theorem. In doing this, we given an alternative proof of the complex periodicity theorem.

Let $\gamma$ denote the canonical line bundle (or hyperplane bundle) over $S^2 = CP^1$. Then, from the results in Chap. 11, 1 and $\gamma - 1$ form an additive base for $K(S^2)$. All $K$-groups are complex $K$-groups.
