The group $\mathfrak{G}$ of all units has a finite basis, and the number $k$ of basis elements of infinite order is $\leq r$.

For the proof let $\varepsilon_1, \ldots, \varepsilon_k$ be $k$ units of infinite order and suppose there do not exist $k + 1$ independent elements of infinite order. Then, by (b) and (c), for each unit $\eta$ in $K$ a system of equations

$$\log|\eta^{(i)}| = \sum_{m=1}^{k} \frac{g_m}{M} \log|\varepsilon_m^{(i)}| \quad (i=1, 2, \ldots, n)$$

holds, for a certain positive rational integer $M$, where the $g_m$ are rational integers. From this it follows by Lemma (a) that

$$\eta^M = \varepsilon_1^{g_1} \varepsilon_2^{g_2} \cdots \varepsilon_k^{g_k} \zeta,$$

where $\zeta$ is a root of unity in $K$, that is, a $w$th root of unity. Hence we have

$$\eta = \varepsilon_1^{g_1/M} \varepsilon_2^{g_2/M} \cdots \varepsilon_k^{g_k/M} \zeta_0^x,$$

where $\zeta_0 = e^{2\pi i/Mw}$, with rational integral $x$. We now consider the totality of products of powers of the $k + 1$ numbers

$$H_1 = \varepsilon_1^{1/M}, \quad \ldots, H_k = \varepsilon_k^{1/M}, \quad H_{k+1} = \zeta_0$$

with arbitrary but fixed values of the roots. The set of these numbers form a (mixed) Abelian group for which $H_1, \ldots, H_{k+1}$ is a basis. By what has already been proved, the group $\mathfrak{G}$ of all units of $K$ is contained as a subgroup, and indeed as a subgroup of finite index, since the $M

Lemma (a). If $r = 0$, the group $\mathfrak{E}$ is identical to the group $\mathfrak{W}$ of the roots of unity in $K$.

For in the imaginary quadratic field it follows immediately from $N(\varepsilon) = \pm 1$ that $\varepsilon^{(1)} \cdot \varepsilon^{(2)} = +1$, and since $|\varepsilon^{(1)}| = |\varepsilon^{(2)}|$, this unit, along with its conjugate has absolute value 1; hence this unit is a root of unity.

Lemma (b). If $r > 0$, then to each system of real numbers $c_1, \ldots, c_r$, not all vanishing, there is associated a unit $\varepsilon$ such that

$$L(\varepsilon) = c_1 \log|\varepsilon^{(1)}| + c_2 \log|\varepsilon^{(2)}| + \cdots + c_r \log|\varepsilon^{(r)}| \neq 0.$$

This second important conclusion in Dirichlet’s train of thought rests on Minkowski’s Theorem 95.

If $\varkappa_1, \ldots, \varkappa_n$ are $n$ positive quantities such that

$$\varkappa_1 \cdot \varkappa_2 \cdots \varkappa_n = |\sqrt{d}|,$$

$$\varkappa_{p+r_2} = \varkappa_p \quad \text{for } p = r_1 + 1, \ldots, r_1 + r_2,$$

then by Theorem 95 there is a nonzero integer $\alpha$ in $K$ (whose norm thus has at least absolute value 1) such that

$$|\alpha^{(i)}| \leq \varkappa_i \quad \text{for } i = 1, 2, \ldots, n, 1 \leq |N(\alpha)| \leq \sqrt{d}.$$

From this it follows that

$$|\alpha^{(i)}| \geq \frac{1}{|\alpha^{(1)}| \cdot |\alpha^{(2)}| \cdots |\alpha^{(i-1)}| \cdot |\alpha^{(i

and for the corresponding $\alpha_h$ we have

$$\left| L(\alpha_h) - 2Ah \right| < A$$
$$A(2h - 1) < L(\alpha_h) < A(2h + 1).$$

Consequently

$$L(\alpha_1) < L(\alpha_2) < L(\alpha_3) \ldots$$

(62)

while at the same time

$$\left| N(\alpha_h) \right| \leq \left| \sqrt{d} \right|.$$

These infinitely many principal ideals $(\alpha_h)$ whose norms are not greater than $\sqrt{d}$, cannot all be distinct; hence there must exist at least two distinct indices $h$ and $m$ such that

$$(\alpha_h) = (\alpha_m),$$ hence $\alpha_m = \varepsilon\alpha_h,$

where $\varepsilon$ is a unit in $k$. For this $\varepsilon$, by (62),

$$L(\alpha_h) \neq L(\alpha_m) = L(\varepsilon\alpha_h)$$
$$L(\varepsilon) = L(\varepsilon\alpha_h) - L(\alpha_h) \neq 0,$$

and Lemma (b) is proved. From this we obtain
