** Let $\mathcal{O}$ denote the family of all open subsets of $R.$ Then:

(i) $\varnothing \in \mathcal{O}$ and $R \in \mathcal{O};$
(ii) if $\mathcal{U}$ is a subfamily of $\mathcal{O},$ then $\bigcup \mathcal{U} \in \mathcal{O}^1;$
(iii) if $\{U_1, U_2, \ldots, U_n\} \subset \mathcal{O},$ then $U_1 \cap U_2 \cap \cdots

showing the simple nature of such ideas as continuity. Also by the addition of only two more axioms, we obtain a class of topological spaces in which many of the processes of analysis can be carried out with great profit. We first give a few examples of topological spaces.

(6.5) Examples. (a) Naturally, the real line $R$ with the topology described in (6.2) and (6.3) is a topological space. This topology for $R$ is known as the usual topology for $R$. We will always suppose that $R$ is equipped with its usual topology unless the contrary is specifically stated.

(b) Consider $R^{\#}$ and the family $\mathcal{O}^{\#}$ of all sets having any of the following four forms: $U, U \cup ]t, \infty]$, $U \cup [-\infty, s[, U \cup [-\infty, s[]t, \infty]$, where $U$ is an open subset of $R$ and $s, t \in R$. Then $(R^{\#}, \mathcal{O}^{\#})$ is a topological space; $\mathcal{O}^{\#}$ is called the usual topology for $R^{\#}$.

(c) Let $X$ be any set. The pair $(X, \mathcal{P}(X))$ is a topological space, obviously. The family $\mathcal{P}(X)$ is called the discrete topology for $X$. A set $X$ with the discrete topology will frequently be denoted by $X_d$.

(d) Let $X$ be any set and let $\mathcal{O} = \{X, \emptyset\}$. Then $\mathcal{O}$ is called the indiscrete [or concrete] topology for $X$. This topology is of little interest to us.

We proceed to the definition of various topological concepts from our basic notion of open sets.

(6.6) Definitions. Let $X$ be a topological space. A neighborhood of a point $x \in X$ is any open subset $U$ of $X$ such that $x \in U$. The space $X$ is known as a Hausdorff space if each pair of distinct points of $X$ have disjoint neighborhoods. A set $A \subset X$ is said to be closed if

(viii) $(A \cup B)^{-} = A^{-} \cup B^{-}$;
(ix) $(A \cap B)^{\circ} = A^{\circ} \cap B^{\circ}$.

For an arbitrary family $\{A_i\}$ of subsets of $X$, we have:
(x) $\cup A_i^{-} \subset (\cup A_i)^{-}$;
(xi) $\cap A_i^{\circ} \supset (\cap A_i)^{\circ}$.

Finally,
(xii) $\varnothing$ and $X$ are closed.