Let $E$ be a simple $K[G]$-module, and let $P$ be a lattice in $E$ stable under $G$. Assume that the dimension $N$ of $E$ is divisible by the largest power $p^n$ of $p$ dividing the order $g$ of $G$. Then:

(a) $P$ is a projective $A[G]$-module.

(b) The canonical map $A[G] \rightarrow \text{End}_A(P)$ is surjective, and its kernel is a direct factor in $A[G]$ (as a two-sided ideal).

(c) The reduction $\bar{P} = P/mP$ of $P$ is a simple and project

16.4: Examples of projective A[G]-modules

EXAMPLE. If G is a semisimple linear group over a finite field of characteristic $p$, there exists a linear irreducible representation of G (over Q) whose degree is equal to $p^n$; it is the special representation of G discovered by R. Steinberg (cf. Canad. J. of Math., 8, 1956, p. 580–591 and 9, 1957, p. 347–351). By a result of Solomon–Tits it may be realized as the homology representation of top dimension for the Tits building associated with $G^*$.

EXERCISES

16.8. Take $G = \mathfrak{A}_4$, cf. 5.7. Show that, for $p = 2$, the group G has no irreducible representation of the type described by prop. 46, but that there is such a representation for $p = 3$. Same question for $\mathfrak{S}_4$.

16.9. Let $S \in S_k$. Prove the equivalence of the following properties:
(i) S is a projective $k[G]$-module.
(ii) S is isomorphic to the reduction mod. m of a module P satisfying the conditions of prop. 46.
(iii) The diagonal coefficient $C_{SS}$ of the Cartan matrix of G is equal to 1. (For the equivalence of (i) and (iii), see ex. 15.7.)

* Cf. L. Solomon, The Steinberg character of a finite group with a BN-pair. Theory of Finite Groups, edited by R. Brauer and C.-H Sah. W. A. Benjamin, New York, 1969, p. 213–221.
