If $K^\star$ is an algebraic extension of $K$, then every element of the quotient group $\Gamma^\star/\Gamma$ has finite order (and the two groups $\Gamma$ and $\Gamma^\star$ have therefore the same rational rank).

Proof. Let $\alpha^\star$ be an arbitrary element of $\Gamma^\star$. We have to show that there exists an integer $s \neq 0$ such that $s\alpha^\star \in \Gamma$. We fix an element $z$ of

We next show that our mapping $\Delta^\star \rightarrow \Delta$ is univalent. We observe that if $\alpha^\star$ is any element of $\Delta^\star$, then all integral multiples of $\alpha^\star$ belong to $\Delta^\star$, while, by Lemma 1, some multiple $s\alpha^\star$, $s \neq 0$, belongs to $\Gamma$ and hence also to $\Delta$. Conversely, if $\alpha^\star$ is an element of $\Gamma^\star$ such that $s\alpha^\star \in \Delta$ for some integer $s \neq 0$, then $s\alpha^\star \in \Delta^\star$ and therefore $\alpha^\star \in \Delta^\star$ (since $\Delta^\star$ is a segment). We have thus shown that $\Delta^\star$ is uniquely determined by $\Delta$ as the set of all $\alpha^\star$ in $\Gamma^\star$ such that $s\alpha^\star \in \Delta$ for some integer $s \neq 0$. Hence, our mapping $\Delta^\star \rightarrow \Delta$ is univalent, and it is clearly order preserving. Finally, if $\Delta$ is an arbitrary isolated subgroup of $\Gamma$, then it is immediately seen that the set $\Delta^\star$ of elements $\alpha^\star$ in $\Gamma^\star$ such that $s\alpha^\star \in \Delta$, for some integer $s \neq 0$, is an isolated subgroup of $\Gamma^\star$ and that $\Delta^\star \cap \Gamma = \Delta$. Hence our mapping is onto the set of isolated subgroups of $\Gamma$, and the lemma is proved.

Corollary. If $K^\star$ is a finite algebraic extension of $K$ then $v^\star$ is discrete if $v$ is discrete (we recall that it is implicit in our definition of a discrete valuation that any such valuation is of finite rank).

For, let $n$ be the relative degree $[K^\star:K]$. The proof of Lemma 1 shows that if we let $N=n!$, then $N\alpha^\star \in \Gamma$ for all $\alpha^\star$ in $\Gamma^\star$. Let $\Delta_i^\star$ and $\Delta_{i+1}^\star$ be two consecutive

v* be valuations of K and K* respectively, such that v* is an extension of v. Let Γ and Γ* be the value groups of v and v* respectively. Then the index e of the subgroup Γ of Γ* is called the reduced ramification index of v* with respect to v, or relative to v (or with respect to K).

If K* is a finite algebraic extension of K, we can speak of the relative degree of a valuation v* of K*, meaning by this the relative degree of any place associated with v* (see § 6). If v is the restriction of v* to K, then the residue field $R_v / \mathfrak{M}_v$ of v is (or can be canonically identified with) a subfield of the residue field $R_{v^*} / \mathfrak{M}_{v^*}$ of v*, and the relative degree of v* is the relative degree $[R_{v^*} / \mathfrak{M}_{v^*}:R_v / \mathfrak{M}_v]$.

We know that this relative degree is at most equal to $[K^*:K]$ (§ 6, Lemma 2, Corollary 2).

The relative degree of v* shall be denoted by f. If K* is a separable extension of K we also define the ramification index of v* relative to v as the product ep$, where ep$^s$ is the inseparable factor of f.

It is easy to see that the above terminology agrees with terminology introduced for Dedekind rings in the preceding chapter. For, assume that we have the following special case: K is the quotient field of a Dedekind domain R and v is the p-adic valuation of K defined by a proper prime ideal p in R. If $R'$ denotes the integral closure of R in K*, then the valuation ring of v* contains $R'$. Since $R'$ is a Dedekind domain (Vol. I, Ch. V, § 8, Theorem 19), v* is necessarily a p-adic valuation of K*, where p is a prime ideal in $R'$ lying over p. Let $e_1$ be the reduced ramification index of p with respect to p. If u is an

extension of $v_1$ to $K^\star$ and $\bar{v}^\star$ is any extension of $\bar{v}$ to the residue field of $v_1^\star$, then $v^\star = v_1^\star \circ \bar{v}^\star$ is an extension of $v$ to $K^\star$, and if $H^\star$ is the isolated subgroup of the value group of $v^\star$ which corresponds to the decomposition $v_1^\star \circ \bar{v}^\star$, then $H^\star \cap \Gamma = G$.