If $\mathfrak{A}$ is a $v$-ideal (different from (0)) there exist two consecutive $v_1$-ideals $\mathfrak{B}_1$ and $\mathfrak{B}_2$ such that $\mathfrak{B}_1 \supset \mathfrak{A} > \mathfrak{B}_2$, and we have $\mathfrak{B}_1\mathfrak{p}^\rho \subset \mathfrak{A}$ for some integer $\rho \geq 0$. The number of $v$-ideals between $\mathfrak{B}_1$ and $\mathfrak{A}$ is finite.

Proof. Since $R$ is noetherian, every ideal $\mathfrak{A}$ in $R$ is finitely generated and therefore $v$ admits, on $\mathfrak{A}$, a smallest value. As in Appendix 2, we denote this smallest value by $v(\mathfrak{A})$.

Let $\mathfrak{B}_2$ be the first (i.e., the largest) $v_1$-ideal which is a proper subideal of $\mathfrak{A}$. Let $\mathfrak{B}_1 =

and $\mathfrak{p}$ is maximal in $R$; see Vol. I, Ch. IV, ┬¦ 2, Theorem 2). Since $\mathfrak{B}/\mathfrak{Bp}^q$ is a finite $(R/\mathfrak{p}^q)$ module, it has a composition series (Vol. I, Ch. III, ┬¦ 10, Theorem 18). It follows that any descending chain of ideals between $\mathfrak{B}$ and $\mathfrak{Bp}^q$ is finite. In particular, there can only be a finite number of $v$-ideals between $\mathfrak{B}_1$ and $\mathfrak{A}$, since $\mathfrak{A} \supset \mathfrak{B}_1\mathfrak{p}^o$. This completes the proof of Lemma 4.

Corollary. If $\mathfrak{B}_1$ and $\mathfrak{B}_2$ are two consecutives $v_1$-ideals $(\mathfrak{B}_1 > \mathfrak{B}_2)$ then the $v$-ideals $\mathfrak{A}$ such that $\mathfrak{B}_1 \supset \mathfrak{A} > \mathfrak{B}_2$ are finite in number if $\mathfrak{p}$ is also the center of $v_1$, and form a simple infinite sequence in the contrary case.

For, if $\mathfrak{p}$ is the center of $v_1$ then we have seen that $\mathfrak{A} \supset \mathfrak{B}_1\mathfrak{p}$ if $\mathfrak{B}_1 \supset \mathfrak{A} > \mathfrak{B}_2$. If $\mathfrak{p}$ is not the center of $v_1$, then the assertion follows from the last part of the lemma and from the fact that the $v$-ideals $(R_v\mathfrak{B}_1\mathfrak{p}^q) \cap R, q=1, 2, \cdots$, are all distinct and lie between $\mathfrak{B}_1$ and $\mathfrak{B}_2$

We denote by $p'_0, p'_1, \cdots, p'_{g-1}$ the distinct prime ideals in the set $\{M_1 \cap R, M_2 \cap R, \cdots, M_{r-1} \cap R\}$ (we assume that we have $p'_0 > p'_1 > \cdots > p'_{g-1}$).

Case (a): $B_1 = A$. If $M \cap R = M_1 \cap R$ then $g = h$ and $p'_i = p_i$. From Lemma 4 and its Corollary follow that in this case the set of $v_1$-ideals preceding $A$ has ordinal type of the form $m'_0 \omega^{h_0} + m'_1 \omega^{h_1} + \cdots + m'_q \omega^{h_q}$, where the $m'_q$ are positive integers. Hence, by our induction hypothesis, the prime ideals of $A$ are $p'_h_0, p'_h_1, \cdots, p'_h_q$, i.e., $p_{h_0}, p_{h_1}, \cdots, p_{h_q}$. If $M \cap R \neq M_1 \cap R$, then the ordinal type of the set of $v_1$-ideals preceding $A$ must be equal to $m_0 \omega^{h_0-1} + \cdots + m_q \omega^{h_q-1}$ (always by Lemma 4 and its Corollary; note that, by the Corollary, $A$ can have in this case no immediate predecessor in this set of $v$-ideals, whence $h_q > 0$). Hence $p'_{h_0-1}, p'_{h_1-1}, \cdots, p'_{h_q-1}$ are the prime ideals of $A$, and since we have obviously $p'_i = p_{i+1}$ in the present case, the proof of our proposition is complete in Case (a).

Case (b): $B_1 > A$. In this case, $A$ has an immediate