In other words, there is one nonvanishing homotopy group and it is degree $n$. This means that $\Pi$ must be abelian for $n > 1$, but $\Pi$ can be any group for $n = 1$, and for $n = 0$ we can choose $\Pi$ to be any set. Since a $K(\Pi, n)$ is path connected, we can use any base point for $n > 0$.

4.2 Remark. For any abelian group $\Pi$ and any $n \geq 0$ there exists an abelian topological group $A$ which is a $K(\Pi, n)$ as a space. Moreover, the classifying space $B(A) = BK(\Pi, n) = K(\Pi, n + 1)$, which gives an inductive construction of $K(\Pi, n)$ as an abelian group using a classifying space construction which preserves products, and the loop space $\Omega K(\Pi, n) = K(\Pi, n - 1)$ from the homotopy exact triangle for a fibre sequence. Note that we have used the symbol $K(\Pi, n)$ for both the space and the type of space that it is.

4.3 Remark. Any abelian topological group $A$ is a product of $K(\Pi, n)$ spaces as a commutative $H$-space up to homotopy, and indeed up to higher homotopies. This is a theorem of J. C. Moore which was proved in the simplicial set/group context, see H. Cartan Seminaire 1954–55. This is also a reference for (4.2).

4.4 Remark. The first nonzero reduced cohomology group of a $K(\Pi, n)$ is in degree $n$ where $H^n(K(\Pi, n), \Pi) = \text{Hom}(\Pi, \Pi)$ which has a canonical element $\iota_n$ corresponding to the identity on $\Pi$. Using $\iota_n$, we define a natural morphism of abel

application of the theorem of J. C. Moore cited in (4.3) applied to the abelian group structure defined by multiplication of the abelian group valued functions gives that this space is a product of $K(\Pi, q)$ spaces. The groups arising are given in the following theorem of René Thom.
