From this point of view of much interest are the instances, where random processes having desired properties can be built constructively, and with minimal use of “probabilistic structures.”

To demonstrate such possibilities, consider the so-called renewal processes. (A particular case of them is the Poisson process; see Sect. 10 of Chap. 7, Vol. 2.)

Let $(\sigma_1, \sigma_2, \ldots)$ be a sequence of independent identically distributed positive random variables with distribution function $F = F(x)$. (The existence of such a sequence follows from Corollary 1 to Theorem 1.)

Based on $(\sigma_1, \sigma_2, \ldots)$, we form a new sequence $(T_0, T_1, \ldots)$ with $T_0 = 0$ and

$$T_n = \sigma_1 + \cdots + \sigma_n, \quad n \geq 1.$$

For illustrative purposes, let us think of $T_n$ as the time instant of, say, the $n$th telephone call. Then $\sigma_n$ is the time between the $(n-1)$th and $n$th calls.

The random process $N = (N_t)_{t \geq 0}$ with constructively specified random variables

$$N_t = \sum_{n=1}^{\infty} I(T_n \leq t)$$

is referred to as a renewal process.

Clearly, $N_t$ could also be defined as

$$N_t = \max\{n : T_n \leq t\},$$

i.e., $N_t$ is the number of calls that occur in the time interval $(0, t]$, and it is obvious that

$$\{N_t \geq n\} = \{T_n \leq t\}.$$

This simple formula is very useful because it reduces the study of probabilistic properties of the process $N = (N_t)_{t \geq 0}$ to the treatment of the variables $T_n = \sigma_1 + \cdots + \sigma_n$, which are sums of independent random variables $\sigma_1, \ldots, \sigma_n, n \geq 1$ (see Subsection 4 in Sect. 3 of Chapter 4 and Subsection

2. Verify the consistency of the families of distributions in the corollaries to Theorems 1 and 2.
3. Deduce Corollary 2, Theorem 2, from Theorem 1.
4. Let $F_n$ denote the distribution function of $T_n$, $n \geq 1$ (see Subsection 4). Show that $F_{n+1}(t) = \int_0^t F_n(t-s) dF(s)$, $n \geq 1$, where $F_1 = F$.
5. Show that $P\{N_t=n\} = F_n(t) - F_{n+1}(t)$ (see (17)).
6. Show that the renewal function $m(t)$ defined in Subsection 4 satisfies the renewal equation
$$m(t) = F(t) + \int_0^t m(t-x) dF(x).$$
7. Show that the function defined by (20) is a unique solution of the equation (21) within the class of functions bounded on finite intervals.
8. Let $T$ be an arbitrary set.
   (i) Suppose that for every $t \in T$ a probability space $(\Omega_t, \mathcal{F}_t, P_t)$ is given. Put $\Omega = \prod_{t \in T} \Omega_t$, $\mathcal{F} = \bigotimes_{t \in T} \mathcal{F}_t$. Prove that there is a unique probability measure $P$ on $(\Omega, \mathcal{F})$ such that
$$P\left(\prod_{t \in T} B_t\right) = \prod_{t \in T} P(B_t),$$
where $B_t \in \mathcal{F}_t$, $t \in T$, and $B_t = \Omega_t$ for all but finitely many $t$. (Hint. Specify $P$ on an appropriate algebra and use the method of the proof of Ionescu Tulcea’s theorem.)
(ii) Let for every $t \in T$ a measurable space $(E_t, \mathcal{E}_t)$ and a probability measure $P_t$ on it be given. Show that there is a probability space $(\Omega, \mathcal{

$$P \left( \left| \frac{S_n}{n} - p \right| > \varepsilon \right) \to 0, \quad n \to \infty$$

(see Sect. 5 of Chap. 1). In analysis this is known as convergence in measure.
