Let $(X, \mathbf{S}, \mu)$ and $(Y, \mathbf{T}, \nu)$ be measure spaces, and let $(\dot{\mathbf{S}}, \dot{\mu})$ and $(\dot{\mathbf{T}}, \dot{\nu})$, respectively, be their measure rings. A one-to-one mapping $\Phi$ of $\dot{\mathbf{S}}$ onto $\dot{\mathbf{T}}$ is said to be a weak measure ring isomorphism if

(i) $\Phi([E] \setminus [F]) = \Phi([E]) \setminus \Phi([F])$ for every pair $[E], [F]$ in $\dot{\mathbf{S}}$, and

(ii) $\Phi(\bigvee_{n=1}^{\infty} [E_n]) = \bigvee_{n=1}^{\infty} \Phi([E_n])$ for every sequence $\{[E_n]\}_{n=1}^{\infty}$ in $\dot{\mathbf{S}}$.

(It is easy to see that a weak measure ring isomorphism preserves all Boolean operations; cf. the proof of Theorem 9.10.) If $\Phi$ is a weak measure ring isomorphism of $(\dot{\mathbf{S}}, \dot{\mu})$ onto $(\dot{\mathbf{T}}, \dot{\nu})$ satisfying the further condition

(iii) $\dot{\nu}(\Phi([E])) = \dot{\mu}([E])$, $\quad [E] \in \dot{\mathbf{S}}$,

then $\Phi$ is said to be a measure ring isomorphism. If there exists a [weak] measure ring isomorphism of $(\dot{\mathbf{S}}, \dot{\mu})$ onto $(\dot{\mathbf{T}}, \dot{\nu})$,

exists, then the measure spaces $(X, S, \mu)$ and $(Y, T, v)$, as well as the measure rings $(\dot{S}, \dot{\mu})$ and $(\dot{T}, \dot{v})$, are said to be strongly isomorphic. (The point mapping $\varphi$ itself is also frequently called a strong isomorphism.)

Example K. Let $\{(X_{\gamma}, S_{\gamma}, \mu_{\gamma})\}$ and $\{(\tilde{X}_{\gamma}, \tilde{S}_{\gamma}, \tilde{\mu}_{\gamma})\}$ be two similarly indexed families of measure spaces such that $X_{\gamma} \cap X_{\gamma'} = \emptyset = \tilde{X}_{\gamma} \cap \tilde{X}_{\gamma'}$ for all indices $\gamma \neq \gamma'$, and let us form the direct sums

$$(X, S, \mu) = \sum_{\gamma} \oplus (X_{\gamma}, S_{\gamma}, \mu_{\gamma})$$

and

$$(\tilde{X}, \tilde{S}, \tilde{\mu}) = \sum_{\gamma} \oplus (\tilde{X}_{\gamma}, \tilde{S}_{\gamma}, \tilde{\mu}_{\gamma}).$$

If for each index $\gamma$ the measure spaces $X_{\gamma}$ and $\tilde{X}_{\gamma}$ are isomorphic, then it is easy to see that $X$ and $\tilde{X}$ are also isomorphic. Likewise, if for each index $\gamma$ the spaces $X_{\gamma}$ and $\tilde{X}_{\gamma}$ are strongly isomorphic, and if the index family is countable, then it is readily seen that $X$ and $\tilde{X}$ are also strongly isomorphic. On the other hand, if for each index $\gamma$ there exists a strong isomorphism $\varphi_{\gamma}$ of all of $X_{\gamma}$ onto all of $\tilde{X}_{\gamma}$, then the isomorphisms $\varphi_{\gamma}$ can be combined to construct a strong isomorphism of (all of) $X$ onto (all of) $\tilde{X}$, no matter what the cardinality of the index family may be. Using this remark it is possible to introduce a notion of weak direct sum of

defines (unambiguously) a one-to-one mapping of $X_0$ onto the set $Y_0$ of irrational numbers in the unit interval $Y$. Note that if $\mu_1$ denotes Lebesgue–Borel measure on the real line, and $\mu_2$ denotes Lebesgue–Borel measure on the plane $\mathbb{R}^2$, then $\mu_1(Y \setminus Y_0) = \mu_2(X \setminus X_0) = 0$. Moreover, if $r$ and $s$ are any two dyadic fractions of the form $k/2^n$, $0 \leq k < 2^n$, and if $Q$ denotes the square $[r, r + 1/2^n] \times [s, s + 1/2^n]$, then direct calculation discloses that $\varphi$ maps $Q \cap X_0$ onto the set of irrational numbers in an interval of length $1/2^{2n}$. Since

$$\mu_2(Q \cap X_0) = |Q| = \left(\frac{1}{2^n}\right)^2 = \frac{1}{2^{2n}} = \mu_1(\varphi(Q \cap X_0)),$$

and since squares of the special form here considered suffice to generate the $\sigma$-ring of Borel subsets of $X$, while subintervals of the form $[k/2^{2n}, (k + 1)/2^{2n}]$ likewise suffice to generate the $\sigma$-ring of Borel subsets of $Y$, it follows readily that $\varphi$ is a measure preserving mapping of $X_0$ onto $Y_0$ (see Problem 8A). Thus the unit square equipped with Lebesgue–Borel measure and the unit interval equipped with Lebesgue–Borel measure are strongly isomorphic measure spaces. Similarly the real line $\mathbb{R}$ equipped with Lebesgue–Borel measure is strongly isomorphic to the plane $\mathbb{R}^2$ equipped with Lebesgue–Borel measure. More generally, $(\mathbb{R}, \mathbf{B}, \mu_1)$ is strongly isomorphic to $\mathbb{R}^n$ equipped

and the space $\dot{\mathcal{L}}_v$ equipped with the metric

$$\rho_v([g_1], [g_2]) = \int_Y |g_1 - g_2| dv, \quad g_1, g_2 \in \mathcal{L}_v.$$
