(Cayley). The complete graph $K_n$ admits $n^{n-2}$ distinct subgraphs which are spanning trees.

INDICATION OF PROOF. The method sketched here is due to H. Prüfer [p.7]. Let $

of $K_n$ are not divided equally into isomorphism classes. (For example, another class comprises only the $n$ trees consisting of a single vertex of valence $n - 1$ which is joined by an edge to each of the others.) Thus our problem is considerably more difficult than the labeled problem. We find that the groups of automorphisms of systems (§IIE) play a significant role.

Let $G$ be any group, let $e$ denote its identity, and let $X$ be a set. We say that $G$ acts on $X$ if there exists a function $G \times X \rightarrow X$ given by $(g, x) \mapsto gx$ such that for all $x \in X$ and all $g_1, g_2 \in G$,

(a) $ex = x$
(b) $(g_2g_1)x = g_2(g_1x)$.

Of particular interest to us will be the case where $G$ is a subgroup of $\Pi(X)$, the group of all permutations on $X$. In this case, $gx$ becomes $g(x)$ for all $(g, x) \in G \times X$.

Suppose that $G$ acts on $X$ and let $S \subseteq X$. Generalizing a notion from §IA, we say that $g$ fixes $S$ if $gx \in S$ for all $x \in S$. If every element of $G$ fixes $S$, then $S$ is a fixed set of $G$. Certainly $\varnothing$ and $X$ are always fixed sets. If $\mathcal{S}$ denotes the collection of fixed sets, then the cells of the fine partition of $\mathcal{S}$ are called the orbits of $G$. If $S \neq X$, we say that $G$ acts transitively on $S$ if given $x, y \in S$, there exists $g \in G$ such that $gx = y$. (Cf. §IIE.) If $x \in X$, we define the stabilizer of $x$ to be $G_x = \{g \in G : gx = x\}$. Clearly, $G_x$ is a subgroup of $G$.

The following is a pair of

If $g \in G$ and $G$ acts on $X$, then we write $\langle g \rangle$ to denote the (cyclic) subgroup of $G$ generated by $\{g\}$. Clearly $\langle g \rangle$ acts on $X$; we let $o_j(g)$ denote the number of orbits of $\langle g \rangle$ of cardinality $j$ and let $O(g) = \sum_{j=1}^{\infty} o_j(g)$.
