The non-negative solutions of (1) exhibited in P1 are the only ones.

Proof: The two-dimensional case is left out, having been settled in E27.4, but the proof for the one-dimensional case will nevertheless parallel closely that in E27.4. Consequently it will be convenient to adopt the notation in D27.4 and P27.3. At first one is tempted to let $Q(x,y) = P(x,y)$, restricted to $x$ and $y$ in $R - \{0\}$. Then the countable set $S$ in P27.3 would be $S = R - \{0\}$. But this is not a good idea, since $g_{(0)}(x,y)$ may fail to be positive for some $x$ or some $y$ in $R - \{0\}$. Instead we shall choose $S$ in a slightly more elaborate fashion, which will greatly simplify the remainder of the proof.

Given a solution $h(x) \geq 0$ (but not identically zero) on $R - \{0\}$ of

(1) $$\sum_{y \neq 0} P(x,y)h(y) = h(x), \quad x \neq 0,$$

we define

$$S = [x \mid x \in R - \{0\}, h(x

familiar from the proof of P18.8). This observation verifies our claim that $S$ is either a half-line, or all of $R - \{0\}$. Let us now suppose that $S$ is a half-line, say the positive one. Then, as we just saw, it follows that

$$g_{(0)}(x,y) = 0 \text{ when } x < 0, \quad y > 0,$$

and in particular

(3) $$P(x,y) = 0 \text{ when } x < 0, \quad y > 0,$$

as could have been observed directly from (1). This state of affairs simplifies matters considerably. We can now define, in all cases ($S$ being either a half-line or all of $R - \{0\}$),

$$Q(x,y) = Q_1(x,y) = P(x,y), \quad Q_0(x,y) = \delta(x,y), \quad x,y \in S,$$

$$Q_{n+1}(x,y) = \sum_{t \in S} Q_n(x,t)Q(t,y), \quad x,y \in S, \quad n \geq 0,$$

and finally

$$g(x,y) = \sum_{n=0}^{\infty} Q_n(x,y), \quad x,y \in S,$$

being sure that

(4) $$g(x,y) > 0 \text{ for } x,y \in S,$$

(5) $$g(x,y) = g_{(0)}(x,y) \text{ for } x,y \in S.$$

Next we define the transient kernel

$$Q^h(x,y) = \frac{Q(x,y)h(y)}{h(x)}, \quad x,y \in S,$$

its iterates $Q_n^h(x,y)$, and its Green function

(6) $$g^h(x,y) = \sum_{n=0}^{\infty} Q_n^h(x,y) = \frac{g(x,y)h(y)}{h(x)},$$

and proceed along the lines of P27.3. But it is convenient at this point to separate the argument into two cases, according as $\sigma^2 = \infty$ or $\sigma^2 < \infty$.

where $\xi$ is an arbitrary point in $S$. Forgetting for the moment the unpleasant possibility that $a(\xi) = 0$, we see that, in view of (5), (7), and P1, all the hypotheses in P27.3 are satisfied. Thus we are able to conclude that $h(x)$ is a multiple of $a(x)$, which proves P2 when $\sigma^2 = \infty$, provided we were able to choose $\xi$ so that $a(\xi) > 0$. Suppose now that $\xi > 0$ and $a(\xi) = 0$ (the case $\xi < 0$ receives the same treatment). This implies, in view of P30.2, that the random walk is left continuous. Now either $S = R - \{0\}$, in which case we can modify (7) by choosing $\xi < 0$ so that $a(\xi) > 0$. Otherwise $S = [x | x > 0]$, but that is impossible, since (3) gives $P(-1,n) = 0$ for $n > 0$, whereas left continuity together with $\sigma^2 = \infty$ implies $P(-1,n) > 0$ for arbitrarily large $n$. Thus the proof of P2 is complete when $\sigma^2 = \infty$.

When $\sigma^2 < \infty$ we cannot hope to quote P27.3 verbatim, as it deals only with cases where there is a unique solution. But it is easy enough to retrace the steps in the proof of P27.3 until we come to the crucial argument which begins with equation (4), namely

$$e(x) = 1 = \lim_{n \to \infty} \sum_{y \in S} \frac{g^h(x,y)}{g^h(\xi,y)} \gamma_n(y).$$

By the same compactness argument used there and in E27.4 and E27.5, equation (8) yields the conclusion that

$$1 = u^h(x) + \lim_{y \to -\infty} \frac{g^h(x,y)}{g^h(\xi,y)} \gamma(-\infty)$$

$$+ \lim_{y \to +\infty} \frac{

functions. By the Riesz decomposition theorem (T27.1) the potential must be zero. Substituting (10) into (9), and multiplying (9) through by $h(x)$ we find

$$h(x) = \gamma(-\infty) \frac{h(\xi)}{\sigma^2 a(\xi) - \xi} [\sigma^2 a(x) - x] + \gamma(+\infty) \frac{h(\xi)}{\sigma^2 a(\xi) + \xi} [\sigma^2 a(x) + x], \quad x \in S.$$

This shows that every regular function $h(x)$ is a linear combination of $a(x)$ and $x$, which is just what we wanted to prove!

The proof of P2 will now be completed by eliminating the alarming possibility that equation (9) does not make sense because one of the denominators $\sigma^2 a(\xi) \pm \xi$ in (10) vanishes. According to P30.3 of the last section, it is only left- or right-continuous random walk that could cause trouble. For every other random walk one can choose $\xi$ so that $\sigma^2 a(\xi) - |\xi| \neq 0$. Therefore we shall consider all the different possibilities separately.

(a) Suppose the random walk is both left and right continuous. Then $0 < P(0,1) = P(0,-1) = [1 - P(0,0)]/2 \leq 1/2$. But in this very simple case P2 can be verified directly.

(b) Suppose the random walk is left but not right continuous. Then there are several possibilities concerning the set $S$. If $S = R - \{0\}$ or $S = [x \mid x < 0]$ we may choose a negative value of $\xi$, such that, according to P30.3, both $\sigma^2 a(\xi) + \xi$ and $\sigma^2 a(\xi) - \xi$ are non-zero. Finally there is the case $S = [x \mid x > 0]$. But then an examination of equation (1) shows that this case cannot arise; equation (1) implies that if $h(x) > 0$ for $x > 0$, then $h

For many applications it is important to modify T1 to give information about potentials, i.e., about non-negative solutions of

$$\sum_{y \in R} P(x,y)f(y) - f(x) = \delta(x,0), \quad x \in R,$$

or, more generally, about functions $f(x) \geq 0$ on $R$ such that

$$Pf(x) - f(x) = \psi(x), \quad x \in R,$$

with

$$\psi(x) = 0 \quad \text{when} \quad x \in R - A.$$

This reformulation is accomplished by means of a minimum principle which is the recurrent analogue of the maximum principle for transient random walk in part (a) of P25.9 in Chapter VI.