Every open subset $U$ of $\mathbb{C}$ is uniquely expressible as a countable union of disjoint domains, and these domains are the components of $U$.

Proof. The empty set is the empty union of domains. If $U$ is a nonempty open set in $\mathbb{C}$, and if $\lambda_0$ is an element of some component $U_0$ of $U$, then (Ex. A) there is an open disc $D_r(\lambda_0)$ about $\lambda_0$ ($r > 0$) such that $D_r(\lambda_0) \subset U$. Since discs are (arcwise) connected, it is clear that $D_r(\lambda_0) \subset U_0$, and hence that the components of $U$ are open. That no collection of disjoint open sets in $\mathbb{C}$ can be uncountable is clear from the fact that $\mathbb{C}$ satisfies the second axiom of countability. To complete the proof it suffices to observe that if $\{U_n\}$ is a disjoint (countable) collection of nonempty domains such that $U = \bigcup_n U_n$, and if $V$ is a connected component of $U$ that meets some one $U_n$, then $V \cap \partial U_n = \emptyset$, and therefore $V = U_n$ (Prop. 3.6).

If $K$ is a compact subset of $\mathbb{C}$, then $K$ is bounded, that is, there exists a disc $D_R(0)$ large enough so that $K \subset D_R(0)^-$, and since $V = \mathbb{C} \setminus D_R(0)^-$ is (arcwise) connected, it follows that $V$ is entirely

easily seen (Prop. 3.3) that the range $J$ of a Jordan loop $\gamma$ is compact and could equally well be characterized as a homeomorphic image in $\mathbb{C}$ of the unit circle. We shall also refer to the range of a Jordan loop as a Jordan loop or Jordan curve when that is convenient. In the event that a Jordan curve $J$ is a simple polygon in $\mathbb{C}$ (as defined in elementary geometry) we say that $J$ is a Jordan polygon.

A Jordan domain in $\mathbb{C}$ is a domain whose (entire) boundary consists of the union of a finite number of pairwise disjoint Jordan curves. The closure of a Jordan domain is, therefore, the union of the domain and the various Jordan curves constituting its boundary. Such a closed set is known as a Jordan region.

The following result is the central fact concerning the topology of the plane; an elementary proof can be found in [66; pp. 100–104].
