If two cosets $AU, BU$ have one element in common, then they have all elements in common, thus they agree except for order.

To prove this let $AU_a = BU_b$ be a common element. Then it follows that $B = AU_a U_b^{-1}$, hence

$$BU = (AU_a U_b^{-1} U_1, AU_a U_b^{-1} U_2, \ldots).$$

However $U_a U_b^{-1} U_i$ runs through all elements of $\mathfrak{U}$ for $i = 1, 2, \ldots$ because of the group property (iv) of $\mathfrak{U}$, hence in fact $AU$ and $BU$ agree.

The number of different elements occurring in a coset $AU$ is obviously independent of $A$; it is equal to the order of $\mathfrak{U}$. Let this order be called $N$ (where $N$ may also be $=\infty$). Each element $A$ of $\mathfrak{G

contained in each coset, we have

$$h = j \cdot N$$

and thus we have shown

**Theorem 19.** In a finite group of order $h$, the order $N$ of each subgroup is a divisor of $h$.

The quotient $h/N = j$ is called the index of the subgroup relative to $\mathfrak{G}$.

In case $\mathfrak{G}$ is an infinite group, then the order of $\mathfrak{U}$ as well as the number of different cosets can be infinite and at least one of these cases must obviously occur. Furthermore, the number of different cosets is called the index of $\mathfrak{U}$ relative to $\mathfrak{G}$ whether this index is finite or not.

Our further investigations deal first with finite groups.

A system $S = (U_1, U_2, \ldots)$ of elements which belong to a finite group forms a subgroup of $\mathfrak{G}$ as soon as it is known that each product of two elements $U$ again belongs to $S$. For the group axioms (ii) and (iii) are satisfied automatically, (i) holds by assumption, and with finite groups (iv) is a consequence of the remaining axioms.

For example, all the powers of an element $A$ with a positive exponent always form a subgroup of $\mathfrak{G}$. These powers cannot all be different, since $\mathfrak{G}$ contains only finitely many elements. From $A^m = A^n$ it follows that $A^{m-n} = E$. Hence a certain power of $A$ with exponent different from zero is always $E$.

In order to gain an overview of those exponents $q$ for which $A^q = E$, we note that these exponents obviously form a module since from $A^q = E$ and $A^r = E$ it follows that $A^{q \pm r} = E$. Hence by Theorem 1 these $q$ are identical with all multiples of an integer $a (> 0)$. This exponent $a$, uniquely determined by $A$, is called the order of $A$. This exponent has the property:

$$A^r = E \quad \text{if and only if} \
