and use the following principles: To prove that two elements of the product $X$ are equal, it is necessary and sufficient to prove this followed by each projection (perfectly true even when the index set is empty). To prove that two elements of $A$ are equal it is necessary and sufficient to prove that they are identified by the inclusion map $i$. Because $h$ is onto we may invoke the axiom of choice (section 2, exercise 1) to choose $s: \mathcal{V} \longrightarrow X$ such that $s.h = r$. Let us turn to the proof of sufficiency. Let $E$ be the set of all equations $\{e_1, e_2\} \subset \mathcal{V}\Omega$ such that for every algebra $(X, \delta)$ in $\mathcal{A}$ and every function $r: \mathcal{V} \longrightarrow X$ it is the case that $r^\#$ identifies $e_1$ and $e_2$. Trivially, all algebras in $\mathcal{A}$ satisfy $E$. Let $(X, \delta)$ be an arbitrary $(\Omega, E)$-algebra. We will show that $(X, \delta)$ is a quotient of a subalgebra of a product of elements of $\mathcal{A}$. If $\mathbf{T}$ is the algebraic theory of $(\Omega, E)$ as in 4.1, the structure map of $(X, \delta)$ is an $\Omega$-homomorphism onto, so it suffices to show that $XT$ is isomorphic to a subalgebra of a product of elements of $\mathcal{A}$. To do this we resort to a standard argument and show that $XT$ admits enough homomorphisms to elements of $\mathcal{A}$ to separate points, that is:

(4.23) If $[p] \neq [q] \in XT$ then there exists an algebra $(A, \gamma)$ in $\mathcal{A}$ and a map $r: X \longrightarrow A$ such that $[p]r^\# \neq [q]r^\#$.

To prove 4.23, let $X_n = \{x_1, \ldots, x_n\}$ be the finite set of all variables in

Since $[p]r^{\#} = \langle p', s^{\#} \rangle$ the proof of 4.23 is complete. The rest of the proof is based on very general principles. For each pair $(t, u)$ of distinct elements of $XT$ choose $A_{t, u}$ in $\mathcal{A}$ and a homomorphism $r_{t, u}:XT \longrightarrow A_{t, u}$ which maps $t$ and $u$ to different values. Let $A$ be the product algebra of $(A_{t, u}:t \neq u \in XT)$ and define a single homomorphism $r:XT \longrightarrow A$ by $([p]r)_{t, u} = [p]r_{t, u}$. By construction, $r$ is injective. The proof is complete by the following standard fact which we leave to the reader for verification.

(4.24) If $f:(X, \delta) \longrightarrow (Y, \gamma)$ is an injective $\Omega$-homomorphism then its image $Xf \subset Y$ is a subalgebra of $(Y, \gamma)$ and the map $g:X \longrightarrow Xf$, $xg = xf$ is an isomorphism. (For a hint, see 4.32.)

We have already seen that the passage from a finitary equational presentation to its theory is a well-defined injection from equivalence classes of presentations as in 2.18 into isomorphism classes of finitary theories ("isomorphism" being informally defined by 4.14). We conclude this section with a proof that this passage is bijective so that "finitary universal algebra is the study of finitary algebraic theories in Set."