Assume that the order of $G$ is prime to $p$. Then:

(i) Each $k[G]$-module (resp. each $A$-free $A[G]$-module) is projective.

(ii) The operation of reduction mod. $\mathfrak{m}$ defines a bijection from $S_K$ onto $S_k$.

(iii) If we identify $S_K$ with $S_k$ as in (ii), the matrices $C, D, E$ are all identity matrices.

(More briefly: the representation theory of the group $G$ is “the same” over $k$ as over $K$.)

Let $E$ be an $A[G]$-module which is free over $A$. We can write $E$ as a quotient $L/R$ of a free $A[G]$-module $L$. Since $E$ is $A$-

15.7: Example: products of $p'$-groups and $p$-groups

EXERCISE

15.9. Suppose that $g$ is prime to $p$. Let $E$ be a free $A$-module.

(a) Let $n \geqslant 1$ be an integer, and let

$$\rho_n: G \rightarrow \mathbf{GL}(E/m^n E)$$

be a homomorphism of $G$ into the group of automorphisms of $E/m^n E$. Show that $\rho_n$ can be lifted to

$$\rho_{n+1}: G \rightarrow \mathbf{GL}(E/m^{n+1} E)$$

and that this lifting is unique, up to conjugation by an automorphism of $E/m^{n+1} E$ congruent to 1 mod $m^n$. [Use the fact that the cohomology groups of dimension 1 and 2 of $G$ with values in $\text{End}(E/mE)$ are zero.]

(b) Obtain from (a) the fact that every linear representation

$$\rho_1: G \rightarrow \mathbf{GL}(E/mE)$$

of $G$ over $k$ can be lifted, in an essentially unique way, to a representation of $G$ over $A$.

15.6 Example: $p$-groups

Suppose that $G$ is a $p$-group, of order $p^n$. We have seen (8.3, cor. to prop. 26) that the only irreducible representation of $G$ in characteristic $p$ is the unit representation. It follows that the artinian ring $k[G]$ is a local ring with residue class field $k$. The projective envelope of the simple $k[G]$-module $k$ is $k[G]$, i.e., the regular representation of $G$. The groups $R_k(G)$ and $P_k(G)$ can be both identified with $Z$, and the Cartan homomorphism $c: Z \rightarrow Z$ is multiplication by $p^n$. The homomorphism $d: R_K(G) \rightarrow Z$ corresponds to the K-rank; the homomorphism $e: Z \rightarrow R_K

on which P acts trivially. Because of (a) this means that $F \otimes k[P]$ is the projective envelope of F. However, every projective module is the projective envelope of its largest semisimple quotient. We thus see that every projective module has the form $F \otimes k[P]$.

(c) An A[G]-module $\tilde{E}$ is projective if and only if it is isomorphic to $\tilde{F} \otimes A[P]$, where $\tilde{F}$ is an A-free A[S]-module.

Clearly a module of the form $\tilde{F} \otimes A[P]$ is projective. The converse is proved by applying (b) to $E = \tilde{E}/m\tilde{E}$: if $\tilde{E}$ is projective, we have $E \simeq F \otimes k[P]$, and we know that F can be lifted to an A[S]-module $\tilde{F}$ which is free over A (and even A[S]-projective, cf. above). The module $\tilde{F} \otimes A[P]$ is the projective envelope of $F \otimes k[P]$, and thus is isomorphic to $\tilde{E}$.

Properties (a) and (b) show in particular that the Cartan matrix of G is the scalar matrix $p^n$, where $p^n = \text{Card}(P)$.

16. 1 Properties of the cde triangle

The main result is the following*:
