If $\mathcal{E} \neq (0)$ is a normed space, then $\mathcal{L}(\mathcal{E})$ is not only a normed space but is also an algebra (Ch. 2, p. 19) in which the conditions

$$\| ST \| \leq \| S \| \| T \|, \quad S, T \in \mathcal{L}(\mathcal{E}),$$

and

$$\| 1_{\mathcal{E}} \| = 1$$

hold. If $\

Example K. If $x = \{\xi_n\}_{n=0}^{\infty}$ and $y = \{\eta_n\}_{n=0}^{\infty}$ are two elements of $(\ell_p)$ (for some fixed value of $p$, $1 \leq p \leq +\infty$) then the sequence $xy = \{\xi_n \eta_n\}_{n=0}^{\infty}$ also belongs to $(\ell_p)$, and it is readily verified that $\|xy\|_p \leq \|x\|_p \|y\|_p$. (Indeed, $\|xy\|_p \leq \|x\|_\infty \|y\|_p$, and it is clear that $\|x\|_\infty \leq \|x\|_p$.) Moreover, it is easily seen that $(\ell_p)$ is a linear algebra with respect to this product. Thus each of the spaces $(\ell_p)$ is a Banach algebra with respect to termwise or coordinatewise multiplication. The algebra $(\ell_\infty)$ is unital, the algebras $(\ell_p)$, $1 \leq p < +\infty$, are not. Similarly, the spaces $(\ell_p)^{\#}$, $1 \leq p \leq +\infty$, are all Banach algebras with respect to coordinatewise multiplication.

Example L. If $X$ is a nonempty compact Hausdorff space, then $\mathcal{C}(X)$ is a unital Banach algebra with respect to pointwise multiplication. More generally, if $X$ is an arbitrary nonempty topological space, and if $\mathcal{C}_b(X)$ denotes the linear space of bounded continuous complex-valued functions on $X$ equipped with the sup norm (Prob. 11D), then $\mathcal{C}_b(X)$ is a unital Banach algebra with respect to pointwise multiplication. (This example contains, as a special case, the Banach algebra $(\ell_\infty)$, which coincides with $\mathcal{C}_b(\mathbb{N}_0)$ when $\mathbb{N}_0$ is equipped with the discrete topology.)
